---
title: "Working conditions and mental health among doctors and nurses in the European Union, Iceland, and Norway: a cross-sectional survey"
author: "Roberto Mediavilla and Vicente Arrona"
date: "`r Sys.Date()`"
output: 
  html_document: 
    toc: true
    toc_float: true
editor_options: 
  chunk_output_type: console
---

```{r setup}
knitr::opts_chunk$set(                   # high resolution for non-vector formats
  echo = TRUE,
  error = FALSE,
  warning = FALSE,               
  message = TRUE,
  fig.keep = 'none'
)
```

```{r source}
source("src/setup.R")
source("src/fns_associations.R")
source("src/fns_prevalences.R")

ds <- # dataset
  
  readRDS("data/who_hcw_survey_clean.rds")

cb <- # codebook

  read.csv("ext/data_mapping.csv", na.strings = "")

who_ipw_population <- # popuation data
  
  readRDS("ext/who_ipw_population.rds")

ipw_sample <- # sample data
  
  readRDS("ext/ipw_sample.rds")

# weights to DS

w <- 
  
  readRDS("ext/weights.rds")

# total denominator
who_n_loc <- 
  
  readRDS("ext/who_n_loc.rds")

```

```{r weights}
# Add IPW weights to dataset
ds <- left_join(ds, w, by = "user_id")

```

```{r var lists}

# Sociodemographic variables

scdm <- c("scdm_1_rec",
          "scdm_2_rec",
          "work_1",
          "work_2",
          "work_5_rec",
          "work_7")

scdm_ext <- c("scdm_1_rec",
              "scdm_2_rec",
              "scdm_5_dic",
              "scdm_6",
              "work_1",
              "work_2",
              "work_5_rec",
              "work_7",
              "work_13",
              "work_14",
              "work_16")

# MH outcomes

out_dic <- c("phq_co", "gad_co", "suic_idea", "cage_co")

out <- c("phq_sc", "gad_sc", "mh_phq_9", "cage_sc")

out_poisson <- c("phq_co_poi", "gad_co_poi", "suic_idea_poi", "cage_co_poi")

named_outcomes <- c(
  "Depression" = "phq_co",
  "Anxiety"    = "gad_co",
  "Alcohol dependence"  = "cage_co",
  "Suicidal thoughts"    = "suic_idea"
)


# Job demands

demands <- c("work_8", "work_11", "work_12", "work_23", "work_24") 
demands_num <- c(paste0(demands, "_num"))[c(1, 2, 4, 5)] # work_12 is binary
demands_dic <- c(paste0(demands, "_dic")) 

named_demands <- c(
  "Extended working hours"    = "work_8_dic",
  "Frequent night shifts"    = "work_11_dic",
  "Regular shift work" = "work_12_dic",
  "Tight deadlines" = "work_23_dic",
  "Angry patients or relatives" = "work_24_dic")

# Job hazards

hazards <- c("work_30", "work_31", "work_32", "work_33")
hazards_dic <- c(paste0(hazards, "_dic"))

hazards_num <- c(paste0(hazards, "_num"))

named_hazards <- c(
  "Sexual harassment"    = "work_30_dic",
  "Violent threats"    = "work_31_dic",
  "Physical violence" = "work_32_dic",
  "Bullying" = "work_33_dic"
)

# Organisational support structures

protocols <- c("work_25", "work_26", "work_27", "work_28", "work_29")
protocols_dic <- c(paste0(protocols, "_dic"))

named_protocols <- c(
  "Work council or union" = "work_25_dic",
  "Employee feedback"    = "work_26_dic",
  "Stress action plan"    = "work_27_dic",
  "Harassment protocol" = "work_28_dic",
  "Violence protocol" = "work_29_dic"
)

# Job Resources

resources <- c("work_19", "work_20", "work_21", "work_22")
resources_dic <- c(paste0(resources, "_dic"))

named_resources <- c(
  "Influence over work" = "work_19_dic",
  "Influence over work (breaks)"    = "work_20_dic",
  "Colleague support"    = "work_21_dic",
  "Support from superiors" = "work_22_dic"
)

# define exposures

all_exposures <- c(demands_dic, hazards_dic, resources_dic, protocols_dic)

all_exposures_bis <- c(demands, hazards, resources, protocols)

# Covars

covs_1 <- c("scdm_1_rec",
            "scdm_2_rec",
            "scdm_5_dic",
            "scdm_6",
            "work_1",
            "work_2",
            "work_3_rec",
            "work_4_dic",
            "work_5_rec",
            "work_7")

covs_2 <- c("loc_2")

# Exposure order

exposure_order <-  
  c(demands_dic, hazards_dic, resources_dic, protocols_dic)

exposure_order_named <- 
  c("Extended working hours",
    "Frequent night shifts",
    "Regular shift work",
    "Tight deadlines",
    "Angry patients or relatives",
    "Sexual harassment",
    "Violent threats",
    "Physical violence", 
    "Bullying",
    "Influence over work",
    "Influence over work (breaks)",
    "Colleague support",
    "Support from superiors",
    "Work council or union",
    "Employee feedback",
    "Stress action plan",
    "Harassment protocol",
    "Violence protocol")

# This will be needed
exposure_metadata <- 
  
  bind_rows(
  enframe(
    named_demands, 
    name = "Label", 
    value = "Column"
    )  |>
    mutate(Category = "Job Demands"),
  enframe(
    named_hazards, 
    name = "Label", 
    value = "Column"
    )  |>  
    mutate(Category = "Job Hazards"),
  enframe(
    named_resources, 
    name = "Label", 
    value = "Column"
    )  |> 
    mutate(Category = "Job Resources"),
  enframe(
    named_protocols, 
    name = "Label", 
    value = "Column"
    )  |> 
    mutate(Category = "Organisational support structures")
)

# Outcome order

outcome_order <- 
  c("Depression", "Anxiety", "Alcohol dependence", "Suicidal thoughts")
```

```{r preprocess}

# Some responses are too long

ds <- 
  
  ds  |> 
  mutate(work_7 = fct_recode(
    work_7,
    "Public and private sectors" = 
      "I work in both the public sector and in the private sector (or I work in the public sector and I am self-employed)",
    "Private sector only" = 
      "I work in the private healthcare sector only (I do not work in the public sector)",
    "Public sector only" = 
      "I work in the public healthcare sector only (I do not work in the private sector, nor am I self-employed)"
  ))


ds <- 
  
  ds |> 
  mutate(scdm_1 = fct_recode(scdm_1, "Under 20" = "Less than 20 years old"))


ds <- 
  
  ds |> 
  mutate(work_5 = fct_recode(
    work_5,
    "Extra-hospital emergencies" = 
      "Emergency care outside hospital (e.g., ambulance)",
    "In-hospital care" = 
      "Inpatient care (hospital services)",
    "Outpatient primary care" = 
      "Primary care (outpatient services)",
    "Outpatient secondary care" =
      "Secondary care (outpatient services)"
  ))


ds <- 
  
  ds |> 
  mutate(work_5_rec = fct_collapse( 
    work_5,
    "Inpatient" = c("Emergency department",
                    "In-hospital care"),
    "Outpatient" = c("Outpatient primary care",
                     "Outpatient secondary care"),
    "Other" = c("Extra-hospital emergencies",
                "Other")
    )
  )

ds <- 
  
  ds |> 
  mutate(work_11 = fct_recode(
    work_11,
    "Daily" = 
      "Every day",
    "Almost daily" = 
      "At least 4 days a week, but not every day",
    "2-3 days/week" = 
      "2 or 3 days a week",
    "Almost weekly" = 
      "Almost every week",
    "1-2 times/month" =
      "Once or twice a month",
    "Less than monthly" =
    "Less than once a month",
    "Never/Rarely" = 
      "Never or very rarely (e.g., once or twice a year)"
  ))


ds <- 
  
  ds |> 
  mutate(work_8 = fct_recode(
    work_8,
    "< 11 h" = 
      "Less than 11 hours",
    "11-20 h" = 
      "11-20 hours",
    "21-30 h" = 
      "21-30 hours",
    "31-40 h" = 
      "31-40 hours",
    "41-50 h" =
      "41-50 hours",
    "51-60 h" = 
      "51-60 hours",
    "61-70 h" = 
      "61-70 hours",
    "> 70 h" = 
      "More than 70 hours"
  ))

# Some variables and exposures require processing

ds <- 
  
  ds |> 
  
  # Recode household composition 
  
  mutate(scdm_5_dic = case_when(
    str_detect(scdm_5, "with children") ~ "Has children",
    str_detect(scdm_5, "without children") ~ "No children",
    TRUE ~ NA
    ),
    scdm_5_dic = factor(scdm_5_dic,
                        levels = c("Has children", "No children"),
                        ordered = FALSE)
  ) |>
  
  # recode length of service
  
  mutate(work_3_rec = fct_collapse(
    work_3,
    "5 years or less" = c("Less than 1 year", "1-3 years", "4-5 years"),
    "More than 10 years" = c("11-20 years", "21-30 years", "31-40 years",
                             "More than 40 years")
    )
  ) |> 
  
  # Recode number of job positions
  
  mutate(
    work_4_dic = if_else(work_4 == "One",
                         "One",
                         "More than one"),
    work_4_dic = factor(work_4_dic,
                        levels = c("One", "More than one"))
  ) |> 
  
  # Recode weekly working hours
  
  mutate(
    work_8_dic = case_when(as.numeric(work_8) <= 5 ~ "No", # <= 50h
                           as.numeric(work_8) > 5 ~ "Yes"), # > 50h
    work_8_dic = factor(work_8_dic, levels = c("No", "Yes"))
  ) |> 
  
  # Recode frequency of night work
  
  mutate(
    work_11_dic = 
      case_when(as.numeric(work_11) > 5 ~ "No", # 1 or 2x a month or less
                as.numeric(work_11) <= 5 ~ "Yes"), # Almost every week and more
    work_11_dic = factor(work_11_dic, levels = c("No", "Yes")),
    work_11 = fct_rev(work_11)
  ) |> 
  
  # name var for shifts
  
  mutate(work_12_dic = factor(work_12, levels = c("No", "Yes"))
  ) |> 
  
  # create dichotomous var for contract type
  
  mutate(work_16_dic = fct_recode(work_16,
                                  "Yes" = "Temporary contract",
                                  "No" = "Fixed contract"),
         work_16_dic = factor(work_16_dic,
                              levels = c("No", "Yes"),
                              ordered = FALSE)
  ) |> 
  
  # recode managing patient anger
  
  mutate(
    across(
      all_of(c("work_23", "work_24")),
      ~ factor(
        fct_collapse(.x,
                     "Yes" = c("Around 1/4 of the time",
                               "Around half of the time",
                               "Around 3/4 of the time",
                               "Almost all of the time",
                               "All of the time"),
                     "No" = c("Never",
                              "Almost never")),
                     levels = c("No", "Yes"),
                     ordered = FALSE),
        .names = "{.col}_dic"
        )
      ) |> 
  
  # recode violence
  
   mutate(
    across(
      all_of(hazards),
      ~ factor(
        fct_collapse(.x,
                     "Yes" = c("Yes, daily", 
                             "Yes, weekly", 
                             "Yes, monthly", 
                             "Yes, a few times"),
                     "No" = "No"
        ),
        levels = c("No", "Yes"), ordered = FALSE
      ),
      .names = "{.col}_dic"
    )
  ) |>
  
  # Recode protocols, drop "Do not know", ensure factor levels
 
   mutate(
    across(
      all_of(protocols),
      ~ fct_recode(.x, NULL = "Do not know"),
      .names = "{.col}_dic"
    )
  ) |> 

  # relevel protocols

  mutate(
    across(
      all_of(protocols_dic),
      ~ fct_relevel(.x, "No")
    )
  ) |> 
  
  # recode job resources
  
  mutate(
    across(
      all_of(c("work_19", "work_20", "work_21", "work_22")),
      ~ factor(
        fct_collapse(.x,
                     "No" = c("Sometimes", "Seldom", "Never / Hardly ever"),
                     "Yes" = c("Always", "Often"),
        ),
        levels = c("No", "Yes"), ordered = FALSE
      ),
      .names = "{col}_dic"
    )
  ) |> 
  
  # recode work-life balance
  
  mutate(
    work_34_dic = case_when(as.numeric(work_34) <= 3 ~ "No",
                            as.numeric(work_34) > 3 ~ "Yes"),
    work_34_dic = factor(work_34_dic, levels = c("No", "Yes"))
  ) |> 
  
  # create numeric variables
  
  mutate(
    across(
      all_of(hazards),
      ~ case_when(
        .x == "No"                ~ 0,
        .x == "Yes, a few times"  ~ 1,
        .x == "Yes, monthly"      ~ 2,
        .x == "Yes, weekly"       ~ 3,
        .x == "Yes, daily"        ~ 4,
        TRUE                      ~ NA_real_
        ),
      .names = "{.col}_num"
      )
    ) |> 
  mutate(
    across(
      all_of(demands) & !all_of("work_12"), # work_12 is binary
      \(x) as.numeric(x) - 1, # 0 as reference
    .names = "{.col}_num")) |> 
  mutate(
    across(
      all_of(resources),
      \(x) as.numeric(x) - 1, # 0 as reference
    .names = "{.col}_num")) |> 
  
  # create poisson outcome variables

  mutate(
    across(
      all_of(out_dic),
      \(x) case_when(x == "Yes" ~ 1,
                     x == "No"  ~ 0,
                     TRUE       ~ NA_real_),
      .names = "{.col}_poi"
    )
  )


```

```{r dsw}
# We need this dataset for comparative weighted analyses

ds_w <- 
  
  ds |> 
  drop_na(w_country_work_sex)

```

```{r var labs}
# Apply labels to variables

variable_labels <- readxl::read_excel("ext/var_labels_who_survey.xlsx")

for (i in 1:nrow(variable_labels)) {
  uuid <- variable_labels$Question_uuid[i]
  label <-  variable_labels$Label[i]
  ds[[uuid]] <- sjlabelled::set_label(ds[[uuid]], label)
}

rm(variable_labels,
   i,
   uuid,
   label)


```

# Missing data

```{r miss}
var_names_orig <- names(ds)

names(ds) <- paste0("Item ", seq_along(ds))

var_names <-
  ds |> 
  select(1:95) |> 
  select(-c("Item 1", 
            "Item 2", 
            "Item 3", 
            "Item 4",
            "Item 5",
            "Item 6",
            "Item 7",
            "Item 8",
            "Item 9",
            "Item 11",
            "Item 12",
            "Item 13",
            "Item 14",
            "Item 15",
            "Item 17",
            "Item 18",
            "Item 24",
            "Item 25",
            "Item 28",
            "Item 30",
            "Item 31",
            "Item 66")) |>
  colnames()
  


p <- 
  
  ds |> 
  select(1:95) |> 
  select(-c("Item 1", 
            "Item 2", 
            "Item 3", 
            "Item 4",
            "Item 5",
            "Item 6",
            "Item 7",
            "Item 8",
            "Item 9",
            "Item 11",
            "Item 12",
            "Item 13",
            "Item 14",
            "Item 15",
            "Item 17",
            "Item 18",
            "Item 24",
            "Item 25",
            "Item 28",
            "Item 30",
            "Item 31",
            "Item 66")) |>  
  mutate(
    across(
      everything(),
      ~ as.character(.)
    )
  ) |>
  pivot_longer(
    everything(), 
    names_to = "variable", 
    values_to = "value"
    ) |>  
  mutate(missing = if_else(
    is.na(value), 
    "Missing", 
    "Present")) |> 
  count(variable, missing) |> 
  group_by(variable) |>
  mutate(prop = n / sum(n),
         variable = factor(variable, levels = var_names)) |> 
  filter(missing == "Missing") |>  
  ggplot(aes(x = variable, 
             y = prop)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = scales::percent,
                     limits = c(0, 0.25)) +
  scale_fill_grey(start = 0.8, end = 0.2, name = "Data") +
  theme_minimal() +
  labs(x = "Variable", 
       y = "Percent") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 9))

names(ds) <- var_names_orig

ggsave(plot = p, 
       filename = "missing_data.pdf",
       device = "pdf",
       path = "out/figures/",
       scale = 1.9,
       width = 150,
       height = 110,
       units = "mm",
       dpi = 320
       )

# For supplementary material
ragg::agg_png("out/figures/missing_data.png",
              width = 7,
              height = 5,
              units = "in",
              res = 600,
              scaling = 0.6)

print(p)

dev.off()

rm(p)
```

# Coverage

```{r coverage tbl}
rates_work <-
  
  who_n_loc |> 
  rename(N = value) |>
  mutate(N = ifelse(
    is.na(N),
    0,
    N)) |> 
  select(-year, -category)

country_rates_work <-
  
  ds |>
  filter(na_perc < 90) |>
  group_by(loc_2, work_2)  |>
  summarise(n = n(),
            .groups = 'drop') |>
  drop_na() |>
  left_join(rates_work) |>
  mutate(rates_100 = round(n / N * 100, 1)) |>
  pivot_wider(
    names_from = work_2,
    values_from = c(n, N, rates_100)
  ) |> 
  select(loc_2, ends_with("_Doctor"), ends_with("_Nurse"))

rates_tbl <- 
  
  country_rates_work |>
  flextable() |> 
  add_header_row(
    values = c("", "Doctor", "Nurse"),
    colwidths = c(1, 3, 3) 
  ) |> 
  set_header_labels(
    loc_2 = "Country",
    n_Nurse = "n (sample)",
    N_Nurse = "N (Population)",
    rates_100_Nurse = "Coverage (%)",
    n_Doctor = "n (sample)",
    N_Doctor = "N (Population)",
    rates_100_Doctor = "Coverage (%)"
  ) |> 
  align(
    align = "center",
    part = "all"
  )

save_as_docx(rates_tbl, path = "out/tables/rates_tbl.docx")
```


```{r n and coverage}

# This chunk should run without issue in Mac 
  
install.packages("rnaturalearthdata")

world <- rnaturalearth::ne_countries(scale = "medium", returnclass = "sf")

# All professionals


rates_map_work <-
  
  who_n_loc |> 
  rename(N = value) |>
  mutate(N = ifelse(
    is.na(N),
    0,
    N)) |> 
  select(-year, -category)

country_rates_work <-
  
  ds |>
  filter(na_perc < 90) |>
  group_by(loc_2, work_2)  |>
  summarise(n = n(),
            .groups = 'drop') |>
  drop_na() |>
  left_join(rates_map_work) |>
  mutate(rates_100 = round(n/N * 100, 2))  
  
  

europe <-
  world  |>
  filter(continent == "Europe" | name == "Cyprus") |> 
  select(name, geometry) |>   # Select country name and geometry
  rename(loc_2 = name)        # Rename to match your data frame


europe_prof <-
  cross_join(
  europe,
  tibble(work_2 = c("Doctor", "Nurse")) # Define your categories
  )
  
  
map_data_rates_work <-
  
  europe_prof |> 
  left_join(country_rates_work, by = c("loc_2", "work_2")) |>
  mutate(rates_cat = case_when(
  is.na(rates_100) ~ "Not included in the study",
  is.infinite(rates_100) ~ "Population data not available",
  rates_100 < 1 ~ "Less than 1%",
  rates_100 >= 1 & rates_100 < 5 ~ "Between 1% and 5%",
  rates_100 >= 5 & rates_100 < 10 ~ "Between 5% and 10%",
  rates_100 >= 10 ~ "Above 10%"
  ))


vals <- viridis::viridis(4, option = "D")


color_map <- c(
  "Less than 1%" = vals[4],
  "Between 1% and 5%" = vals[3],
  "Between 5% and 10%" = vals[2],
  "Above 10%" = vals[1],
  "Population data not available" = "grey56",
  "Not included in the study" = "grey90"
  )
  
color_map_gradient <- c(
  "Less than 1%" =  "#EFF3FF",
  "Between 1% and 5%" = "#BDD7E7",
  "Between 5% and 10%" = "#6BAED6",
  "Above 10%" = "#2171B5",
  "Population data not available" = "grey56",
  "Not included in the study" = "grey90"
  )
  
prof_plot_prop <- 
  
  ggplot(map_data_rates_work) +
  geom_sf(aes(fill = fct_relevel(rates_cat, 
                                 "Less than 1%",
                                 "Between 1% and 5%",
                                 "Between 5% and 10%",
                                 "Above 10%",
                                 "Population data not available",
                                 "Not included in the study")),
              color = "white") +  # Fill color based on 'value'
  scale_fill_manual(values = color_map_gradient, drop = FALSE) +
  labs(title = NULL,
       fill = "Proportion of responses") +  
  theme_minimal() +
  theme(
    legend.position = "right",
    legend.key.size = unit(2.5, "mm"), # shrinks colored boxes
    legend.text = element_text(size =6),
    legend.title = element_text(size = 8),
    legend.spacing.x = unit(1, "mm"), # adjusts horizontal space
    plot.title = element_text(hjust = 0.5),
    axis.text = element_blank(),
    axis.title = element_blank(),
    axis.ticks = element_blank(),
    axis.line = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()
  ) +
  xlim(-20, 50) +
  ylim(25, 70) +
    facet_wrap(~work_2, nrow = 1)

print(prof_plot_prop)

ggsave(filename = "map.pdf",
       plot = prof_plot_prop,
       path = "out/figures/",
       width = 210,
       height = 150,
       units = "mm",
       dpi = 320
       )

ragg::agg_png("out/figures/map.png",
              width = 7,
              height = 3,
              units = "in",
              res = 600,
              scaling = 1)

print(prof_plot_prop)

dev.off()

```

```{r repr}
ipw_sample <- readRDS("ext/ipw_sample.rds")

repr <- 
  
  ipw_sample |> 
  select(loc_2, work_2, scdm_2_rec, age_eurostat, N, perc_country_work_sex) |> 
  full_join(who_ipw_population, 
            by = c("loc_2", "work_2", "scdm_2_rec", "age_eurostat")) |> 
  select(-c("N_year", "perc_eu", "perc_country", "perc_country_work")) |> 
  
  # calculate numeric difference between proportions
  
  mutate(diff = abs(perc_country_work_sex.x - perc_country_work_sex.y)) |> 
  mutate(
    across(
      contains("perc_"),
      ~round(., digits = 0)
      ),
    across(
      contains(".x"),
      ~format(replace_na(., 0), big.mark = ",", trim = TRUE)
      ),
    across(
      ends_with(".y"),
      ~if_else(
        is.na(.x),
        "-",
        format(.x, big.mark = ",", trim = TRUE, scientific = FALSE)
        )
      )
  ) |> 
  mutate(
    n = paste0(N.x, " (", perc_country_work_sex.x, "%)"),
    N = if_else(
      N.y == "-",
      "-",
      paste0(N.y, " (", perc_country_work_sex.y, "%)"))
    ) |> 
  mutate(samp_pop = paste0(n, " / ", N)) |> 
  select(1:4, samp_pop, diff) |> 
  
  # pivot for gt
  
  pivot_wider(
    names_from = c(work_2, scdm_2_rec),
    values_from = c(samp_pop, diff),
    names_glue = "{work_2}_{scdm_2_rec}_{.value}"
    )

  

# Identify column prefixes and remove _samp_pop
col_prefixes <- 
  names(repr) |> 
  str_subset("_samp_pop$") |> 
  str_remove("_samp_pop$")


repr_table <- 
  
  repr |> 
  gt(rowname_col = "age_eurostat",
     groupname_col = "loc_2") |>
  tab_options(row_group.as_column = TRUE)


# loop through prefixes to apply styles

repr_table <- 
  
  col_prefixes |> 
  reduce(function(data, prefix) {
    
    target_col <- paste0(prefix, "_samp_pop")
    logic_col <- paste0(prefix, "_diff")
    
    data |> 
      tab_style(
        style = cell_fill(color = "#EFF3FF"),
        locations = cells_body(
          columns = all_of(target_col),
          rows = .data[[logic_col]] <= 5
        )
      ) |> 
      tab_style(
        style = cell_fill(color = "#BDD7E7"),
        locations = cells_body(
          columns = all_of(target_col),
          rows = .data[[logic_col]] > 5
        )
      ) |> 
      tab_style(
        style = cell_fill(color = "#6BAED6"),
        locations = cells_body(
          columns = all_of(target_col),
          rows = .data[[logic_col]] > 10
        )
      ) |> 
      tab_style(
        style = cell_fill(color = "#2171B5"),
        locations = cells_body(
          columns = all_of(target_col),
          rows = .data[[logic_col]] > 15
        )
      )
  }, .init = repr_table)

repr_table <- 
  
  repr_table |> 
  tab_spanner(
    label = md("**Doctor**"),
    columns = starts_with("Doctor")
  ) |>
  tab_spanner(
    label = md("**Nurse**"),
    columns = starts_with("Nurse")
  ) |>
  cols_label(
    Doctor_Female_samp_pop = md("**Female**"),
    Doctor_Male_samp_pop = md("**Male**"),
    Nurse_Female_samp_pop = md("**Female**"),
    Nurse_Male_samp_pop = md("**Male**"),
  ) |> 
  cols_hide(
    columns = ends_with("_diff")
    ) |> 
  cols_align(
    align = "center",
    columns = contains(c("Doctor", "Nurse"))
  ) |> 
  tab_footnote(
    locations = cells_column_labels(contains(c("Doctor", "Nurse"))),
    footnote = "n (Sample %) / N (Population %)"
    ) |> 
  tab_footnote(
    footnote = md("*Cell colour defined by absolute difference between sample and population proportions.*")
    ) 

gtsave(data = repr_table, filename = "out/tables/represent.docx")


```

# Sociodemographic characteristics

```{r scdm all, eval = FALSE}
# scdm by type of job and gender

t1 <- 
  
  ds |> 
  select(all_of(c(scdm, covs_1))) |> 
  tbl_strata(
    strata = work_2,
    .tbl_fun = ~ tbl_summary(.x, by = scdm_2_rec) |> 
      add_overall()
  ) |> 
  as_flex_table()

save_as_docx(
  t1, 
  path = "out/tables/scdm_tbl_uw.docx" 
    )

# scdm by type of job and gender, by country (one long table)

countries <- 
  ds |>
  drop_na(loc_2) |>
  pull(loc_2) |>
  levels()

t_long <- 
  map(countries, function(ctry) {
    ds |>
      filter(loc_2 == ctry) |>
      select(all_of(c(scdm, covs_1))) |>
      tbl_strata(
        strata = work_2,
        .tbl_fun = ~ tbl_summary(
          .x,
          by = scdm_2_rec,
          missing = "no"
        ) |> 
          add_overall() |>
        add_n(),
        modify_header(all_stat_cols() ~ "{level}"),
        quiet = TRUE
      )
  }) |>
  tbl_stack(
    group_header = countries,
    quiet = TRUE
  ) |>
  as_flex_table()

save_as_docx(
  t_long, 
  path = "out/tables/scdm_tbl_uw_ctry.docx" 
    )

```

```{r scdm-tbl-w, eval = FALSE}

ds_w <- 
  
  ds |> 
  drop_na(w_country_work_sex)
  
svy_design <- 
  
  svydesign(ids = ~user_id,
            weights = ~w_country_work_sex,
            data = ds_w)

my_label_formulas <- list(
  scdm_1_rec ~ "Age groups",
  scdm_5_dic ~ "Having children in the household",
  scdm_6     ~ "Household income",
  work_1     ~ "Ongoing post-graduate training",
  work_3_rec ~ "Length of service",
  work_4_dic ~ "Number of jobs",
  work_5_rec ~ "Healthcare setting",
  work_7 ~ "Sector type"
  
  # Add any other variables in 'scdm' vector here
)

tbl_vars <- union(scdm, covs_1)

tbl_vars <- setdiff(tbl_vars, "work_2")

# We do this first so we can use them in the labels later
n_counts <- 
  ds_w |> 
  count(work_2, scdm_2_rec)

n_total_counts <- 
  ds_w |> 
  count(work_2) # For the Overall headers

get_n_style <- 
  function(w, g = NULL) {
    
    if(is.null(g)) {
      
      val <- 
        n_total_counts |> 
        filter(work_2 == w) |> 
        pull(n)
      
      } else {
        
        val <- 
          n_counts |> 
          filter(work_2 == w, 
                 scdm_2_rec == g) |> 
          pull(n)
  }
  style_number(val)
}

# Doctors
n_doc_all <- get_n_style("Doctor")
n_doc_m   <- get_n_style("Doctor", "Male")
n_doc_f   <- get_n_style("Doctor", "Female")

# Nurses
n_nur_all <- get_n_style("Nurse")
n_nur_m   <- get_n_style("Nurse", "Male")
n_nur_f   <- get_n_style("Nurse", "Female")


# Summaries (With add_overall) 

doc_n <- 
  ds_w |> 
  filter(work_2 == "Doctor") |>
  tbl_summary(
    by = scdm_2_rec,
    include = all_of(tbl_vars),
    statistic = list(all_categorical() ~ "{n}"),
    missing = "no"
  ) |>
  add_overall() |> # Adds stat_0
  modify_header(all_stat_cols() ~ "**{level}** (n)") 

doc_p <- 
  subset(svy_design, work_2 == "Doctor") |>
  tbl_svysummary(
    by = scdm_2_rec,
    include = all_of(tbl_vars),
    statistic = list(all_categorical() ~ "({p}%)"),
    missing = "no",
    label = my_label_formulas
  ) |>
  add_overall() |> # Adds stat_0
  modify_header(all_stat_cols() ~ "**{level}** (%)")

doc_merged <- 
  tbl_merge(list(doc_n, doc_p), 
            tab_spanner = FALSE)


nur_n <- 
  ds_w |> 
  filter(work_2 == "Nurse") |>
  tbl_summary(
    by = scdm_2_rec,
    include = all_of(tbl_vars),
    statistic = list(all_categorical() ~ "{n}"),
    missing = "no"
  ) |>
  add_overall() |>
  modify_header(all_stat_cols() ~ "**{level}** (n)")

nur_p <- 
  subset(svy_design, work_2 == "Nurse") |>
  tbl_svysummary(
    by = scdm_2_rec,
    include = all_of(tbl_vars),
    statistic = list(all_categorical() ~ "({p}%)"),
    missing = "no",
    label = my_label_formulas
  ) |>
  add_overall() |>
  modify_header(all_stat_cols() ~ "**{level}** (%)")

nur_merged <- 
  tbl_merge(list(nur_n, nur_p), 
            tab_spanner = FALSE)


# Merge 

scdm_tbl_w <- 
  
  tbl_merge(
    list(doc_merged, nur_merged),
    tab_spanner = c("**Doctor**", "**Nurse**")
  ) |>  
  modify_footnote(everything() ~ NA) 

# Column merging

# LOGIC:
# stat_0 = Overall
# stat_1 = Female (Alphabetical F < M)
# stat_2 = Male
#
# Suffixes added by tbl_merge:
# _1 = Counts (from the first merge n+p)
# _2 = Props  (from the first merge n+p)
# _1 (outer) = Doctors
# _2 (outer) = Nurses


# Column merging inside gtsummary
scdm_tbl_w_flex <- 
  scdm_tbl_w |>
  
  # Merge the n and % columns directly in the underlying dataframe
  modify_table_body(~ .x |>
    mutate(
      stat_0_1_1 = ifelse(is.na(stat_0_1_1), NA, paste(stat_0_1_1, stat_0_2_1)),
      stat_1_1_1 = ifelse(is.na(stat_1_1_1), NA, paste(stat_1_1_1, stat_1_2_1)),
      stat_2_1_1 = ifelse(is.na(stat_2_1_1), NA, paste(stat_2_1_1, stat_2_2_1)),
      
      stat_0_1_2 = ifelse(is.na(stat_0_1_2), NA, paste(stat_0_1_2, stat_0_2_2)),
      stat_1_1_2 = ifelse(is.na(stat_1_1_2), NA, paste(stat_1_1_2, stat_1_2_2)),
      stat_2_1_2 = ifelse(is.na(stat_2_1_2), NA, paste(stat_2_1_2, stat_2_2_2))
    )
  ) |>
  
  # Hide the now-redundant percentage columns
  modify_column_hide(
    columns = c("stat_0_2_1", "stat_1_2_1", "stat_2_2_1", 
                "stat_0_2_2", "stat_1_2_2", "stat_2_2_2")
  ) |>
  
  # Label headers (using \n instead of <br> for Word compatibility)
  modify_header(
    stat_0_1_1 = glue::glue("**Overall**\nN = {n_doc_all}"), 
    stat_1_1_1 = glue::glue("**Female**\nN = {n_doc_f}"), 
    stat_2_1_1 = glue::glue("**Male**\nN = {n_doc_m}"),
    
    stat_0_1_2 = glue::glue("**Overall**\nN = {n_nur_all}"),
    stat_1_1_2 = glue::glue("**Female**\nN = {n_nur_f}"),
    stat_2_1_2 = glue::glue("**Male**\nN = {n_nur_m}")
  ) |>
  
  # Add the footnote correctly
  modify_footnote(
    c(stat_0_1_1, stat_1_1_1, stat_2_1_1, 
      stat_0_1_2, stat_1_1_2, stat_2_1_2) ~ "n (weighted %)"
  ) |>
  
  # Convert to flextable and apply formatting
  as_flex_table() |>
  align(align = "center", part = "all") |> # Centers everything
  align(j = 1, align = "left", part = "all") |> # first column left-aligned
  autofit()       # Adjusts column widths nicely

# View
scdm_tbl_w_flex

save_as_docx(
  scdm_tbl_w_flex, 
  path = "out/tables/scdm_tbl_w.docx" 
    )
)
```

# Prevalences

## Unweighted

```{r exp by prof-gen}
t_exp <- 
  
  ds |> 
  select(all_of(c("work_2", "scdm_2_rec", all_exposures))) |> 
  tbl_strata(
    strata = work_2,
    .tbl_fun = ~ tbl_summary(.x, 
                             by = scdm_2_rec,
                             missing_text = "Missing") |> 
      add_overall()
  ) 

# Group exposures and add labels
t_exp_groups <- 
  
  t_exp |> 
  as_tibble() |> 
  mutate(groupname_col = case_when(
      `**Characteristic**` %in% c("Extended working hours", "Frequent night shifts",
                  "Frequent rotating shifts", "Tight deadlines",
                  "Managing patient and relative anger") ~ "Job demands",
      `**Characteristic**` %in% c("Sexual harassment", "Violent threats",
                  "Physical violence", "Bullying") ~ "Job hazards",
      `**Characteristic**` %in% c("Influence over work", "Influence over work (breaks)",
                  "Colleague support", "Support from superiors") ~ "Job resources",
      `**Characteristic**` %in% c("Work council or union", "Mechanisms for employee feedback",
                  "Workplace stress action plan", "Bullying and harassment protocols", "Violence protocols") ~ "Organisational support structures",
      TRUE ~ NA_character_
  )) |> 
  tidyr::fill(groupname_col, .direction  = "down") |> 
  flextable::as_grouped_data(groups = "groupname_col") |> 
  flextable() |> 
  # CLEAN THE LABELS (Removing asterisks)
  set_header_labels(
    values = setNames(
      gsub("\\*\\*", "", names(as_tibble(t_exp))), 
      names(as_tibble(t_exp))
      )) |> 
  set_header_labels(
    groupname_col = "Group",
    Characteristic = "Exposure"
  )|> 
  # RE-ADD THE SPANNERS (Doctor and Nurse)
  # Values: 1 empty for the labels, then "Doctor" spanning 3, then "Nurse" spanning 3
  add_header_row(
    values = c("", "",  "Doctor", "Nurse"),
    colwidths = c(1, 1, 3, 3) 
  ) |> 
  # 3. SCIENTIFIC STYLING
  align(i = 1, align = "center", part = "header") |> 
  bold(i = 1, part = "header") |> 
  # Formatting the group rows
  bold(i = ~ !is.na(groupname_col), j = 1) |> 
  italic(i = ~ `**Characteristic**` == "Missing", j = 1)



save_as_docx(
  t_exp_groups, 
  path = "out/tables/exp_tbl_uw.docx" 
    )

# By country

exposures_by_loc <- 
  map(all_exposures, ~prevalence_by_loc_tbl(.x, ds))

outcomes_by_loc <- 
  map(out_dic, ~prevalence_by_loc_tbl(.x, ds))

# View the first table to make sure
exposures_by_loc[[1]]
outcomes_by_loc[[1]]

# Save all

output_dir <- "out/tables"

# Save exposure tables
# Loop through the list of tables and save each one
for (i in seq_along(all_exposures)) {
  
  # Get the current table and its corresponding exposure name
  current_table <- exposures_by_loc[[i]]
  exp_name <- all_exposures[i]
  
  # Build the file path (e.g., "out/exposure_tables/work_8_dic.docx")
  file_path <- file.path(output_dir, paste0(exp_name, "_by_loc", ".docx"))
  
  # Export directly to Word
  save_as_docx(current_table, path = file_path)
  
  # Optional: Print a message to the console so you can watch the progress
  message(paste("Saved:", file_path))
}

# Save outcome tables
for (i in seq_along(out_dic)) {
  
  # Get the current table and its corresponding exposure name
  current_table <- outcomes_by_loc[[i]]
  out_name <- out_dic[i]
  
  # Build the file path (e.g., "out/exposure_tables/work_8_dic.docx")
  file_path <- file.path(output_dir, paste0(out_name, "_by_loc", ".docx"))
  
  # Export directly to Word
  save_as_docx(current_table, path = file_path)
  
  # Optional: Print a message to the console so you can watch the progress
  message(paste("Saved:", file_path))
}
```

```{r exp by scdm long}
my_exposures <- c(
  "work_8_dic"  =  "Extended working hours",
  "work_11_dic" =  "Frequent night shifts",
  "work_12_dic" =  "Regular shift work",
  "work_23_dic" =  "Tight deadlines",
  "work_24_dic" =  "Angry patients or relatives",
  "work_30_dic" =  "Sexual harassment",
  "work_31_dic" =  "Violent threats",
  "work_32_dic" =  "Physical violence", 
  "work_33_dic" =  "Bullying",
  "work_19_dic" =  "Influence over work",
  "work_20_dic" =  "Influence over work (breaks)",
  "work_21_dic" =  "Colleague support",
  "work_22_dic" =  "Support from superiors",
  "work_25_dic" =  "Work council or union",
  "work_26_dic" =  "Employee feedback",
  "work_27_dic" =  "Stress action plan",
  "work_28_dic" =  "Harassment protocol",
  "work_29_dic" =  "Violence protocol"
)

scdm_tbl <- union(scdm, covs_1) 
scdm_tbl <- setdiff(scdm_tbl, c("work_2", "scdm_2_rec"))

scdm_order <- c(
  "Overall",
  "Age groups",
  "Having children in the household",
  "Healthcare setting",
  "Household income",
  "Length of service",
  "Number of jobs",
  "Ongoing post-graduate training",
  "Sector type"
)

# Generate the long table
exp_by_scdm_table <- 
  generate_exposure_by_scdm_table(
    data = ds, 
    exposure_list = my_exposures, 
    scdm = scdm_tbl,
    desired_order = scdm_order)

exp_by_scdm_table

save_as_docx(
  exp_by_scdm_table, 
  path = "out/tables/exp_by_scdm_long.docx" )
```

```{r out by prof-gen}
t_out <- 
  
  ds |> 
  select(all_of(c("work_2", "scdm_2_rec", out_dic))) |> 
  tbl_strata(
    strata = work_2,
    .tbl_fun = ~ tbl_summary(.x, by = scdm_2_rec) |> 
      add_overall()
  ) |> 
  as_flex_table()

save_as_docx(
  t_out, 
  path = "out/tables/out_tbl_uw.docx" 
    )
```

```{r out by scdm long}
my_outcomes = c(
  "phq_co" = "Depression",
  "gad_co" = "Anxiety",
  "cage_co" = "Alcohol dependence",
  "suic_idea" = "Suicidal thoughts"
)

scdm_tbl <- union(scdm, covs_1) 
scdm_tbl <- setdiff(scdm_tbl, c("work_2", "scdm_2_rec"))

scdm_order <- c(
  "Overall",
  "Age groups",
  "Having children in the household",
  "Healthcare setting",
  "Household income",
  "Length of service",
  "Number of jobs",
  "Ongoing post-graduate training",
  "Sector type"
)

# Generate the long table
out_by_scdm_table <- 
  generate_outcome_by_scdm_table(
    data = ds, 
    outcome_list = my_outcomes, 
    scdm = scdm_tbl,
    desired_order = scdm_order)

out_by_scdm_table

save_as_docx(
  out_by_scdm_table, 
  path = "out/tables/out_by_scdm_long.docx" )
```

## Unweighted vs Weighted

```{r uw vs w exp}
# name variables
all_exposures <- set_names(all_exposures)

# Create named grid
exp_grid <- 
  bind_rows(
    tibble(var = demands_dic, Group = "Demands"),
    tibble(var = hazards_dic, Group = "Hazards"),
    tibble(var = resources_dic, Group = "Resources"),
    tibble(var = protocols_dic, Group = "Structures"),
  ) |> 
  mutate(
    Label = case_when(
      var == "work_8_dic"  ~ "Extended working hours",  
      var == "work_11_dic" ~ "Frequent night shifts",
      var == "work_12_dic" ~ "Regular shift work",
      var == "work_23_dic" ~ "Tight deadlines",
      var == "work_24_dic" ~ "Angry patients or relatives",
      var == "work_30_dic" ~ "Sexual harassment",
      var == "work_31_dic" ~ "Violent threats",
      var == "work_32_dic" ~ "Physical violence", 
      var == "work_33_dic" ~ "Bullying",
      var == "work_25_dic" ~ "Work council or union",
      var == "work_26_dic" ~ "Employee feedback",
      var == "work_27_dic" ~ "Stress action plan",
      var == "work_28_dic" ~ "Harassment protocol",
      var == "work_29_dic" ~ "Violence protocol",
      var == "work_19_dic" ~ "Influence over work",
      var == "work_20_dic" ~ "Influence over work (breaks)",
      var == "work_21_dic" ~ "Colleague support",
      var == "work_22_dic" ~ "Support from superiors",
      TRUE ~ var
    )
  )


# Unweighted

svy_design <- 
  
  svydesign(ids = ~user_id,
            weights = NULL,
            data = ds_w)

uprop_by_job_country <-
  
  imap(
    all_exposures,
    ~ generate_outcome_table(.x, .y)
  )

uprop_by_job_country_percent <- # required for computing diff
  
  map(uprop_by_job_country, ~ .x |> 
        mutate(
          Doc = as.numeric(str_extract(Doc, "^[0-9\\.]+")),
          Nur = as.numeric(str_extract(Nur, "^[0-9\\.]+"))
          )
      )

# Weighted

svy_design <- 
  
  svydesign(ids = ~user_id,
            weights = ~w_country_work_sex,
            data = ds_w)

wprop_by_job_country <-
  
  imap(
    all_exposures,
    ~ generate_outcome_table(.x, .y)
  )

wprop_by_job_country_percent <- # required for computing diff
  
  map(wprop_by_job_country, ~ .x |> 
        mutate(
          Doc = as.numeric(str_extract(Doc, "^[0-9\\.]+")),
          Nur = as.numeric(str_extract(Nur, "^[0-9\\.]+"))
          )
      )

# table

uprop_long <- imap_dfr(
  uprop_by_job_country,
  ~ mutate(.x, outcome = .y)
)

wprop_long <- imap_dfr(
  wprop_by_job_country,
  ~ mutate(.x, outcome = .y)
)

st_w_vs_u_exp <- left_join(
  uprop_long, # No uprev for nurses because we use ds_w
  wprop_long,
  by = c("Variable", "outcome"),
  keep =  
  ) |> 
  rename(
    Country = Variable,
    Doc_unweighted = Doc.x,
    Nur_unweighted = Nur.x,
    Doc_weighted   = Doc.y,
    Nur_weighted   = Nur.y,
    Outcome        = outcome
  ) |> 
  relocate(
    Country, Outcome,
    Doc_unweighted, Doc_weighted,
    Nur_unweighted, Nur_weighted
  ) 

# plot

comparison_tables <- map2(uprop_by_job_country_percent,
                          wprop_by_job_country_percent,
                          ~ left_join(.x, 
                                      .y, 
                                      by = "Variable", 
                                      suffix = c("_unweighted", "_weighted")
                                      ) |> 
                            mutate(
                              Doc_diff = Doc_unweighted - Doc_weighted,
                              Nur_diff = Nur_unweighted - Nur_weighted
                            ) 
)

comparison_tidy_list <- map(
  comparison_tables,
  ~ .x |> 
    select(Variable,
           Doc_unweighted, Doc_weighted,
           Nur_unweighted, Nur_weighted) |> 
    pivot_longer(
      cols = -Variable,
      names_to = c("Job", "Weighted"),
      names_pattern = "(Doc|Nur)_(unweighted|weighted)",
      values_to = "Prevalence"
    ) |> 
    mutate(
      Job = recode(Job,
                   Doc = "Doctor",
                   Nur = "Nurse"),
      Weighted = recode(Weighted,
                        unweighted = "No",
                        weighted = "Yes")
    )
)

comparison_tidy <- imap_dfr(
  comparison_tidy_list,
  ~ mutate(.x, Exposure = .y)
  ) |> 
  select(Exposure, Variable, Job, Weighted, Prevalence)


# Pivot data to join with grid
plot_data <- 
  
  comparison_tidy |> 
  pivot_wider(names_from = Weighted, values_from = Prevalence) |> 
  filter(Variable != "Overall") |>
  left_join(exp_grid, by = c("Exposure" = "var"))


# Plot with function
# Loop over the two professions
for (current_job in c("Doctor", "Nurse")) {
  
  # Filter data for just this job
  job_data <- 
    
    plot_data |> 
    filter(Job == current_job)
  
# Split by group, and loop (grp_data is the data, grp_name is the text)
  iwalk(split(job_data, job_data$Group), function(grp_data, grp_name) {
    
    # Build the plot
    p <- 
      
      ggplot(grp_data, 
             aes(x = No, 
                 y = Yes, 
                 label = Variable)) +
      # facet by clean label
      facet_wrap(vars(Label)) + 
      geom_point() +
      geom_abline(intercept = 0, linetype = "dashed") +
      ggrepel::geom_text_repel(
        size = 4,
        segment.color = "black",
        segment.size = 0.4,
        segment.alpha = 0.8,
        box.padding = 0.8,
        point.padding = 0.5,
        max.overlaps = Inf,
        force = 2
      ) +
      labs(
        x = "Prevalence (no weights)",
        y = "Prevalence (weights)"
      ) +
      theme(
        title = element_text(size = 16),
        axis.title.x = element_text(size = 16),
        axis.title.y = element_text(size = 16),
        strip.text.x = element_text(size = 16),
        strip.text.y = element_text(size = 16),
        axis.text.x = element_text(size = 16),
        axis.text.y = element_text(size = 16)
      ) +
      xlim(0, 100) +
      ylim(0, 100) 
    
    # Define file base names dynamically (e.g., "w_vs_uw_doc_hazards")
    file_base <- 
      paste0("w_vs_uw_", tolower(substring(current_job, 1, 3)), "_", tolower(grp_name))
    
    # Save as PDF
    ggsave(
      filename = paste0(file_base, ".pdf"),
      device = "pdf",
      path = "out/figures/",
      width = 10,  # Adjusted slightly to fit the facets better
      height = 8,
      units = "in",
      dpi = 320,
      scale = 1.5
    )
    
    # Save as PNG (Supplementary material)
    ragg::agg_png(
      paste0("out/figures/", file_base, ".png"),
      width = 10,
      height = 8,
      units = "in",
      res = 600,
      scaling = 0.5
    )
    print(p)
    dev.off()
    
  })
}
```

```{r uw vs w outcomes}
# name variables
out_dic <- set_names(out_dic)

# Unweighted

svy_design <- 
  
  svydesign(ids = ~user_id,
            weights = NULL,
            data = ds_w)

uprop_by_job_country <-
  
  imap(
    out_dic,
    ~ generate_outcome_table(.x, .y)
  )

uprop_by_job_country_percent <- # required for computing diff
  
  map(uprop_by_job_country, ~ .x |> 
        mutate(
          Doc = as.numeric(str_extract(Doc, "^[0-9\\.]+")),
          Nur = as.numeric(str_extract(Nur, "^[0-9\\.]+"))
          )
      )

# Weighted

svy_design <- 
  
  svydesign(ids = ~user_id,
            weights = ~w_country_work_sex,
            data = ds_w)

wprop_by_job_country <-
  
  imap(
    out_dic,
    ~ generate_outcome_table(.x, .y)
  )

wprop_by_job_country_percent <- # required for computing diff
  
  map(wprop_by_job_country, ~ .x |> 
        mutate(
          Doc = as.numeric(str_extract(Doc, "^[0-9\\.]+")),
          Nur = as.numeric(str_extract(Nur, "^[0-9\\.]+"))
          )
      )

# table

uprop_long <- imap_dfr(
  uprop_by_job_country,
  ~ mutate(.x, outcome = .y)
)

wprop_long <- imap_dfr(
  wprop_by_job_country,
  ~ mutate(.x, outcome = .y)
)

st_w_vs_u_exp <- left_join(
  uprop_long, # No uprev for nurses because we use ds_w
  wprop_long,
  by = c("Variable", "outcome"),
  keep =  
  ) |> 
  rename(
    Country = Variable,
    Doc_unweighted = Doc.x,
    Nur_unweighted = Nur.x,
    Doc_weighted   = Doc.y,
    Nur_weighted   = Nur.y,
    Outcome        = outcome
  ) |> 
  relocate(
    Country, Outcome,
    Doc_unweighted, Doc_weighted,
    Nur_unweighted, Nur_weighted
  ) 

# plot

comparison_tables <- map2(uprop_by_job_country_percent,
                          wprop_by_job_country_percent,
                          ~ left_join(.x, 
                                      .y, 
                                      by = "Variable", 
                                      suffix = c("_unweighted", "_weighted")
                                      ) |> 
                            mutate(
                              Doc_diff = Doc_unweighted - Doc_weighted,
                              Nur_diff = Nur_unweighted - Nur_weighted
                            ) 
)

comparison_tidy_list <- map(
  comparison_tables,
  ~ .x |> 
    select(Variable,
           Doc_unweighted, Doc_weighted,
           Nur_unweighted, Nur_weighted) |> 
    pivot_longer(
      cols = -Variable,
      names_to = c("Job", "Weighted"),
      names_pattern = "(Doc|Nur)_(unweighted|weighted)",
      values_to = "Prevalence"
    ) |> 
    mutate(
      Job = recode(Job,
                   Doc = "Doctor",
                   Nur = "Nurse"),
      Weighted = recode(Weighted,
                        unweighted = "No",
                        weighted = "Yes")
    )
)

comparison_tidy <- imap_dfr(
  comparison_tidy_list,
  ~ mutate(.x, Outcome = .y)
  ) |> 
  select(Outcome, Variable, Job, Weighted, Prevalence) |> 
  mutate(Outcome = case_when(
    Outcome == "phq_co" ~ "Depression",
    Outcome == "gad_co" ~ "Anxiety",
    Outcome == "cage_co" ~ "Alcohol dependence",
    Outcome == "suic_idea" ~ "Suicidal thoughts",
    TRUE ~ Outcome)
    )




# Plot now
p_doc <- 
  
  comparison_tidy |> 
  pivot_wider(names_from = Weighted,
              values_from = Prevalence) |> 
  filter(Variable != "Overall",
         Job == "Doctor") |> 
  mutate(Outcome = factor(Outcome, levels = outcome_order)) |> 
  arrange(Outcome) |> 
  ggplot(aes(x = No,
             y = Yes,
             label = Variable)) +
  facet_wrap(vars(Outcome)) +
  geom_point() +
  geom_abline(intercept = 0,linetype = "dashed") +
  ggrepel::  geom_text_repel(
    size = 3,                   # Text sizing
    segment.color = "black",    # Segment line colour
    segment.size = 0.4,         # Line width
    segment.alpha = 0.8,        # Line transparency
    box.padding = 0.8,          # Space between dot and text
    point.padding = 0.5,        # Space between dot and line
    max.overlaps = Inf,         # Do not delete labels
    force = 2                   # Forces labels to separate
  ) +
  labs(x = "Prevalence (no weights)",
       y = "Prevalence (weights)") +
  xlim(0,100) +
  ylim(0,100) 

# Supplementary material

ragg::agg_png("out/figures/w_vs_uw_out_doc.png",
              width = 7,
              height = 5,
              units = "in",
              res = 600,
              scaling = 0.5)

print(p_doc)

dev.off()

ggsave(filename = "w_vs_uw_doc_doc.pdf",
       device = "pdf",
       path = "out/figures/",
       scale = 3,
       width = 110,
       height = 110,
       units = "mm",
       dpi = 320
       )

p_nur <- 
  
  comparison_tidy |> 
  pivot_wider(names_from = Weighted,
              values_from = Prevalence) |> 
  filter(Variable != "Overall",
         Job == "Nurse") |> 
  mutate(Outcome = factor(Outcome, levels = outcome_order)) |> 
  arrange(Outcome) |>
  ggplot(aes(x = No,
             y = Yes,
             label = Variable)) +
  facet_wrap(vars(Outcome)) + 
  geom_point() +
  geom_abline(intercept = 0,linetype = "dashed") +
  ggrepel::  geom_text_repel(
    size = 3,                   
    segment.color = "black",    
    segment.size = 0.4,         
    segment.alpha = 0.8,        
    box.padding = 0.8,          
    point.padding = 0.5,        
    max.overlaps = Inf,         
    force = 2                   
  ) +
  labs(x = "Prevalence (no weights)",
       y = "Prevalence (weights)") +
  xlim(0,100) +
  ylim(0,100)

ggsave(filename = "w_vs_uw_doc_nur.pdf",
       device = "pdf",
       path = "out/figures/",
       scale = 3,
       width = 110,
       height = 110,
       units = "mm",
       dpi = 320
       )

# Supplementary material

ragg::agg_png("out/figures/w_vs_uw_out_nur.png",
              width = 7,
              height = 5,
              units = "in",
              res = 600,
              scaling = 0.5)

print(p_nur)

dev.off()

rm(p_doc, p_nur)
```

## Meta-analysis

### Exposures

```{r exposures ma}
# Generate meta-analyses
exp_ma <- map(all_exposures, run_ma)

# Extract information for table
exp_ma_data <- 
  map2_dfr(all_exposures, exp_ma, function(exposure_name, res) {
    
    ma <- res$ma
    
    # Range of prevalences (calculated as events / n for each)
    ctry_prev <- ma$event / ma$n
    prev_min <- min(ctry_prev, na.rm = TRUE)
    prev_max <- max(ctry_prev, na.rm = TRUE)
    
    # To back-transform Freemn-Turkey (PFT) pooled estimates, "meta" requires
    # the harmonic mean of individual countries' sample sizes.
    n_harm <- length(ma$n) / sum(1 / ma$n)
    
    # Helper function to back-transform estimates
    bt <- function(x) {
      meta::backtransf(x, 
                       sm = "PFT", 
                       n = n_harm)
    }
    
    # Safely extract I^2
    i2_val <- if (is.list(ma$I2)) ma$I2$TE else ma$I2
    
    tibble(
      
      # Name of exposure
      Exposure = exposure_name,
      
      # Pooled estimates (Fixed)
      fixed_est = bt(ma$TE.common),
      fixed_low = bt(ma$lower.common),
      fixed_up = bt(ma$upper.common),
      
      # Pooled estimates (Random)
      random_est = bt(ma$TE.random),
      random_low = bt(ma$lower.random),
      random_up = bt(ma$upper.random),
      
      # Prevalence ranges
      min_prev = prev_min,
      max_prev = prev_max,
      
      # Heterogeneity stats
      I2_pct   = i2_val * 100, # To get a percentage instead of decimals
      I2_low   = ma$lower.I2 * 100,
      I2_up    = ma$upper.I2 * 100,
      
      tau      = ma$tau,
      tau_low  = ma$lower.tau,
      tau_up   = ma$upper.tau,
      
      tau2    = ma$tau2,
      tau2_low  = ma$lower.tau2,
      tau2_up   = ma$upper.tau2
      )
    })

exp_ma_data

```

```{r exp ma tbl}
# Tidy everything
exp_ma_tbl <-
  
  exp_ma_data |> 
  mutate(
    across(
      all_of(2:9),
      \(x) round(x * 100, 1)
      )
    ) |> 
  mutate(
    across(
      contains("I2"),
      \(x) round(x, 1)
    )
  ) |> 
  mutate(
    across(
      contains("tau"),
      \(x) round(x, 3)
    )
  ) |> 
  mutate(
    pooled_fix = paste0(fixed_est, "% (", fixed_low, "-", fixed_up, ")"),
    pooled_rand = paste0(random_est, "% (", random_low, "-", random_up, ")"),
    prev_range = paste0(min_prev, "%-", max_prev, "%"),
    I2 = paste0(I2_pct, "% (", I2_low, "-", I2_up, ")"),
    tau = paste0(tau, " (", tau_low, "-", tau_up), ")",
    tau2 = paste0(tau2, " (", tau2_low, "-", tau2_up, ")")
  ) |> 
  mutate(
    Group = case_when(
      Exposure %in% demands_dic ~ "Job demands",
      Exposure %in% hazards_dic ~ "Job hazards",
      Exposure %in% resources_dic ~ "Job resources",
      Exposure %in% protocols_dic ~ "Organisational support structures",
    ),
    Exposure = case_when(
      Exposure == "work_8_dic"  ~ "Extended working hours",  
      Exposure == "work_11_dic" ~ "Frequent night shifts",
      Exposure == "work_12_dic" ~ "Regular shift work",
      Exposure == "work_23_dic" ~ "Tight deadlines",
      Exposure == "work_24_dic" ~ "Angry patients or relatives",
      Exposure == "work_30_dic" ~ "Sexual harassment",
      Exposure == "work_31_dic" ~ "Violent threats",
      Exposure == "work_32_dic" ~ "Physical violence", 
      Exposure == "work_33_dic" ~ "Bullying",
      Exposure == "work_25_dic" ~ "Work council or union",
      Exposure == "work_26_dic" ~ "Employee feedback",
      Exposure == "work_27_dic" ~ "Stress action plan",
      Exposure == "work_28_dic" ~ "Harassment protocol",
      Exposure == "work_29_dic" ~ "Violence protocol",
      Exposure == "work_19_dic" ~ "Influence over work",
      Exposure == "work_20_dic" ~ "Influence over work (breaks)",
      Exposure == "work_21_dic" ~ "Colleague support",
      Exposure == "work_22_dic" ~ "Support from superiors",
      TRUE ~ Exposure)
    ) |> 
  select(Group, Exposure, pooled_fix, pooled_rand, prev_range, I2, tau, tau2)


# Generate flextable
exp_ma_ft <- 
  
  exp_ma_tbl  |> 
  as_grouped_data(groups = "Group") |>
  flextable() |>
  # Column headers
  set_header_labels(
    Group = "Group",
    Exposure = "Exposure",
    pooled_fix = "Pooled prevalence with 95% CI (Fixed Effects)",
    pooled_rand = "Pooled prevalence with 95% CI (Random Effects)",
    prev_range = "Prevalence Range",
    I2 = "I²",
    tau = "Tau (\u03C4)",
    tau2 = "Tau² (\u03C4²)"
  ) |>
  # Align the text (Left for the exposure names, Center for the data)
  align(j = 1, 
        align = "left", 
        part = "all") |>
  align(j = 2:7, 
        align = "center", 
        part = "all") |>
  # Make the header row bold
  bold(part = "header") |>
  # Automatically adjust column widths to fit the content
  autofit()

save_as_docx(
  exp_ma_ft,
  path = "out/tables/exp_ma_tbl.docx"
)
```

### Outcomes

```{r outcomes}
# Generate meta-analyses
out_ma <- map(out_dic, run_ma)

# Extract information for table
out_ma_data <- 
  map2_dfr(out_dic, out_ma, function(outcome_name, res) {
    
    ma <- res$ma
    
    # Range of prevalences (calculated as events / n for each)
    ctry_prev <- ma$event / ma$n
    prev_min <- min(ctry_prev, na.rm = TRUE)
    prev_max <- max(ctry_prev, na.rm = TRUE)
    
    # To back-transform Freemn-Turkey (PFT) pooled estimates, "meta" requires
    # the harmonic mean of individual countries' sample sizes.
    n_harm <- length(ma$n) / sum(1 / ma$n)
    
    # Helper function to back-transform estimates
    bt <- function(x) {
      meta::backtransf(x, 
                       sm = "PFT", 
                       n = n_harm)
    }
    
    # Safely extract I^2
    i2_val <- if (is.list(ma$I2)) ma$I2$TE else ma$I2
    
    tibble(
      
      # Name of outcome
      outcome = outcome_name,
      
      # Pooled estimates (Fixed)
      fixed_est = bt(ma$TE.common),
      fixed_low = bt(ma$lower.common),
      fixed_up = bt(ma$upper.common),
      
      # Pooled estimates (Random)
      random_est = bt(ma$TE.random),
      random_low = bt(ma$lower.random),
      random_up = bt(ma$upper.random),
      
      # Prevalence ranges
      min_prev = prev_min,
      max_prev = prev_max,
      
      # Heterogeneity stats
      I2_pct   = i2_val * 100, # To get a percentage instead of decimals
      I2_low   = ma$lower.I2 * 100,
      I2_up    = ma$upper.I2 * 100,
      
      tau      = ma$tau,
      tau_low  = ma$lower.tau,
      tau_up   = ma$upper.tau,
      
      tau2    = ma$tau2,
      tau2_low  = ma$lower.tau2,
      tau2_up   = ma$upper.tau2
      )
    })

out_ma_data

```

```{r out ma tbl}
# Tidy everything
out_ma_tbl <-
  
  out_ma_data |> 
  mutate(
    across(
      all_of(2:9),
      \(x) round(x * 100, 1)
      )
    ) |> 
  mutate(
    across(
      contains("I2"),
      \(x) round(x, 1)
    )
  ) |> 
  mutate(
    across(
      contains("tau"),
      \(x) round(x, 3)
    )
  ) |> 
  mutate(
    pooled_fix = paste0(fixed_est, "% (", fixed_low, "-", fixed_up, ")"),
    pooled_rand = paste0(random_est, "% (", random_low, "-", random_up, ")"),
    prev_range = paste0(min_prev, "%-", max_prev, "%"),
    I2 = paste0(I2_pct, "% (", I2_low, "-", I2_up, ")"),
    tau = paste0(tau, " (", tau_low, "-", tau_up), ")",
    tau2 = paste0(tau2, " (", tau2_low, "-", tau2_up, ")")
  ) |>
  mutate(
    outcome = case_when(
      outcome == "phq_co" ~ "Depression",
      outcome == "gad_co" ~ "Anxiety",
      outcome == "cage_co" ~ "Alcohol dependence",
      outcome == "suic_idea" ~ "Suicidal thoughts",
      TRUE ~ outcome)
    ) |> 
  select(outcome, pooled_fix, pooled_rand, prev_range, I2, tau, tau2)


# Generate flextable
out_ma_ft <- 
  
  out_ma_tbl  |> 
  flextable() |>
  # Column headers
  set_header_labels(
    outcome = "Outcome",
    pooled_fix = "Pooled prevalence with 95% CI (Fixed Effects)",
    pooled_rand = "Pooled prevalence with 95% CI (Random Effects)",
    prev_range = "Prevalence Range",
    I2 = "I²",
    tau = "Tau (\u03C4)",
    tau2 = "Tau² (\u03C4²)"
  ) |>
  # Align the text (Left for the exposure names, Center for the data)
  align(j = 1, 
        align = "left", 
        part = "all") |>
  align(j = 2:7, 
        align = "center", 
        part = "all") |>
  # Make the header row bold
  bold(part = "header") |>
  # Automatically adjust column widths to fit the content
  autofit()

save_as_docx(
  out_ma_ft,
  path = "out/tables/out_ma_tbl.docx"
)
```

## Weighted

```{r exp and out w tables}

svy_design <- 
  
  svydesign(
    ids = ~1,
    data = ds_w,
    weights = ~w_country_work_sex
  )

# Exposures
table_all_exp_w <- gen_w_exp_tbl(exposure_metadata)
  
gtsave(table_all_exp_w,
       "out/tables/all_exp_tbl_w.docx")

# Outcomes
out_order_names <- 
  c("Probable depression (PHQ-9)",
    "Probable anxiety (GAD-7)",
    "Probable alcohol dependence disorder (CAGE)",
    "Passive suicide thoughts (Item 9 of PHQ-9)")

table_all_out_w <- gen_w_out_tbl(out_dic)
  
gtsave(table_all_out_w,
       "out/tables/all_out_tbl_w.docx")

```

## Sensitivity analyses

```{r out by n}
ds_sens <- 
  
  ds |> 
  right_join(country_rates_work, by = c("loc_2", "work_2")) |> 
  mutate(N = if_else(N == 0, NA_integer_, N),
         rates_100 = if_else(is.na(N), NA_real_, rates_100))

ors <- run_out_by_n_bin(ds_sens, out_dic)
prs <- run_out_by_n_poi(ds_sens, out_poisson)

#expl

x <- 
  
  glm(phq_co ~ rates_100,
      data = ds_sens,
      family = binomial(link = "logit"),
      weights = N
      )

summary(x)
exp(coef(x))
```

# GLM Models

## Aggregated

```{r exp-out assoc prep}

# define outcomes, exposures, covariates

out_poisson

# already defined

demands_dic

hazards_dic

protocols_dic

resources_dic

covs_1

covs_2

# define strata

profs <- levels(ds$work_2)



# maps

covariate_map <- list(
  "base_covs" = covs_1
)


# Create grid
tasks <- expand_grid(
  Outcome = out_poisson,
  Family = "poisson",          
  Exposure = all_exposures,
  Covar_Key = "base_covs",      
  profession = profs            
)


tasks_all <- expand_grid(
  Outcome = out_poisson,
  Family = "poisson",
  Exposure = all_exposures,
  Covar_Key = "base_covs",
  profession = "All"
)

# Needed to run more than one model at once
library(furrr)
library(future)

# Set up parallel processing (uses all cores minus whatever you want)
# FIXME: MODIFY CORES ACCORDINGLY
plan(multisession, workers = availableCores() - 2)
  
```

```{r exp-out all}
exp_out_all <- future_pmap(list(
  tasks_all$Outcome,
  tasks_all$Family,
  tasks_all$Exposure,
  tasks_all$Covar_Key,
  tasks_all$profession
), function(outcome, family, exposure, cov_key, prof) {
  
  message(paste("Processing:", outcome, "x", exposure, "in", prof))

  res_crude <- run_crude_glm(
    data = ds,
    outcome_var = outcome,
    exposure_var = exposure,
    profession = prof,
    cluster_var = covs_2,
    family_type = family
  )

  res_adj <- run_adj_glm(
    data = ds,
    outcome_var = outcome,
    exposure_var = exposure,
    profession = prof,
    family_type = family,
    cluster_var = covs_2,
    confounder_list = covariate_map[[cov_key]],
    model_label = "Adjusted"
  )

  # Combine internally
  
  row_multilevel <- 
    
    bind_rows(
    res_crude$multilevel,
      res_adj$multilevel
    )
  
  row_robust <- 
    
    bind_rows(
    res_crude$robust,
      res_adj$robust
    )
  
  # return as clean pair
  
  return(list(
    multilevel = row_multilevel,
    robust     = row_robust
  ))
}, .options = furrr_options(seed = TRUE))


# Unzip and combine

glm_multilevel_df <- map_dfr(exp_out_all, "multilevel")

glm_robust_df <- map_dfr(exp_out_all, "robust")


# Save

saveRDS(glm_multilevel_df, "out/models/summary/glm_multilevel_df.rds")
saveRDS(glm_robust_df, "out/models/summary/glm_robust_df.rds")
```

## Profession

```{r exp-out by job}

exp_out_job <- future_pmap(list(
  tasks$Outcome,
  tasks$Family,
  tasks$Exposure,
  tasks$Covar_Key,
  tasks$profession
), function(outcome, family, exposure, cov_key, prof) {
  
  message(paste("Processing:", outcome, "x", exposure, "in", prof))
  
  res_crude <- run_crude_glm(
    data = ds,
    outcome_var = outcome,
    exposure_var = exposure,
    profession = prof,
    cluster_var = covs_2,
    family_type = family
  )


  res_adj <- run_adj_glm(
    data = ds,
    outcome_var = outcome,
    exposure_var = exposure,
    profession = prof,
    family_type = family,
    cluster_var = covs_2,
    confounder_list = covariate_map[[cov_key]],
    model_label = "Adjusted"
  )
  
  
  # Combine internally
  
  row_multilevel <- 
    
    bind_rows(
      res_crude$multilevel,
      res_adj$multilevel
    )
  
  row_robust <- 
    
    bind_rows(
      res_crude$robust,
      res_adj$robust
    )
  
  # return as clean pair
  
  return(list(
    multilevel = row_multilevel,
    robust     = row_robust
  ))
}, .options = furrr_options(seed = TRUE))

# Unzip and combine

glm_multilevel_df_by_job <- map_dfr(exp_out_job, "multilevel")

glm_robust_df_by_job <- map_dfr(exp_out_job, "robust")


# Save

saveRDS(glm_multilevel_df_by_job, "out/models/summary/glm_multilevel_df_by_job.rds")
saveRDS(glm_robust_df_by_job, "out/models/summary/glm_robust_df_by_job.rds")
```

## SE ratios

```{r se ratios}
# all, aggregated

glm_multilevel_df <- readRDS("out/models/summary/glm_multilevel_df.RDS")
glm_robust_df <- readRDS("out/models/summary/glm_robust_df.RDS")

glm_se_ratios <-
  
  glm_multilevel_df |>
  select(Outcome, Exposure, Profession, Adjustment, beta, PR, SE) |> 
  rename(pr = PR,
         se_ml = SE) |> 
  left_join(glm_robust_df |> 
              select(Outcome, Exposure, Profession, Adjustment, SE),
            by = c("Outcome", "Exposure", "Profession", "Adjustment")) |> 
  rename(se_rob = SE) |> 
  mutate(se_ratio = se_rob / se_ml) |> 
  mutate(
    Exposure = case_when(
      Exposure == "work_21_dic" ~ "Colleague support",
      Exposure == "work_22_dic" ~ "Support from superiors",
      Exposure == "work_31_dic" ~ "Violent threats",
      Exposure == "work_32_dic" ~ "Physical violence",
      Exposure == "work_30_dic" ~ "Sexual harassment",
      Exposure == "work_33_dic" ~ "Bullying",
      Exposure == "wb_wami_1_dic" ~ "Meaning in work",
      Exposure == "wb_wami_2_dic" ~ "Purpose in work",
      TRUE ~ Exposure),
    Outcome = case_when(
      Outcome == "phq_co_poi" ~ "Depression",
      Outcome == "gad_co_poi" ~ "Anxiety",
      Outcome == "cage_co_poi" ~ "Alcohol dependence",
      Outcome == "suic_idea_poi" ~ "Suicidal thoughts",
      TRUE ~ Outcome
    )
  )

# plot

se_plot <- 
  
  glm_se_ratios |> 
  mutate(Outcome = factor(Outcome, levels = outcome_order)) |> 
  arrange(Outcome) |> 
  ggplot(aes(x = se_ml,
             y = se_rob, 
             colour = Adjustment,
             shape = Adjustment)) +
  geom_abline(
    intercept = 0,
    slope = 1,
    linetype = "dashed",
    colour = "grey50"
  ) +
  geom_point(
    size = 2.5,
    alpha = 0.8
  ) +
  scale_colour_grey() +
  labs(
    x = "Model-based SE (multilevel Poisson)",
    y = "Cluster-robust SE (fixed-effects Poisson)",
    colour = "Outcome",
    title = "Comparison of standard errors across inferential frameworks"
    ) +
  theme_minimal(base_size = 12) +
  theme(
    legend.position = "bottom"
  ) +
  facet_wrap(~Outcome) 


ragg::agg_png("out/figures/se_ratios.png",
              width = 7,
              height = 5,
              units = "in",
              res = 600,
              scaling = 0.5)

print(se_plot)

dev.off()

beta_plot <- 
  
  glm_multilevel_df |>
  select(Outcome, Exposure, Adjustment, beta) |>
  mutate(
    Outcome = case_when(
      Outcome == "phq_co_poi" ~ "Depression",
      Outcome == "gad_co_poi" ~ "Anxiety",
      Outcome == "cage_co_poi" ~ "Alcohol dependence",
      Outcome == "suic_idea_poi" ~ "Suicidal thoughts",
      TRUE ~ Outcome
    )
  ) |> 
  left_join(glm_robust_df |> 
              select(Outcome, Exposure, Adjustment, beta) |> 
               mutate(Outcome = case_when(
                 Outcome == "phq_co_poi" ~ "Depression",
                 Outcome == "gad_co_poi" ~ "Anxiety",
                 Outcome == "cage_co_poi" ~ "Alcohol dependence",
                 Outcome == "suic_idea_poi" ~ "Suicidal thoughts",
                 TRUE ~ Outcome)),
            by = c("Outcome", "Exposure", "Adjustment")
            ) |>
    rename(beta_ml = beta.x,
           beta_rob = beta.y) |> 
  mutate(Outcome = factor(Outcome, levels = outcome_order)) |> 
  arrange(Outcome) |> 
  ggplot(aes(x = beta_ml,
             y = beta_rob, 
             colour = Adjustment,
             shape = Adjustment)) +
  geom_abline(
    intercept = 0,
    slope = 1,
    linetype = "dashed",
    colour = "grey50"
  ) +
  geom_point(
    size = 2.5,
    alpha = 0.8
  ) +
  scale_colour_grey() +
  labs(
    x = "Model-based beta (multilevel Poisson)",
    y = "Cluster-robust beta (fixed-effects Poisson)",
    title = "Comparison of betas across inferential frameworks"
    ) +
  theme_minimal(base_size = 12) +
  theme(
    legend.position = "bottom"
  ) +
  facet_wrap(~Outcome)


# Supplementary material

ragg::agg_png("out/figures/betas.png",
              width = 7,
              height = 5,
              units = "in",
              res = 600,
              scaling = 0.5)

print(beta_plot)

dev.off()
```

## Tables of results

```{r glm results tbl agg}
# Results with ML estimator + SE robust

glm_results <-
  
  glm_multilevel_df |> 
  select(Outcome, Exposure, Adjustment, beta, PR, CI_l, CI_u) |> 
  rename(beta_ml = beta,
         PR_ml = PR,
         CI_l_ml = CI_l,
         CI_u_ml = CI_u) |> 
  left_join(glm_robust_df, 
            by = c("Outcome", "Exposure", "Adjustment")) |> 
  select(-c(Profession, model, SE, N_Analysis)) |> 
  rename(beta_rob = beta,
         PR_rob = PR,
         CI_l_rob = CI_l,
         CI_u_rob = CI_u) |> 
  mutate(Exposure = factor(Exposure, levels = exposure_order)) |> 
  mutate(
    Exposure = case_when(
      Exposure == "work_8_dic"  ~ "Extended working hours",  
      Exposure == "work_11_dic" ~ "Frequent night shifts",
      Exposure == "work_12_dic" ~ "Regular shift work",
      Exposure == "work_23_dic" ~ "Tight deadlines",
      Exposure == "work_24_dic" ~ "Angry patients or relatives",
      Exposure == "work_30_dic" ~ "Sexual harassment",
      Exposure == "work_31_dic" ~ "Violent threats",
      Exposure == "work_32_dic" ~ "Physical violence", 
      Exposure == "work_33_dic" ~ "Bullying",
      Exposure == "work_25_dic" ~ "Work council or union",
      Exposure == "work_26_dic" ~ "Employee feedback",
      Exposure == "work_27_dic" ~ "Stress action plan",
      Exposure == "work_28_dic" ~ "Harassment protocol",
      Exposure == "work_29_dic" ~ "Violence protocol",
      Exposure == "work_19_dic" ~ "Influence over work",
      Exposure == "work_20_dic" ~ "Influence over work (breaks)",
      Exposure == "work_21_dic" ~ "Colleague support",
      Exposure == "work_22_dic" ~ "Support from superiors",
      TRUE ~ Exposure),
    Outcome = case_when(
      Outcome == "phq_co_poi" ~ "Depression",
      Outcome == "gad_co_poi" ~ "Anxiety",
      Outcome == "cage_co_poi" ~ "Alcohol dependence",
      Outcome == "suic_idea_poi" ~ "Suicidal thoughts",
      TRUE ~ Outcome
    ),
    Outcome = factor(Outcome, levels = outcome_order)
  ) |> 
  arrange(Outcome, Exposure) |> 
  mutate(
     Est_CI_ml = sprintf("%.2f (%.2f, %.2f)", PR_ml, CI_l_ml, CI_u_ml),
     Est_CI_rob = sprintf("%.2f (%.2f, %.2f)", PR_rob, CI_l_rob, CI_u_rob)
  )

saveRDS(glm_results, "out/models/summary/glm_results_df.rds")
writexl::write_xlsx(glm_results, "out/models/summary/glm_results_df.xlsx")
  

# Load data

glm_results <- readRDS("out/models/summary/glm_results_df.rds")


ls() |> 
  str_subset("^glm_") |> 
  rm(list = _)

```

```{r glm results tbl job}
glm_multilevel_df_by_job <- readRDS("out/models/summary/glm_multilevel_df_by_job.rds")

glm_robust_df_by_job <- readRDS("out/models/summary/glm_robust_df_by_job.rds")


# Extract ml estimators and rob se

glm_robust_job_se <- 
  
  glm_robust_df_by_job |>  
  select(Outcome, Exposure, Profession, Adjustment, PR, CI_l, CI_u) |> 
  rename(CI_l_rob = CI_l, 
         CI_u_rob = CI_u,
         PR_rob = PR) 

glm_res_job <- 
  
  glm_multilevel_df_by_job |> 
  select(Outcome, Exposure, Adjustment, Profession, beta, PR, CI_l, CI_u) |> 
  rename(beta_ml = beta,
         PR_ml = PR,
         CI_l_ml = CI_l,
         CI_u_ml = CI_u) |> 
  left_join(glm_robust_job_se, 
            by = c("Outcome", "Exposure", "Profession", "Adjustment")) |> 
  mutate(Exposure = factor(Exposure, levels = exposure_order)) |> 
  mutate(
    Exposure = case_when(
      Exposure == "work_8_dic"  ~ "Extended working hours",  
      Exposure == "work_11_dic" ~ "Frequent night shifts",
      Exposure == "work_12_dic" ~ "Regular shift work",
      Exposure == "work_23_dic" ~ "Tight deadlines",
      Exposure == "work_24_dic" ~ "Angry patients or relatives",
      Exposure == "work_30_dic" ~ "Sexual harassment",
      Exposure == "work_31_dic" ~ "Violent threats",
      Exposure == "work_32_dic" ~ "Physical violence", 
      Exposure == "work_33_dic" ~ "Bullying",
      Exposure == "work_19_dic" ~ "Influence over work",
      Exposure == "work_20_dic" ~ "Influence over work (breaks)",
      Exposure == "work_21_dic" ~ "Colleague support",
      Exposure == "work_22_dic" ~ "Support from superiors",
      Exposure == "work_25_dic" ~ "Work council or union",
      Exposure == "work_26_dic" ~ "Employee feedback",
      Exposure == "work_27_dic" ~ "Stress action plan",
      Exposure == "work_28_dic" ~ "Harassment protocol",
      Exposure == "work_29_dic" ~ "Violence protocol",
      TRUE ~ Exposure),
    Outcome = case_when(
      Outcome == "phq_co_poi" ~ "Depression",
      Outcome == "gad_co_poi" ~ "Anxiety",
      Outcome == "cage_co_poi" ~ "Alcohol dependence",
      Outcome == "suic_idea_poi" ~ "Suicidal thoughts",
      TRUE ~ Outcome
    ),
    Outcome = factor(Outcome, levels = outcome_order)
  ) |> 
  arrange(Outcome, Exposure) |> 
  mutate(
     Est_CI_ml = sprintf("%.2f (%.2f, %.2f)", PR_ml, CI_l_ml, CI_u_ml),
     Est_CI_rob = sprintf("%.2f (%.2f, %.2f)", PR_rob, CI_l_rob, CI_u_rob)
  )
  
saveRDS(glm_res_job, "out/models/summary/glm_with_rob_se_job.rds")


# Read data if not loaded
glm_res_job <- readRDS("out/models/summary/glm_with_rob_se_job.rds")


glm_res_job_tbl <- 
  
  glm_res_job |> 
  rename(PR = PR_ml,
         Lower = CI_l_rob,
         Upper = CI_u_rob) |> 
  select(-ends_with(c("_ml", "_rob"))) |> 
  mutate(Est_CI = sprintf("%.2f (%.2f, %.2f)", PR, Lower, Upper))
  
# Generate table
glm_strat_tbl <- 
  make_stratified_table(glm_res_job_tbl, "GLM Multilevel Models with Robust SE")

save_as_docx(glm_strat_tbl,
             path = "out/tables/glm_strat_tbl.docx")
```

## Forest plots

```{r forest plot with labels-adjusted}
# Prep the data
glm_results <- readRDS("out/models/summary/glm_results_df.rds")


glm_res_plot <- 
  
  glm_results |> 
  mutate(
    Group = case_when(
      Exposure %in% names(named_demands) ~ "Job demands",
      Exposure %in% names(named_hazards) ~ "Job hazards",
      Exposure %in% names(named_resources) ~ "Job resources",
      Exposure %in% names(named_protocols) ~ "Organisational support structures",
      TRUE ~ "Other"
      ),
    Group = factor(Group, levels = c("Job demands", "Job hazards", "Job resources", "Organisational support structures"))
  )


plot_data_prepped <- 
  
  glm_res_plot |>
  filter(Adjustment == "Adjusted") |> 
  rename(PR = PR_ml, Lower = CI_l_rob, Upper = CI_u_rob) |> 
  select(-ends_with(c("_ml", "_rob"))) |>
  mutate(
    Outcome = factor(Outcome, levels = outcome_order),
    Exposure = factor(Exposure, levels = exposure_order_named),
    PR_fmt = format(round(PR, 2), nsmall = 1, decimal.mark = "·"),
    Low_fmt = format(round(Lower, 2), nsmall = 1, decimal.mark = "·"),
    Up_fmt = format(round(Upper, 2), nsmall = 1, decimal.mark = "·")
  ) |> 
  arrange(Outcome, Exposure)


# Generate forest plot function
make_forest_plot <- 
  function(df, target_outcome, show_y = TRUE) {
  
  p <- 
    
    df |>
    filter(Outcome == target_outcome) |> 
    ggplot(aes(x = PR, y = fct_rev(Exposure))) +
    geom_point(size = 2.5) +
    geom_linerange(aes(xmin = Lower, xmax = Upper)) +
    geom_text(aes(x = 3, label = paste0(PR_fmt, " (", Low_fmt, "-", Up_fmt, ")")),
              hjust = 1, size = 4) + 
    
    facet_grid(Group ~ ., scales = "free_y", space = "free_y", switch = "y") +
    geom_vline(xintercept = 1, linetype = "dashed") +
    
    scale_x_log10(
      breaks = c(0.2, 0.5, 1, 2),
      labels = scales::label_number(accuracy = 0.1, decimal.mark = "·")
    ) +
    
    labs(y = "", x = "Prevalence Ratio", title = target_outcome) + 
    ggpubr::theme_pubr() + 
    theme(
      plot.title = element_text(hjust = 0.5, face = "bold", size = 12),
      strip.placement = "outside",
      strip.background.y = element_blank(),
      strip.text.y.left = element_text(angle = 0, face = "bold", size = 10),
      axis.text = element_text(size = 10),
      axis.title.x = element_text(size = 10),
      panel.border = element_rect(color = "black", fill = NA, linewidth = 0.5) 
    )
  
  # RULE FOR THE RIGHT-SIDE PLOTS 
  # If show_y is FALSE, we make the y-axis text and Group labels invisible
  if (!show_y) {
    p <- p + theme(
      axis.text.y = element_blank(),      # Hides the exposure names
      axis.ticks.y = element_blank(),     # Hides the little tick marks
      strip.text.y.left = element_blank() # Hides the Group names
    )
  }
  
  return(p)
  }

# Left plots get the labels (show_y = TRUE is the default)
p_dep <- make_forest_plot(plot_data_prepped, "Depression", show_y = TRUE)
p_alc <- make_forest_plot(plot_data_prepped, "Alcohol dependence", show_y = TRUE)

# Right plots hide the labels
p_anx <- make_forest_plot(plot_data_prepped, "Anxiety", show_y = FALSE)
p_sui <- make_forest_plot(plot_data_prepped, "Suicidal thoughts", show_y = FALSE)

# Stitch them together!
final_grid_adj <- (p_dep | p_anx) / (p_alc | p_sui)

# View it
final_grid_adj

ragg::agg_png("out/figures/forest_adjusted.png",
              width = 9,
              height = 7,
              units = "in",
              res = 600,
              scaling = 0.5)

print(final_grid_adj)

dev.off()

ggsave(final_grid_adj, 
       filename = "forest_adjusted.pdf",
       device = "pdf",
       path = "out/figures/",
       scale = 3.5,
       width = 140,
       height = 100,
       units = "mm",
       dpi = 320
       )

rm(final_grid_adj)
```

```{r forest plot with labels-crude}
# Prep the data
plot_data_prepped <- 
  
  glm_res_plot |>
  filter(Adjustment == "Crude") |> 
  rename(PR = PR_ml, Lower = CI_l_rob, Upper = CI_u_rob) |> 
  select(-ends_with(c("_ml", "_rob"))) |>
  mutate(
    Outcome = factor(Outcome, levels = outcome_order),
    Exposure = factor(Exposure, levels = exposure_order_named),
    PR_fmt = format(round(PR, 2), nsmall = 1, decimal.mark = "·"),
    Low_fmt = format(round(Lower, 2), nsmall = 1, decimal.mark = "·"),
    Up_fmt = format(round(Upper, 2), nsmall = 1, decimal.mark = "·")
  ) |> 
  arrange(Outcome, Exposure)


# Generate forest plot function
make_forest_plot <- 
  function(df, target_outcome, show_y = TRUE) {
  
  p <- 
    
    df |>
    filter(Outcome == target_outcome) |> 
    ggplot(aes(x = PR, y = fct_rev(Exposure))) +
    geom_point(size = 2.5) +
    geom_linerange(aes(xmin = Lower, xmax = Upper)) +
    geom_text(aes(x = 4, label = paste0(PR_fmt, " (", Low_fmt, "-", Up_fmt, ")")),
              hjust = 1, size = 4) + 
    
    facet_grid(Group ~ ., scales = "free_y", space = "free_y", switch = "y") +
    geom_vline(xintercept = 1, linetype = "dashed") +
    
    scale_x_log10(
      breaks = c(0.2, 0.5, 1, 2),
      labels = scales::label_number(accuracy = 0.1, decimal.mark = "·")
    ) +
    
    labs(y = "", x = "Prevalence Ratio", title = target_outcome) + 
    ggpubr::theme_pubr() + 
    theme(
      plot.title = element_text(hjust = 0.5, face = "bold", size = 12),
      strip.placement = "outside",
      strip.background.y = element_blank(),
      strip.text.y.left = element_text(angle = 0, face = "bold", size = 10),
      axis.text = element_text(size = 10),
      axis.title.x = element_text(size = 10),
      panel.border = element_rect(color = "black", fill = NA, linewidth = 0.5) 
    )
  
  # === NEW RULE FOR THE RIGHT-SIDE PLOTS ===
  # If show_y is FALSE, we make the y-axis text and Group labels invisible
  if (!show_y) {
    p <- p + theme(
      axis.text.y = element_blank(),      # Hides the exposure names
      axis.ticks.y = element_blank(),     # Hides the little tick marks
      strip.text.y.left = element_blank() # Hides the Group names
    )
  }
  
  return(p)
  }

# Left plots get the labels (show_y = TRUE is the default)
p_dep <- make_forest_plot(plot_data_prepped, "Depression", show_y = TRUE)
p_alc <- make_forest_plot(plot_data_prepped, "Alcohol dependence", show_y = TRUE)

# Right plots hide the labels
p_anx <- make_forest_plot(plot_data_prepped, "Anxiety", show_y = FALSE)
p_sui <- make_forest_plot(plot_data_prepped, "Suicidal thoughts", show_y = FALSE)

# Stitch them together!
final_grid_cr <- (p_dep | p_anx) / (p_alc | p_sui)

# View it
final_grid_cr

ragg::agg_png("out/figures/forest_crude.png",
              width = 9,
              height = 7,
              units = "in",
              res = 600,
              scaling = 0.5)

print(final_grid_cr)

dev.off()


ggsave(final_grid_cr, 
       filename = "forest_crude.pdf",
       device = "pdf",
       path = "out/figures/",
       scale = 3.5,
       width = 140,
       height = 100,
       units = "mm",
       dpi = 320
       )

rm(final_grid_cr)
```

# Dose-response models

-   Main plot demands and depression grid -\> consider stratifying by profession
    if time allows.

## Hazards

```{r dose haz prep}
# define outcomes, exposures, covariates

out # already defined

hazards # already defined

covs_1

# define strata

profs <- levels(ds$work_2) # not used

# maps

covariate_map <- list(
  "base_covs" = covs_1
)


# Create grid
tasks_haz <- expand_grid(
  Outcome = out,
  Family = "gaussian",          
  Exposure = hazards,
  Covar_Key = "base_covs",      
  profession = profs            
)

tasks_dose_haz <- expand_grid(
  Outcome = out,
  Family = "gaussian",
  Exposure = hazards,
  Covar_Key = "base_covs",
  profession = "All"
)

```

```{r dose haz mod}
dose_all_haz <- pmap_dfr(list(
  tasks_dose_haz$Outcome,
  tasks_dose_haz$Family,
  tasks_dose_haz$Exposure,
  tasks_dose_haz$Covar_Key
  ), function(outcome, family, exposure, cov_key) {
  
  message(paste("Processing:", outcome, "&", exposure))
  
  res_crude <- run_glm_dose_emm(
    data = ds,
    outcome_var = outcome,
    exposure_var = exposure,
    confounder_list = NULL,
    model_label = "Crude"
  )
  
  res_adj <- run_glm_dose_emm(
    data = ds,
    outcome_var = outcome,
    exposure_var = exposure,
    confounder_list = covariate_map[[cov_key]],
    model_label = "Adjusted"
  ) 
  
  bind_rows(res_crude, res_adj)
})

dose_all_haz |> # clean and export
  mutate(
    Est_CI = sprintf("%.2f (%.2f, %.2f)", estimate, conf.low, conf.high),
    Exposure_Label = case_when(
      Exposure == "work_31" ~ "Violent threats",
      Exposure == "work_32" ~ "Physical violence",
      Exposure == "work_30" ~ "Sexual harassment",
      Exposure == "work_33" ~ "Bullying",
      TRUE ~ Exposure),
    Outcome = case_when(
      Outcome == "phq_sc"   ~ "PHQ-9 score",
      Outcome == "gad_sc"   ~ "GAD-7 score",
      Outcome == "mh_phq_9" ~ "PHQ-9 suicidality item score",
      Outcome == "cage_sc"  ~ "CAGE score",
      TRUE ~ Outcome
      )
    ) |> 
  as_tibble() |> 
  saveRDS("out/models/summary/dose_all_haz.rds")
```

```{r dose haz tbl}

dose_all_haz <- 
  readRDS("out/models/summary/dose_all_haz.rds")

dose_tbl_haz <- 
  
  dose_all_haz |>
  select(Exposure_Label, Level, Outcome, Model, Est_CI) |>
  pivot_wider(
    names_from  = c(Outcome, Model),
    names_sep   = "|",
    values_from = Est_CI
  ) |>
  select(
    Level,
    Exposure_Label,
    `PHQ-9 score|Crude`,
    `PHQ-9 score|Adjusted`,
    `GAD-7 score|Crude`,
    `GAD-7 score|Adjusted`,
    `CAGE score|Crude`,
    `CAGE score|Adjusted`,
    `PHQ-9 suicidality item score|Crude`,
    `PHQ-9 suicidality item score|Adjusted`
  ) |> 
  
  # creates gt
  
  gt(
    rowname_col   = "Level",
    groupname_col = "Exposure_Label"
  ) |>
  tab_spanner_delim(
    delim = "|"
  ) |>
  cols_label(
    Level = "Level"
  ) |> 
    tab_options(row_group.as_column = FALSE) |> 
    cols_align(align = "center", -Level)

gtsave(dose_tbl_haz, "dose_tbl_haz.docx", "out/tables/")

```

## Demands

```{r dose dem prep}
# define outcomes, exposures, covariates

out # already defined

demands # already defined

covs_1

# define strata

profs <- levels(ds$work_2) # not used

# maps

covariate_map <- list(
  "base_covs" = covs_1
)


# Create grid
tasks_dem <- expand_grid(
  Outcome = out,
  Family = "gaussian",          
  Exposure = demands,
  Covar_Key = "base_covs",      
  profession = profs            
)

tasks_dose_dem <- expand_grid(
  Outcome = out,
  Family = "gaussian",
  Exposure = demands,
  Covar_Key = "base_covs",
  profession = "All"
)

```

```{r dose dem mod}
dose_all_dem <- pmap_dfr(list(
  tasks_dose_dem$Outcome,
  tasks_dose_dem$Family,
  tasks_dose_dem$Exposure,
  tasks_dose_dem$Covar_Key
  ), function(outcome, family, exposure, cov_key) {
  
  message(paste("Processing:", outcome, "&", exposure))
  
  res_crude <- run_glm_dose_emm(
    data = ds,
    outcome_var = outcome,
    exposure_var = exposure,
    confounder_list = NULL,
    model_label = "Crude"
  )
  
  res_adj <- run_glm_dose_emm(
    data = ds,
    outcome_var = outcome,
    exposure_var = exposure,
    confounder_list = covariate_map[[cov_key]],
    model_label = "Adjusted"
  ) 
  
  bind_rows(res_crude, res_adj)
})

dose_all_dem |> # clean and export
  mutate(
    Est_CI = sprintf("%.2f (%.2f, %.2f)", estimate, conf.low, conf.high),
    Exposure_Label = case_when(
      Exposure == "work_8"  ~ "Weekly working hours",
      Exposure == "work_11" ~ "Night shift frequency",
      Exposure == "work_23" ~ "Tight deadlines frequency",
      Exposure == "work_24" ~ "Angry patients frequency",
      TRUE ~ Exposure),
    Outcome = case_when(
      Outcome == "phq_sc"   ~ "PHQ-9 score",
      Outcome == "gad_sc"   ~ "GAD-7 score",
      Outcome == "mh_phq_9" ~ "PHQ-9 suicidality item score",
      Outcome == "cage_sc"  ~ "CAGE score",
      TRUE ~ Outcome
      )
    ) |> 
  as_tibble() |> 
  saveRDS("out/models/summary/dose_all_dem.rds")
```

```{r dose dem tbl}

dose_all_dem <- readRDS("out/models/summary/dose_all_dem.rds")

dose_tbl_dem <- 
  
  dose_all_dem |>
  filter(Exposure != "work_12") |> 
  select(Exposure_Label, Level, Outcome, Model, Est_CI) |>
  pivot_wider(
    names_from  = c(Outcome, Model),
    names_sep   = "|",
    values_from = Est_CI
  ) |>
  select(
    Level,
    Exposure_Label,
    `PHQ-9 score|Crude`,
    `PHQ-9 score|Adjusted`,
    `GAD-7 score|Crude`,
    `GAD-7 score|Adjusted`,,
    `CAGE score|Crude`,
    `CAGE score|Adjusted`,
    `PHQ-9 suicidality item score|Crude`,
    `PHQ-9 suicidality item score|Adjusted`
  ) |> 
  
  # creates gt
  
  gt(
    rowname_col   = "Level",
    groupname_col = "Exposure_Label"
  ) |>
  tab_spanner_delim(
    delim = "|"
  ) |>
  cols_label(
    Level = "Level"
  ) |> 
    tab_options(row_group.as_column = FALSE) |> 
    cols_align(align = "center", -Level)

gtsave(dose_tbl_dem, "dose_tbl_dem.docx", "out/tables/")
```


## Resources

```{r dose res prep}
# define outcomes, exposures, covariates

out # already defined

resources # already defined

covs_1

# define strata

profs <- levels(ds$work_2) # not used

# maps

covariate_map <- list(
  "base_covs" = covs_1
)


# Create grid

tasks_dose_res <- expand_grid(
  Outcome = out,
  Family = "gaussian",
  Exposure = resources,
  Covar_Key = "base_covs",
  profession = "All"
)
```

```{r dose res mod}
dose_all_res <- pmap_dfr(list(
  tasks_dose_res$Outcome,
  tasks_dose_res$Family,
  tasks_dose_res$Exposure,
  tasks_dose_res$Covar_Key
  ), function(outcome, family, exposure, cov_key) {
  
  message(paste("Processing:", outcome, "&", exposure))
  
  res_crude <- run_glm_dose_emm(
    data = ds,
    outcome_var = outcome,
    exposure_var = exposure,
    confounder_list = NULL,
    model_label = "Crude"
  )
  
  res_adj <- run_glm_dose_emm(
    data = ds,
    outcome_var = outcome,
    exposure_var = exposure,
    confounder_list = covariate_map[[cov_key]],
    model_label = "Adjusted"
  ) 
  
  bind_rows(res_crude, res_adj)
})

dose_all_res |> # clean and export
  mutate(
    Est_CI = sprintf("%.2f (%.2f, %.2f)", estimate, conf.low, conf.high),
    Exposure_Label = case_when(
      
      Exposure == "work_19"  ~ "Influence over work",
      Exposure == "work_20" ~ "Influence over work (breaks)",
      Exposure == "work_21" ~ "Colleague support",
      Exposure == "work_22" ~ "Support from superiors",
      TRUE ~ Exposure),
    Outcome = case_when(
      Outcome == "phq_sc"   ~ "PHQ-9 score",
      Outcome == "gad_sc"   ~ "GAD-7 score",
      Outcome == "mh_phq_9" ~ "PHQ-9 suicidality item score",
      Outcome == "cage_sc"  ~ "CAGE score",
      TRUE ~ Outcome
      )
    ) |> 
  as_tibble() |> 
  saveRDS("out/models/summary/dose_all_res.rds")
```

```{r dose res tbl}
dose_all_res <- readRDS("out/models/summary/dose_all_res.rds")

dose_tbl_res <- 
  
  dose_all_res |>
  select(Exposure_Label, Level, Outcome, Model, Est_CI) |>
  pivot_wider(
    names_from  = c(Outcome, Model),
    names_sep   = "|",
    values_from = Est_CI
  ) |>
  select(
    Level,
    Exposure_Label,
    `PHQ-9 score|Crude`,
    `PHQ-9 score|Adjusted`,
    `GAD-7 score|Crude`,
    `GAD-7 score|Adjusted`,
    `CAGE score|Crude`,
    `CAGE score|Adjusted`,
    `PHQ-9 suicidality item score|Crude`,
    `PHQ-9 suicidality item score|Adjusted`
  ) |> 
  
  # creates gt
  
  gt(
    rowname_col   = "Level",
    groupname_col = "Exposure_Label"
  ) |>
  tab_spanner_delim(
    delim = "|"
  ) |>
  cols_label(
    Level = "Level"
  ) |> 
    tab_options(row_group.as_column = FALSE) |> 
    cols_align(align = "center", -Level)

gtsave(dose_tbl_res, "dose_tbl_res.docx", "out/tables/")

```

# Dose-response trends

```{r dose trends prep}
files <- 
  
  list.files(
    path = "out/models/dose/",
    pattern = "\\.rds$",
    full.names = TRUE)

mods <- 
  
  set_names(
  map(files, function(f) {
    x <- readRDS(f)
    x$model   # keep only the lmer model
  }),
  tools::file_path_sans_ext(basename(files))
)


trends <- 
  
  map_df(
  mods,
  function(m) {
    coefs <- summary(m)$coefficients
    lin_term <- grep("\\.L$", rownames(coefs), value = TRUE)[1]
    
    if (!is.na(lin_term)) {
      data.frame(
        term = lin_term,
        estimate = coefs[lin_term, "Estimate"],
        std.error = coefs[lin_term, "Std. Error"]
      )
    }
  },
  .id = "model"
  ) |> 
  separate(
    model, 
    into = c("dose", "out", "exp", "adj"), sep = "_", remove = FALSE
    ) |> 
  mutate(
    term = str_remove(term, "\\..*$"),
    conf.low  = estimate - 1.96 * std.error,
    conf.high = estimate + 1.96 * std.error
    ) |>
  filter(term %in% all_exposures_bis)


saveRDS(trends, "out/models/summary/dose_trends.rds")

rm(mods)
```

```{r dose trends plot}

exposure_order_short <- c(
  "Extended working hours",  
  "Frequent night shifts",
  "Tight deadlines",
  "Angry patients or relatives",
  "Sexual harassment",
  "Violent threats",
  "Physical violence", 
  "Bullying",
  "Influence over work",
  "Influence over work (breaks)",
  "Colleague support",
  "Support from superiors"
  )

# Prep the data
plot_trends_prepped <- 
  
  trends |>
  filter(adj == "adjusted") |> 
  rename(beta = estimate, 
         Lower = conf.low, 
         Upper = conf.high) |> 
  mutate(
    term = case_when(
      term == "work_8"  ~ "Extended working hours",  
      term == "work_11" ~ "Frequent night shifts",
      term == "work_23" ~ "Tight deadlines",
      term == "work_24" ~ "Angry patients or relatives",
      term == "work_30" ~ "Sexual harassment",
      term == "work_31" ~ "Violent threats",
      term == "work_32" ~ "Physical violence", 
      term == "work_33" ~ "Bullying",
      term == "work_19" ~ "Influence over work",
      term == "work_20" ~ "Influence over work (breaks)",
      term == "work_21" ~ "Colleague support",
      term == "work_22" ~ "Support from superiors",
      TRUE ~ term),
    out = case_when(
      out == "dep" ~ "Depression",
      out == "anx" ~ "Anxiety",
      out == "alc" ~ "Alcohol dependence",
      out == "suic" ~ "Suicidal thoughts",
      TRUE ~ out
    ),
    out = factor(out, levels = outcome_order),
    term = factor(term, levels = exposure_order_short),
    beta_fmt = format(round(beta, 2), nsmall = 1, decimal.mark = "·"),
    Low_fmt = format(round(Lower, 2), nsmall = 1, decimal.mark = "·"),
    Up_fmt = format(round(Upper, 2), nsmall = 1, decimal.mark = "·"),
    Group = case_when(
      term %in% names(named_demands) ~ "Job demands",
      term %in% names(named_hazards) ~ "Job hazards",
      term %in% names(named_protocols) ~ "Protocols & procedures",
      term %in% names(named_resources) ~ "Job resources",
      TRUE ~ "Other"
      ),
    Group = factor(Group, levels = c("Job demands", "Job hazards", "Protocols & procedures", "Job resources"))
  ) |> 
  arrange(out, term)

# Generate forest plot function
make_forest_plot_dose <- 
  function(df, target_outcome, show_y = TRUE, is_small_scale = FALSE) {
  
     # Rule for scaling
  if (is_small_scale) {
    # Narrow scale for Alcohol Dependence & Suicidal Thoughts
    my_breaks <- c(-0.5, 0, 0.5) 
    my_text_x <- 0.8  # Pulls the text much closer!
  } else {
    # Wide scale for Depression & Anxiety
    my_breaks <- c(-5, -4, -3, -2, -1, 0, 1, 2, 3, 4, 5)
    my_text_x <- 7
  }
    
  p <- 
    
    df |>
    filter(out == target_outcome) |> 
    ggplot(aes(x = beta,
               y = fct_rev(term))) +
    geom_point(size = 2.5) +
    geom_linerange(aes(xmin = Lower, 
                       xmax = Upper)) +
    geom_text(aes(x = my_text_x, 
                  label = paste0(beta_fmt, " (", Low_fmt, ", ", Up_fmt, ")")),
              hjust = 1, 
              size = 4) + 
    
    facet_grid(Group ~ ., 
               scales = "free", 
               space = "free", 
               switch = "y") +
    geom_vline(xintercept = 0, 
               linetype = "dashed") +
    scale_x_continuous(
      breaks = my_breaks,
      labels = scales::label_number(accuracy = 0.1, decimal.mark = "·")
    ) +
    labs(y = "", 
         x = "Estimate (B)", 
         title = target_outcome) + 
    ggpubr::theme_pubr() + 
    theme(
      plot.title = element_text(hjust = 0.5, face = "bold", size = 12),
      strip.placement = "outside",
      strip.background.y = element_blank(),
      strip.text.y.left = element_text(angle = 0, face = "bold", size = 10),
      axis.text = element_text(size = 10),
      axis.title.x = element_text(size = 10),
      panel.border = element_rect(color = "black", fill = NA, linewidth = 0.5) 
    )
  
 
  
  # Rule for right side plots
  # If show_y is FALSE, we make the y-axis text and Group labels invisible
  if (!show_y) {
    p <- 
      p + theme(
        axis.text.y = element_blank(),      # Hides the exposure names
        axis.ticks.y = element_blank(),     # Hides the little tick marks
        strip.text.y.left = element_blank() # Hides the Group names
    )
  }
  
  return(p)
  }

# Left plots get the labels (show_y = TRUE is the default)
p_dep <- make_forest_plot_dose(plot_trends_prepped, 
                               "Depression", 
                               show_y = TRUE)
p_alc <- make_forest_plot_dose(plot_trends_prepped, 
                               "Alcohol dependence", 
                               show_y = TRUE,
                               is_small_scale = TRUE)

# Right plots hide the labels
p_anx <- make_forest_plot_dose(plot_trends_prepped, 
                               "Anxiety", 
                               show_y = FALSE)
p_sui <- make_forest_plot_dose(plot_trends_prepped, 
                               "Suicidal thoughts", 
                               show_y = FALSE,
                               is_small_scale = TRUE)

# Stitch them together!
forest_dose <- (p_dep | p_anx) / (p_alc | p_sui)

# View it
forest_dose

ragg::agg_png("out/figures/forest_dose.png",
              width = 9,
              height = 7,
              units = "in",
              res = 600,
              scaling = 0.5)

print(forest_dose)

dev.off()

rm(forest_dose)
```

```{r dose haz plot}
# extract Bs and 95% CIs

trends <- readRDS("out/models/summary/dose_trends.rds")

dose_all_haz <- readRDS("out/models/summary/dose_all_haz.rds")

slope_labels <- 
  
  trends |> 
  filter(adj == "adjusted",
         out == "dep") |> 
  mutate(
    Exposure_Label = case_when(
      term == "work_30" ~ "Harassment",
      term == "work_31" ~ "Threats",
      term == "work_32" ~ "Violence",
      term == "work_33" ~ "Bullying",
      TRUE ~ NA_character_
    )
  ) |> 
  filter(term %in% hazards) |> 
  mutate(
    Exposure_Label = factor(Exposure_Label,
                            levels = 
                              c("Harassment", "Threats", "Violence", "Bullying")
                            )
  ) |> 
  arrange(Exposure_Label)
  

dose_plot_haz <-
  
  dose_all_haz |> 
  filter(Model == "Adjusted",
         Outcome == "PHQ-9 score") |> 
  mutate(
    Exposure_Label = case_when(
      Exposure == "work_30" ~ "Sexual harassment",
      Exposure == "work_31" ~ "Violent threats",
      Exposure == "work_32" ~ "Physical violence",
      Exposure == "work_33" ~ "Bullying",
      TRUE ~ Exposure
    ),
    Exposure_Label = factor(
      Exposure_Label,
      levels = c("Sexual harassment",
                 "Violent threats", 
                 "Physical violence",
                 "Bullying")
    )
  ) |> 
  group_by(Exposure_Label) |> 
  mutate(Level = factor(Level, levels = unique(Level))) |> 
  ungroup() |> 
  ggplot(aes(x = Level, 
             y = estimate,
             group = Outcome)) +
  geom_point(size = 2) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high),
                width = 0.1) +
  geom_smooth(method = "lm",
              linewidth = 0.6,
              colour = "black") +
  facet_wrap(~ Exposure_Label, scales = "free_x") +
  labs(
    x = "Exposure level",
    y = "Depressive symptoms (PHQ-9 score, 0-27)"
  ) +
  theme_bw() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "bottom"
  ) +
  scale_y_continuous(limit = c(0,15),
                     breaks = seq(0, 15, by = 1)) 

dose_plot_haz <- 
  
  dose_plot_haz + 
  labs(
    caption = slope_labels |>
      dplyr::mutate(
        foot = paste0(
          Exposure_Label, " slope: B = ", round(estimate, 2),
          " (95% CI ", round(conf.low, 2), " to ", round(conf.high, 2), ")"
        )
      ) |>
      dplyr::summarise(txt = paste(foot, collapse = "; ")) |>
      # Replace all periods with the Unicode midpoint
      dplyr::mutate(txt = gsub("\\.", "\u00B7", txt)) |> 
      dplyr::pull(txt)
  ) +
  theme(plot.caption = element_text(hjust = 0))

ggsave(filename = "dose_response_haz.pdf",
       plot = dose_plot_haz,
       device = "pdf",
       path = "out/figures/",
       scale = 3,
       width = 140,
       height = 70,
       units = "mm",
       dpi = 320
       )

# Supplementary material

ragg::agg_png("out/figures/dose_response_haz.png",
              width = 9,
              height = 7,
              units = "in",
              res = 600,
              scaling = 0.8)

print(dose_plot_haz)

dev.off()
```

```{r dose dem plot}
# extract Bs and 95% CIs

trends <- readRDS("out/models/summary/dose_trends.rds")


dose_all_dem <- readRDS("out/models/summary/dose_all_dem.rds")

slope_labels <- 
  
  trends |> 
  filter(adj == "adjusted",
         out == "dep") |> 
  mutate(
    Exposure_Label = case_when(
      term == "work_8" ~ "Hours",
      term == "work_11" ~ "Nights",
      term == "work_23" ~ "Deadlines",
      term == "work_24" ~ "Angry",
      TRUE ~ NA_character_
    )
  ) |> 
  filter(term %in% demands) |> 
  mutate(
    Exposure_Label = factor(Exposure_Label,
                            levels = c("Hours", "Nights", "Deadlines", "Angry"))
  ) |> 
  arrange(Exposure_Label)
  

dose_plot_dem <- 
  
  dose_all_dem |> 
  filter(Model == "Adjusted",
         Exposure != "work_12",
         Outcome == "PHQ-9 score") |> 
  mutate(
    Exposure_Label = case_when(
      Exposure == "work_8"  ~ "Weekly working hours",
      Exposure == "work_11" ~ "Night shift",
      Exposure == "work_23" ~ "Tight deadlines",
      Exposure == "work_24" ~ "Angry patients",
      TRUE ~ Exposure
    ),
    Exposure_Label = factor(
      Exposure_Label,
      levels = c(
        "Weekly working hours",
        "Night shift",
        "Tight deadlines",
        "Angry patients"
      )
    )
  ) |> 
  group_by(Exposure_Label) |> 
  mutate(Level = factor(Level, levels = unique(Level))) |> 
  ungroup() |> 
  ggplot(aes(x = Level, 
             y = estimate,
             group = Outcome)) +
  geom_point(size = 2) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high),
                width = 0.1) +
  geom_smooth(method = "lm",
              linewidth = 0.6,
              colour = "black") +
  facet_wrap(~ Exposure_Label, scales = "free_x") +
  labs(
    x = "Exposure level",
    y = "Depressive symptoms (PHQ-9 score, 0-27)"
  ) +
  theme_bw() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "bottom"
  ) +
  scale_y_continuous(limit = c(0,15),
                     breaks = seq(0, 15, by = 1)) 

dose_plot_dem <- 
  
  dose_plot_dem + # Bs in footnote
  labs(
    caption = paste0(slope_labels |>
      dplyr::mutate(
        foot = paste0(
          Exposure_Label, " slope: B = ", round(estimate, 2),
          " (95% CI ", round(conf.low, 2), " to ", round(conf.high, 2), ")"
        )
      ) |>
      dplyr::summarise(txt = paste(foot, collapse = "; ")) |>
        
      # Replace all periods with the Unicode midpoint
      dplyr::mutate(txt = gsub("\\.", "\u00B7", txt)) |> 
      dplyr::pull(txt), " Shift work original response options were yes no and dose-response models were not performed."
  )) +
  theme(plot.caption = element_text(hjust = 0))

ggsave(filename = "dose_response_dem.pdf",
       plot = dose_plot_dem,
       device = "pdf",
       path = "out/figures/",
       scale = 3,
       width = 140,
       height = 70,
       units = "mm",
       dpi = 320
       )

```

```{r dose res plot}
# extract Bs and 95% CIs

trends <- readRDS("out/models/summary/dose_trends.rds")

dose_all_res <- readRDS("out/models/summary/dose_all_res.rds")

slope_labels <- 
  
  trends |> 
  filter(adj == "adjusted",
         out == "dep") |> 
  mutate(
    Exposure_Label = case_when(
      term == "work_19"  ~ "Influence",
      term == "work_20" ~ "Breaks",
      term == "work_21" ~ "Colleagues",
      term == "work_22" ~ "Superiors",
      TRUE ~ NA_character_
    )
  ) |> 
  filter(term %in% resources) |> 
  mutate(
    Exposure_Label = factor(Exposure_Label, 
                            levels = 
                              c("Influence", 
                                "Breaks", 
                                "Colleagues", 
                                "Superiors"))
    ) |> 
  arrange(Exposure_Label)
  

dose_plot_res <- 
  
  dose_all_res |> 
  filter(Model == "Adjusted",
         Outcome == "PHQ-9 score") |> 
  mutate(
    Exposure_Label = case_when(
      Exposure == "work_19"  ~ "Influence over work",
      Exposure == "work_20" ~ "Influence over work (breaks)",
      Exposure == "work_21" ~ "Colleague support",
      Exposure == "work_22" ~ "Support from superiors",
      TRUE ~ Exposure
    ),
    Exposure_Label = factor(
      Exposure_Label,
      levels = c(
        "Influence over work",
        "Influence over work (breaks)",
        "Colleague support",
        "Support from superiors"
      )
    )
  ) |> 
  group_by(Exposure_Label) |> 
  mutate(Level = factor(Level, levels = unique(Level))) |> 
  ungroup() |> 
  ggplot(aes(x = Level, 
             y = estimate,
             group = Outcome)) +
  geom_point(size = 2) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high),
                width = 0.1) +
  geom_smooth(method = "lm",
              linewidth = 0.6,
              colour = "black") +
  facet_wrap(~ Exposure_Label, scales = "free_x") +
  labs(
    x = "Exposure level",
    y = "Depressive symptoms (PHQ-9 score, 0-27)"
  ) +
  theme_bw() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "bottom"
  ) +
  scale_y_continuous(limit = c(0,15),
                     breaks = seq(0, 15, by = 1))
dose_plot_res <- 
  dose_plot_res + # Bs in footnote
  labs(
    caption = slope_labels |>
      dplyr::mutate(
        foot = paste0(
          Exposure_Label, " slope: B = ", round(estimate, 2),
          " (95% CI ", round(conf.low, 2), " to ", round(conf.high, 2), ")"
        )
      ) |>
      dplyr::summarise(txt = paste(foot, collapse = "; ")) |>
      # Replace all periods with the Unicode midpoint
      dplyr::mutate(txt = gsub("\\.", "\u00B7", txt)) |> 
      dplyr::pull(txt)
  ) +
  theme(plot.caption = element_text(hjust = 0))

ggsave(filename = "dose_response_res.pdf",
       plot = dose_plot_res,
       device = "pdf",
       path = "out/figures/",
       scale = 3,
       width = 140,
       height = 70,
       units = "mm",
       dpi = 320
       )


```

# Moderation: protocols

## Linear models multiplicative interaction

```{r moder haz prep}

# define outcomes, exposures, covariates

out # already defined

hazards # already defined

covs_1

# define moderators

moder <- c("work_28_dic", "work_29_dic")

# define strata

profs <- levels(ds$work_2) # not used

# maps

covariate_map <- list(
  "base_covs" = covs_1
)


# Create grid
tasks_moder <- expand_grid(
  Outcome = out,
  Family = "gaussian",          
  Exposure = hazards,
  Covar_Key = "base_covs",      
  profession = "All",
  Moderator = moder
)
```

```{r moder haz mod}
moder_all <- pmap_dfr(list(
  tasks_moder$Outcome,
  tasks_moder$Family,
  tasks_moder$Exposure,
  tasks_moder$Covar_Key,
  tasks_moder$Moderator
  ), function(outcome, family, exposure, cov_key, moderator) {
  
  message(paste("Processing:", outcome, "&", exposure, "&", moderator))
  
  res_crude <- run_glm_moder_emm(
    data = ds,
    outcome_var = outcome,
    exposure_var = exposure,
    confounder_list = NULL,
    moderator_var = moderator,
    model_label = "Crude"
  )
  
  res_adj <- run_glm_moder_emm(
    data = ds,
    outcome_var = outcome,
    exposure_var = exposure,
    confounder_list = covariate_map[[cov_key]],
    moderator_var = moderator,
    model_label = "Adjusted"
  ) 
  
  bind_rows(res_crude, res_adj)
})

moder_all |> # clean and export
  mutate(
    Est_CI = sprintf("%.2f (%.2f, %.2f)", estimate, conf.low, conf.high),
    Exposure_Label = case_when(
      Exposure == "work_31" ~ "Violent threats",
      Exposure == "work_32" ~ "Physical violence",
      Exposure == "work_30" ~ "Sexual harassment",
      Exposure == "work_33" ~ "Bullying",
      TRUE ~ Exposure),
    Outcome = case_when(
      Outcome == "phq_sc"   ~ "PHQ-9 score",
      Outcome == "gad_sc"   ~ "GAD-7 score",
      Outcome == "mh_phq_9" ~ "PHQ-9 suicidality item score",
      Outcome == "cage_sc"  ~ "CAGE score",
      TRUE ~ Outcome
    ),
    Moderator = case_when(
      Moderator == "work_28_dic" ~ "Bullying and harassment",
      Moderator == "work_29_dic" ~ "Threats, abuse, and assault"
    )
    ) |> 
  as_tibble() |> 
  saveRDS("out/models/summary/moder_all_final.rds")
```

```{r moder haz plot}
moder_all_final <- readRDS("out/models/summary/moder_all_final.rds")

moder_plot_bull_harass <- 
  
  moder_all_final |> 
  filter(Moderator == "Bullying and harassment" & Model == "Adjusted") |> 
  mutate(
    estimate = if_else(str_detect(Outcome, "suic|CAGE"),
                       estimate*10,
                       estimate),
    conf.low = if_else(str_detect(Outcome, "suic|CAGE"),
                       conf.low*10,
                       conf.low),
    conf.high = if_else(str_detect(Outcome, "suic|CAGE"),
                       conf.high*10,
                       conf.high)
    ) |> 
  mutate(level_index = case_when(Level == "No"               ~ "1",
                                 Level == "Yes, a few times" ~ "2",
                                 Level == "Yes, monthly"     ~ "3",
                                 Level == "Yes, weekly"      ~ "4",
                                 Level == "Yes, daily"       ~ "5"),
         level_index = as.integer(level_index)
         ) |> 
  ungroup() |> 
  mutate(Outcome = factor(Outcome, 
                          levels = c("PHQ-9 score",
                                     "GAD-7 score",
                                     "PHQ-9 suicidality item score",
                                     "CAGE score"))
         ) |> 
  arrange(Outcome) |> 
  ggplot(aes(x = level_index, 
             y = estimate, 
             group = Moderator_Level,
             color = Moderator_Level)
         ) +
    geom_ribbon(
    aes(
      ymin = conf.low,
      ymax = conf.high,
      fill = Moderator_Level
    ),
    alpha = 0.2,
    color = NA
  ) +
  geom_line(linewidth = 0.5,
            position = position_dodge(width = 0.2)) + 
  geom_point(size = 2,
             position = position_dodge(width = 0.2)) + 
  facet_grid(rows = vars(Exposure_Label),
             cols = vars(Outcome),
             scales = "free",
             switch = "y") + 
  scale_fill_viridis_d() +
  scale_color_viridis_d() +
  scale_x_continuous(breaks = 1:5, minor_breaks = NULL) +
  labs(
    x = "Level of exposure",
    y = "Score change estimate",
    caption = "Bullying and harassment protocols"
  ) + 
  theme(
    strip.placement = "outside",  
    strip.text.y.left = element_text(angle = 90, face = "bold", size = 10), 
    strip.text.x = element_text(face = "bold", size = 10),
    axis.text.x = element_text(size = 10),
    axis.title.x = element_text(size = 10),
    axis.text.y = element_text(size = 10),
    panel.border = element_rect(color = "black", fill = NA),  
    axis.title.y = element_blank(), 
    legend.position = "right",
    legend.key.width = unit(1.5, "cm")
  ) +
  ylim(0,25)

moder_plot_threats_abuse_assault <- 
  
  moder_all_final |> 
  filter(Moderator == "Threats, abuse, and assault" & Model == "Adjusted") |> 
  mutate(
    estimate = if_else(str_detect(Outcome, "suicide"),
                       estimate*10,
                       estimate),
    conf.low = if_else(str_detect(Outcome, "suicide"),
                       conf.low*10,
                       conf.low),
    conf.high = if_else(str_detect(Outcome, "suicide"),
                       conf.high*10,
                       conf.high)
    ) |> 
  mutate(level_index = case_when(Level == "No"               ~ "1",
                                 Level == "Yes, a few times" ~ "2",
                                 Level == "Yes, monthly"     ~ "3",
                                 Level == "Yes, weekly"      ~ "4",
                                 Level == "Yes, daily"       ~ "5"),
         level_index = as.integer(level_index)
         ) |> 
  ungroup() |> 
  mutate(Outcome = factor(Outcome, 
                          levels = c("PHQ-9 score",
                                     "GAD-7 score",
                                     "PHQ-9 suicidality item score",
                                     "CAGE score")
                          )
         ) |> 
  arrange(Outcome) |> 
  ggplot(aes(x = level_index, 
             y = estimate, 
             group = Moderator_Level,
             color = Moderator_Level)
         ) +
    geom_ribbon(
    aes(
      ymin = conf.low,
      ymax = conf.high,
      fill = Moderator_Level
    ),
    alpha = 0.2,
    color = NA
  ) +
  geom_line(linewidth = 0.5,
            position = position_dodge(width = 0.2)) + 
  geom_point(size = 2,
             position = position_dodge(width = 0.2)) + 
  facet_grid(rows = vars(Exposure_Label),
             cols = vars(Outcome),
             scales = "free",
             switch = "y") + 
  scale_fill_viridis_d() +
  scale_color_viridis_d() +
  scale_x_continuous(breaks = 1:5, minor_breaks = NULL) +
  labs(
    x = "Level of exposure",
    y = "Score change estimate",
    caption = "Threats, abuse, or assaults protocols"
  ) + 
  theme(
    strip.placement = "outside",  
    strip.text.y.left = element_text(angle = 90, face = "bold", size = 10), 
    strip.text.x = element_text(face = "bold", size = 10),
    axis.text.x = element_text(size = 10),
    axis.title.x = element_text(size = 10),
    axis.text.y = element_text(size = 10),
    panel.border = element_rect(color = "black", fill = NA),  
    axis.title.y = element_blank(), 
    legend.position = "right",
    legend.key.width = unit(1.5, "cm")
  ) +
  ylim(0,25)

# save plots

ggsave(filename = "moder_plot_bull_harass.pdf",
       plot = moder_plot_bull_harass,
       device = "pdf",
       path = "out/figures/",
       scale = 3,
       width = 140,
       height = 70,
       units = "mm",
       dpi = 320
       )

ggsave(filename = "moder_plot_threats_abuse_assault.pdf",
       plot = moder_plot_threats_abuse_assault,
       device = "pdf",
       path = "out/figures/",
       scale = 3,
       width = 140,
       height = 70,
       units = "mm",
       dpi = 320
       )
```

```{r moder haz tbl}

tasks_inter <- 
  
  tasks_moder |> 
    mutate(
    Covariates = purrr::map(Covar_Key, ~ covariate_map[[.x]])
  )

safe_lrt <- purrr::possibly(
  run_glm_moder_lrt,
  otherwise = NULL
)

lrt_results <- 
  
  tasks_inter |>
  mutate(
    lrt = purrr::pmap(
      list(
        outcome_var     = Outcome,
        exposure_var    = Exposure,
        moderator_var   = Moderator,
        confounder_list = Covariates
      ),
      ~ safe_lrt(
        data = ds,
        outcome_var = ..1,
        exposure_var = ..2,
        moderator_var = ..3,
        confounder_list = ..4,
        model_label = "Adjusted"
      )
    )
  )

lrt_table_all <- 
  
  lrt_results |>
  filter(!purrr::map_lgl(lrt, is.null)) |>
  select(lrt) |>
  tidyr::unnest(lrt)


lrt_table_all <- 
  
  lrt_table_all |>
  group_by(Outcome) |>
  mutate(
    p_fdr = p.adjust(p_value, method = "fdr")
  ) |>
  ungroup()

tbl_moder <- 
  
  lrt_table_all |> 
  mutate(
    Exposure = fct_recode(Exposure,
                          "Sexual harassment" = "work_30",
                          "Violent threats" = "work_31",
                          "Physical violence" = "work_32",
                          "Bullying" = "work_33"),
    Outcome = fct_recode(Outcome,
                         "Depression" = "phq_sc",
                         "Anxiety" = "gad_sc",
                         "Alcohol dependence" = "cage_sc",
                         "Suicidal thoughts" = "mh_phq_9"),
    Moderator = 
      fct_recode(Moderator,
                 "Workplace harassment protocol" = "work_28_dic",
                 "Workplace violence protocol" = "work_29_dic")
  ) |> 
  select(!Model) |> 
  mutate(
    label = paste0(
      "Chi-squared (", df,") = ", round(chisq,2), ", p = ", round(p_value,3))
  ) |> 
  select(Outcome, Exposure, Moderator, label)
  

tab_wide <- tbl_moder |> 
  tidyr::pivot_wider(
    names_from  = Moderator,
    values_from = label
  ) |> 
  mutate(Outcome = factor(Outcome, levels = outcome_order)) |> 
  arrange(Outcome, Exposure)


# With chi square symbol
# Define the columns to modify
target_cols <- 
  c("Workplace harassment protocol", 
    "Workplace violence protocol")

# Initialize the flextable
ft <- flextable(tab_wide) 

# Use a loop to format the Chi-squared symbol for each column
for(col in target_cols){
  ft <- mk_par(
    x = ft,
    j = col,
    value = as_paragraph(
      as_chunk("\u03c7", props = officer::fp_text(italic = TRUE)), # Chi symbol
      as_chunk("2", 
               props = officer::fp_text(vertical.align = "superscript")),#Squared
      as_chunk("(4)"), # Degrees of freedom
      # This removes "Chi-squared (4)", keeping the " = X, p = Y"
      as_chunk(gsub("Chi-squared \\(4\\)", "", tab_wide[[col]]))
    )
  )
}

# Apply your final styling
ft <- 
  
  ft |>
  set_header_labels(
    Outcome  = "Outcome",
    Exposure = "Exposure",
    `Workplace harassment protocol` = "Harassment protocol",
    `Workplace violence protocol`   = "Violence protocol"
  ) |>
  align(j = "Exposure", align = "left", part = "all") |>
  align(j = target_cols, align = "center", part = "all") |>
  # Optional: Merge identical Outcome cells for a cleaner Word look
  merge_v(j = "Outcome") |> 
  valign(j = "Outcome", valign = "top") |>
  autofit()

# Export to Word
save_as_docx(ft, path = "out/tables/moder_interacts.docx")

save_as_docx(ft, path = "out/tables/moder_interacts.docx")
```

## Poisson models multiplicative interactions

```{r moder-dic haz prep}

# define outcomes, exposures, covariates

out_poisson # already defined

hazards_dic # already defined

covs_1

# define moderators

moder <- c("work_28_dic", "work_29_dic")

# define strata

profs <- levels(ds$work_2) # not used

# maps

covariate_map <- list(
  "base_covs" = covs_1
)


# Create grid
tasks_moder_dic <- expand_grid(
  Outcome = out_poisson,
  Family = "poisson",          
  Exposure = hazards_dic,
  Covar_Key = "base_covs",      
  profession = "All",
  Moderator = moder,
  Moderator_YesNo = c("Yes", "No")
)
```

```{r moder-dic haz mod}
moder_dic <- pmap(list(
  tasks_moder_dic$Outcome,
  tasks_moder_dic$Family,
  tasks_moder_dic$Exposure,
  tasks_moder_dic$Covar_Key,
  tasks_moder_dic$Moderator,
  tasks_moder_dic$Moderator_YesNo
), function(outcome, family, exposure, cov_key, moder, moder_val) {
  
  message(paste("Processing:", outcome, "x", exposure, "in", moder))
  
  specific_covars <- covariate_map[[cov_key]]

  res_adj <- run_adj_moder_glm(
    data = ds,
    outcome_var = outcome,
    exposure_var = exposure,
    moderator = moder,
    moder_val = moder_val,
    family_type = family,
    confounder_list = specific_covars,
    model_label = "Adjusted"
  )

  # Combine internally
  
  row_multilevel <- 
    
      res_adj$multilevel
  
  row_robust <- 

      res_adj$robust

  
  # return as clean pair
  
  return(list(
    multilevel = row_multilevel,
    robust     = row_robust
  ))
})

glm_multilevel_moder_dic_df <- map_dfr(moder_dic, "multilevel")

glm_robust_moder_dic_df <- map_dfr(moder_dic, "robust")

# Save

saveRDS(glm_multilevel_moder_dic_df, "out/models/summary/multi_inter_haz_dic.rds")
saveRDS(glm_robust_moder_dic_df, "out/models/summary/rob_inter_haz_dic.rds")
```

```{r moder-dic haz plot}

ds_plot <-
  
  readRDS("out/models/summary/multi_inter_haz_dic.rds") |> 
  select(Outcome, Exposure, Moderator, ModeratorLevel, Risk_Unexp, Risk_Exp) |> 
  pivot_longer(cols = Risk_Unexp:Risk_Exp) |> 
  mutate(
    value = str_extract(value, "[:digit:]*.[:digit:]*") |> as.numeric(),
    name = fct_recode(name, "Yes" = "Risk_Exp", "No" = "Risk_Unexp"),
    Exposure = fct_recode(Exposure,
                          "Sexual harassment" = "work_30_dic",
                          "Violent threats" = "work_31_dic",
                          "Physical violence" = "work_32_dic",
                          "Bullying" = "work_33_dic"),
    Outcome = fct_recode(Outcome,
                         "Depression" = "phq_co_poi",
                         "Anxiety" = "gad_co_poi",
                         "Suicidal thoughts" = "suic_idea_poi",
                         "Alcohol dependence" = "cage_co_poi"),
    name = fct_relevel(name, "No", "Yes"),
    Outcome = fct_relevel(Outcome, 
                          "Depression",
                          "Anxiety",
                          "Suicidal thoughts",
                          "Alcohol dependence")
         )

# depression

moder_dic_dep <- 
  
  ds_plot |> 
  filter(Outcome ==  "Depression") |>
  mutate(Moderator = if_else(Moderator == "work_28_dic",
                             "Bullying and harassment protocol",
                             "Violence protocol")
         ) |>
  ggplot(
    aes(
      x = name,
      y = value,
      shape = ModeratorLevel
    )
  ) +
  facet_grid(cols = vars(Moderator),
             rows = vars(Exposure)) +
  geom_point(size = 2) +
  geom_line(aes(group = ModeratorLevel)) +
  labs(x = "Exposed",
       y = "Depression prevalence (%)",
       shape = "Protocol available") +
  ylim(0,60) + 
  theme(
    legend.text = element_text(size = 8),
    legend.title = element_text(size = 8),
    axis.text.x = element_text(size = 8),
    axis.text.y = element_text(size = 8),
    axis.title.x = element_text(size = 8),
    axis.title.y = element_text(size = 8),
    strip.text = element_text(size = 8)
  )

ggsave(moder_dic_dep, 
       filename = "moder_dic_dep.pdf",
       device = "pdf",
       path = "out/figures/",
       scale = 1.9,
       width = 140,
       height = 100,
       units = "mm",
       dpi = 320
       )

moder_dic_dep

ragg::agg_png("out/figures/moder_dic_dep.png",
              width = 9,
              height = 7,
              units = "in",
              res = 600,
              scaling = 0.5)

print(moder_dic_dep)

dev.off()

rm(moder_dic_dep)

# anxiety

moder_dic_anx <- 
  
  ds_plot |> 
  filter(Outcome ==  "Anxiety") |>
  mutate(Moderator = if_else(Moderator == "work_28_dic",
                             "Bullying and harassment protocol",
                             "Violence protocol")
         ) |>
  ggplot(
    aes(
      x = name,
      y = value,
      shape = ModeratorLevel
    )
  ) +
  facet_grid(cols = vars(Moderator),
             rows = vars(Exposure)) +
  geom_point(size = 2) +
  geom_line(aes(group = ModeratorLevel)) +
  labs(x = "Exposed",
       y = "Anxiety prevalence (%)",
       shape = "Protocol available") +
  ylim(0,60) + 
  theme(
    legend.text = element_text(size = 8),
    legend.title = element_text(size = 8),
    axis.text.x = element_text(size = 8),
    axis.text.y = element_text(size = 8),
    axis.title.x = element_text(size = 8),
    axis.title.y = element_text(size = 8),
    strip.text = element_text(size = 8)
  )

ggsave(moder_dic_anx, 
       filename = "moder_dic_anx.pdf",
       device = "pdf",
       path = "out/figures/",
       scale = 1.9,
       width = 140,
       height = 100,
       units = "mm",
       dpi = 320
       )

moder_dic_anx

ragg::agg_png("out/figures/moder_dic_anx.png",
              width = 9,
              height = 7,
              units = "in",
              res = 600,
              scaling = 0.5)

print(moder_dic_anx)

dev.off()

rm(moder_dic_anx)

# suicidal thoughts

moder_dic_suic <- 
  
  ds_plot |> 
  filter(Outcome ==  "Suicidal thoughts") |>
  mutate(Moderator = if_else(Moderator == "work_28_dic",
                             "Bullying and harassment protocol",
                             "Violence protocol")
         ) |>
  ggplot(
    aes(
      x = name,
      y = value,
      shape = ModeratorLevel
    )
  ) +
  facet_grid(cols = vars(Moderator),
             rows = vars(Exposure)) +
  geom_point(size = 2) +
  geom_line(aes(group = ModeratorLevel)) +
  labs(x = "Exposed",
       y = "Suicidal thoughts prevalence (%)",
       shape = "Protocol available") +
  ylim(0,30) + 
  theme(
    legend.text = element_text(size = 8),
    legend.title = element_text(size = 8),
    axis.text.x = element_text(size = 8),
    axis.text.y = element_text(size = 8),
    axis.title.x = element_text(size = 8),
    axis.title.y = element_text(size = 8),
    strip.text = element_text(size = 8)
  )

ggsave(moder_dic_suic, 
       filename = "moder_dic_suic.pdf",
       device = "pdf",
       path = "out/figures/",
       scale = 1.9,
       width = 140,
       height = 100,
       units = "mm",
       dpi = 320
       )

moder_dic_suic

ragg::agg_png("out/figures/moder_dic_suic.png",
              width = 9,
              height = 7,
              units = "in",
              res = 600,
              scaling = 0.5)

print(moder_dic_suic)

dev.off()

rm(moder_dic_suic)

# alcohol dependence

moder_dic_alc <-
  
  ds_plot |> 
  filter(Outcome ==  "Alcohol dependence") |>
  mutate(Moderator = if_else(Moderator == "work_28_dic",
                             "Bullying and harassment protocol",
                             "Violence protocol")
         ) |>
  ggplot(
    aes(
      x = name,
      y = value,
      shape = ModeratorLevel
    )
  ) +
  facet_grid(cols = vars(Moderator),
             rows = vars(Exposure)) +
  geom_point(size = 2) +
  geom_line(aes(group = ModeratorLevel)) +
  labs(x = "Exposed",
       y = "Alcohol dependence prevalence (%)",
       shape = "Protocol available") +
  ylim(0,15) + 
  theme(
    legend.text = element_text(size = 8),
    legend.title = element_text(size = 8),
    axis.text.x = element_text(size = 8),
    axis.text.y = element_text(size = 8),
    axis.title.x = element_text(size = 8),
    axis.title.y = element_text(size = 8),
    strip.text = element_text(size = 8)
  )

ggsave(moder_dic_alc, 
       filename = "moder_dic_alc.pdf",
       device = "pdf",
       path = "out/figures/",
       scale = 1.9,
       width = 140,
       height = 100,
       units = "mm",
       dpi = 320
       )

moder_dic_alc

ragg::agg_png("out/figures/moder_dic_alc.png",
              width = 9,
              height = 7,
              units = "in",
              res = 600,
              scaling = 0.5)

print(moder_dic_alc)

dev.off()

rm(moder_dic_alc)

```

## Additive interaction (hazards)

```{r expl RERI}
tasks_moder_prevs <- 
  
  expand_grid(
    Outcome    = out_poisson,
    Family     = "poisson",
    Exposure   = hazards_dic,
    Covar_Key  = "base_covs",
    profession = "All",
    Moderator  = moder
    )

results_moder_prevs <- 
  
  tasks_moder_prevs |>
  mutate(
    confounders = purrr::map(Covar_Key, ~ covariate_map[[.x]])
  ) |> 
  pmap_dfr(function(Outcome,
                    Family,
                    Exposure,
                    Covar_Key,
                    profession,
                    Moderator,
                    confounders) {
    
    run_adj_moder_prevs(
      data            = ds,
      outcome_var     = Outcome,
      exposure_var    = Exposure,
      moderator_var   = Moderator,
      confounder_list = confounders,
      profession      = profession
    )
  })

saveRDS(results_moder_prevs, "out/models/summary/results_moder_prevs.rds")
```

```{r inter prevs}
inter_prevs <- readRDS("out/models/summary/results_moder_prevs.rds")

# Cleaning
inter_prevs_clean <-
  
  inter_prevs |> 
  mutate(
    across(
      where(is.numeric),
      \(x) round(x, 2)
    )
  ) |> 
  mutate(
    RERI_fmt = paste0(RERI, " (", CI_l, " to ", CI_u, ")"),
    MI_fmt = paste0(MI, " (", MI_CI_l, " to ", MI_CI_u, ")")
  ) |> 
  select(
    Outcome, Exposure, Moderator, RR11, RR10, RR01, RERI_fmt, MI_fmt
    ) |> 
  pivot_wider(
    names_from = Moderator,
    values_from = 4:8,
    names_glue = "{Moderator}_{.value}"
  ) |> 
  select(
    Outcome, Exposure, starts_with("work_28_"), starts_with("work_29")
  ) |> 
  mutate(
    Outcome = case_when(
      Outcome == "phq_co_poi" ~ "Depression",
      Outcome == "gad_co_poi" ~ "Anxiety",
      Outcome == "cage_co_poi" ~ "Alcohol dependence",
      Outcome == "suic_idea_poi" ~ "Suicidal thoughts"
    ),
    Outcome = factor(Outcome, levels = c("Depression", "Anxiety", "Alcohol dependence", "Suicidal thoughts")),
    Exposure = case_when(
      Exposure == "work_30_dic" ~ "Sexual harassment",
      Exposure == "work_31_dic" ~ "Violent threats",
      Exposure == "work_32_dic" ~ "Physical violence",
      Exposure == "work_33_dic" ~ "Bullying"
    )
  ) |> 
  arrange(Outcome)

# Generate table
inter_prevs_tbl <-
  
  inter_prevs_clean |> 
  as_grouped_data(groups = "Outcome") |> 
  flextable() |> 
  add_header_row(
    values = c("", "",  "Harassment protocols", "Violence protocols"),
    colwidths = c(1, 1, 5, 5) 
  ) |> 
  set_header_labels(
    Outcome = "Outcome",
    Exposure = "Exposure",
    work_28_dic_RR11 = "PR (E = 1, M = 1)",
    work_28_dic_RR10 = "PR (E = 1, M = 0)",
    work_28_dic_RR01 = "PR (E = 0, M = 1)",
    work_28_dic_RERI_fmt = "Excess PR due to interaction",
    work_28_dic_MI_fmt = "Ratio of PR's",
    work_29_dic_RR11 = "PR (E = 1, M = 1)",
    work_29_dic_RR10 = "PR (E = 1, M = 0)",
    work_29_dic_RR01 = "PR (E = 0, M = 1)",
    work_29_dic_RERI_fmt = "Excess PR due to interaction",
    work_29_dic_MI_fmt = "Ratio of PR's"
  ) |> 
  align(i = 1, align = "center", part = "header") 


# With subindices
inter_prevs_clean |> 
  as_grouped_data(groups = "Outcome") |> 
  flextable() |> 
  # 1. Create the spanners (Row 1)
  add_header_row(
    values = c("", "", "Harassment protocols", "Violence protocols"),
    colwidths = c(1, 1, 5, 5) 
  ) |> 
  # 2. Set the static labels for the lower header (Row 2)
  set_header_labels(
    Outcome = "Outcome",
    Exposure = "Exposure",
    work_28_dic_RERI_fmt = "Excess PR due to interaction",
    work_28_dic_MI_fmt = "Ratio of PR's",
    work_29_dic_RERI_fmt = "Excess PR due to interaction",
    work_29_dic_MI_fmt = "Ratio of PR's"
  ) |> 
  # 3. Format PR with subscripts ONLY on Row 2 (i = 2)
  mk_par(i = 2, j = "work_28_dic_RR11", part = "header", value = as_paragraph("PR", as_sub("11"))) |> 
  mk_par(i = 2, j = "work_28_dic_RR10", part = "header", value = as_paragraph("PR", as_sub("10"))) |> 
  mk_par(i = 2, j = "work_28_dic_RR01", part = "header", value = as_paragraph("PR", as_sub("01"))) |> 
  mk_par(i = 2, j = "work_29_dic_RR11", part = "header", value = as_paragraph("PR", as_sub("11"))) |> 
  mk_par(i = 2, j = "work_29_dic_RR10", part = "header", value = as_paragraph("PR", as_sub("10"))) |> 
  mk_par(i = 2, j = "work_29_dic_RR01", part = "header", value = as_paragraph("PR", as_sub("01"))) |> 
  # 4. Alignment
  align(i = 1:2, align = "center", part = "header")
  



# Long


inter_prevs_long <-
  
  inter_prevs |> 
  mutate(
    across(
      where(is.numeric),
      \(x) round(x, 2)
    )
  ) |> 
  mutate(
    RERI_fmt = paste0(RERI, " (", CI_l, " to ", CI_u, ")"),
    MI_fmt = paste0(MI, " (", MI_CI_l, " to ", MI_CI_u, ")")
  ) |> 
  select(
    Outcome, Exposure, Moderator, RR11, RR10, RR01, RERI_fmt, MI_fmt
    ) |>
  mutate(
    Outcome = case_when(
      Outcome == "phq_co_poi" ~ "Depression",
      Outcome == "gad_co_poi" ~ "Anxiety",
      Outcome == "cage_co_poi" ~ "Alcohol dependence",
      Outcome == "suic_idea_poi" ~ "Suicidal thoughts"
    ),
    Outcome = factor(Outcome, levels = c("Depression", "Anxiety", "Alcohol dependence", "Suicidal thoughts")),
    Exposure = case_when(
      Exposure == "work_30_dic" ~ "Sexual harassment",
      Exposure == "work_31_dic" ~ "Violent threats",
      Exposure == "work_32_dic" ~ "Physical violence",
      Exposure == "work_33_dic" ~ "Bullying"
    ),
    Moderator = case_when(
      Moderator == "work_28_dic" ~ "Harassment protocol",
      Moderator == "work_29_dic" ~ "Violence protocol"
    )
  ) |> 
  arrange(Outcome)

# table long
inter_prevs_tbl_long <- 
  
  inter_prevs_long |> 
  flextable() |>
  set_header_labels(
    Outcome = "Outcome",
    Exposure = "Exposure",
    Protocol_Type = "Protocol",
    RR11 = "PR11",
    RR10 = "PR10",
    RR01 = "PR01",
    RERI_fmt = "Excess PR due to interaction",
    MI_fmt = "Ratio of PR's"
  ) |> 
  # Apply the subscripts to the single set of PR columns
  mk_par(
    j = "RR11",
    part = "header",
    value = as_paragraph("PR", as_sub("11"))
    ) |> 
  mk_par(
    j = "RR10", 
    part = "header", 
    value = as_paragraph("PR", as_sub("10"))
    ) |>
  mk_par(
    j = "RR01", 
    part = "header", 
    value = as_paragraph("PR", as_sub("01"))
    ) |> 
  # Merge the Outcome and Exposure vertically
  merge_v(j = c("Outcome", "Exposure")) |> 
  # Add a border between Exposure groups for clarity
  fix_border_issues() |> 
  valign(j = c("Outcome", "Exposure"), valign = "top")


save_as_docx(
  inter_prevs_tbl_long,
  path = "out/tables/inter_prevs_tbl_long.docx"
)

```

