---
title: "MeND working conditions manuscript: response to reviewers (R1)"
author: "Roberto Mediavilla and Vicente Arrona"
date: "`r Sys.Date()`"
output: 
  html_document: 
    toc: true
    toc_float: true
editor_options: 
  chunk_output_type: console
---

```{r setup}
knitr::opts_chunk$set(
  fig.path = "out/",  
  fig.ext = "pdf",
  fig.height = 12,
  fig.width = 16,
  dpi = 300,                     # high resolution for non-vector formats
  echo = TRUE,                  
  warning = TRUE,               
  message = TRUE                
)
```

```{r source}

source("src/setup.R") # updated with new packages
source("src/fns_r1.R") # new functions to work with mids
source("src/fns_associations.R") # old functions -still required

ds <- # dataset
  
  readRDS("data/who_hcw_survey_clean.rds")

cb <- # codebook

  read.csv("ext/data_mapping.csv", na.strings = "")

who_ipw_population <- # popuation data
  
  readRDS("ext/who_ipw_population.rds")

ipw_sample <- # sample data
  
  readRDS("ext/ipw_sample.rds")

# weights to DS

w <- 
  
  readRDS("ext/weights.rds")

# total denominator
who_n_loc <- 
  
  readRDS("ext/who_n_loc.rds")

```

```{r weights}
ds <- left_join(ds, w, by = "user_id")
```

# Preprocessing

This is inherited from analysis.Rmd for consistency, with a few minor tweaks to make new functions run on mids objects

```{r var lists}

# scdm

scdm <- c("scdm_1_rec",
          "scdm_2",
          "work_1",
          "work_2",
          "work_5_rec",
          "work_7")

scdm_ext <- c("scdm_1_rec",
              "scdm_2_rec",
              "scdm_5_dic",
              "scdm_6",
              "work_1",
              "work_2",
              "work_5_rec",
              "work_7",
              "work_13",
              "work_14",
              "work_16")

# MH outcomes

out_dic <- c("phq_co", "gad_co", "suic_idea", "cage_co")

out <- c("phq_sc", "gad_sc", "mh_phq_9", "cage_sc")

out_poisson <- c("phq_co_poi", "gad_co_poi", "suic_idea_poi", "cage_co_poi")

named_outcomes <- c(
  "Probable Depression" = "phq_co",
  "Probable Anxiety"    = "gad_co",
  "Alcohol dependence"  = "cage_co",
  "Suicidal thoughts"    = "suic_idea"
)


# Job demands

demands <- c("work_8", "work_11", "work_12", "work_23", "work_24") 
demands_num <- c(paste0(demands, "_num"))[c(1, 2, 4, 5)] # work_12 is binary
demands_dic <- c(paste0(demands, "_dic")) 

named_demands <- c(
  "Extended working hours"    = "work_8_dic",
  "Frequent night shifts"    = "work_11_dic",
  "Regular shift work" = "work_12_dic",
  "Tight deadlines" = "work_23_dic",
  "Angry patients or relatives" = "work_24_dic")

# Job hazards

hazards <- c("work_30", "work_31", "work_32", "work_33")
hazards_dic <- c(paste0(hazards, "_dic"))

hazards_num <- c(paste0(hazards, "_num"))

named_hazards <- c(
  "Sexual harassment"    = "work_30_dic",
  "Violent threats"    = "work_31_dic",
  "Physical violence" = "work_32_dic",
  "Bullying" = "work_33_dic"
)

# Organisational support structures

protocols <- c("work_25", "work_26", "work_27", "work_28", "work_29")
protocols_dic <- c(paste0(protocols, "_dic"))

named_protocols <- c(
  "Work council or union" = "work_25_dic",
  "Employee feedback"    = "work_26_dic",
  "Stress action plan"    = "work_27_dic",
  "Harassment protocol" = "work_28_dic",
  "Violence protocol" = "work_29_dic"
)

# Job Resources

resources <- c("work_19", "work_20", "work_21", "work_22")
resources_dic <- c(paste0(resources, "_dic"))

resources_num <- c(paste0(resources, "_num"))

named_resources <- c(
  "Influence over work" = "work_19_dic",
  "Influence over work (breaks)"    = "work_20_dic",
  "Colleague support"    = "work_21_dic",
  "Support from superiors" = "work_22_dic"
)

# define exposures

all_exposures <- c(demands_dic, hazards_dic, resources_dic, protocols_dic)

all_exposures_bis <- c(demands, hazards, resources, protocols)

# Covars

covs_1 <- c("scdm_1_rec",
            "scdm_2", # "Other" gender excluded before MICE; _rec no longer required
            "scdm_5_dic",
            "scdm_6",
            "work_1",
            "work_2",
            "work_3_rec",
            "work_4_dic",
            "work_5_rec",
            "work_7")

covs_2 <- c("loc_2")

# exposure order

exposure_order <-  
  c(demands_dic, hazards_dic, resources_dic, protocols_dic)

exposure_order_named <- 
  c("Extended working hours",
    "Frequent night shifts",
    "Regular shift work",
    "Tight deadlines",
    "Angry patients or relatives",
    "Sexual harassment",
    "Violent threats",
    "Physical violence", 
    "Bullying",
    "Influence over work",
    "Influence over work (breaks)",
    "Colleague support",
    "Support from superiors",
    "Work council or union",
    "Employee feedback",
    "Stress action plan",
    "Harassment protocol",
    "Violence protocol")


exposure_order_dose <- 
  c("Weekly working hours",
    "Night shift frequency",
    "Tight deadlines frequency",
    "Angry patients frequency",
    "Sexual harassment",
    "Violent threats",
    "Physical violence", 
    "Bullying",
    "Influence over work",
    "Influence over work (breaks)",
    "Colleague support",
    "Support from superiors")


# This will be needed
exposure_metadata <- 
  
  bind_rows(
  enframe(
    named_demands, 
    name = "Label", 
    value = "Column"
    )  |>
    mutate(Category = "Job Demands"),
  enframe(
    named_hazards, 
    name = "Label", 
    value = "Column"
    )  |>  
    mutate(Category = "Job Hazards"),
  enframe(
    named_resources, 
    name = "Label", 
    value = "Column"
    )  |> 
    mutate(Category = "Job Resources"),
  enframe(
    named_protocols, 
    name = "Label", 
    value = "Column"
    )  |> 
    mutate(Category = "Organisational support structures")
)

# outcome order

outcome_order <- 
  c("Depression", "Anxiety", "Alcohol dependence", "Suicidal thoughts")
```

```{r preprocess}

# some responses are too long

ds <- 
  
  ds  |> 
  mutate(work_7 = fct_recode(
    work_7,
    "Public and private sectors" = 
      "I work in both the public sector and in the private sector (or I work in the public sector and I am self-employed)",
    "Private sector only" = 
      "I work in the private healthcare sector only (I do not work in the public sector)",
    "Public sector only" = 
      "I work in the public healthcare sector only (I do not work in the private sector, nor am I self-employed)"
  ))

ds <- 
  
  ds |> 
  mutate(scdm_1 = fct_recode(scdm_1, "Under 20" = "Less than 20 years old"))

ds <- 
  
  ds |> 
  mutate(work_5 = fct_recode(
    work_5,
    "Extra-hospital emergencies" = 
      "Emergency care outside hospital (e.g., ambulance)",
    "In-hospital care" = 
      "Inpatient care (hospital services)",
    "Outpatient primary care" = 
      "Primary care (outpatient services)",
    "Outpatient secondary care" =
      "Secondary care (outpatient services)"
  ))

ds <- 
  
  ds |> 
  mutate(work_5_rec = fct_collapse( 
    work_5,
    "Inpatient" = c("Emergency department",
                    "In-hospital care"),
    "Outpatient" = c("Outpatient primary care",
                     "Outpatient secondary care"),
    "Other" = c("Extra-hospital emergencies",
                "Other")
  )
  )

ds <- 
  
  ds |> 
  mutate(work_11 = fct_recode(
    work_11,
    "Daily" = 
      "Every day",
    "Almost daily" = 
      "At least 4 days a week, but not every day",
    "2-3 days/week" = 
      "2 or 3 days a week",
    "Almost weekly" = 
      "Almost every week",
    "1-2 times/month" =
      "Once or twice a month",
    "Less than monthly" =
    "Less than once a month",
    "Never/Rarely" = 
      "Never or very rarely (e.g., once or twice a year)"
  ))

ds <- 
  
  ds |> 
  mutate(work_8 = fct_recode(
    work_8,
    "< 11 h" = 
      "Less than 11 hours",
    "11-20 h" = 
      "11-20 hours",
    "21-30 h" = 
      "21-30 hours",
    "31-40 h" = 
      "31-40 hours",
    "41-50 h" =
      "41-50 hours",
    "51-60 h" = 
      "51-60 hours",
    "61-70 h" = 
      "61-70 hours",
    "> 70 h" = 
      "More than 70 hours"
  ))

# Some variables and exposures require processing

ds <- 
  
  ds |> 
  
  # Household 
  
  mutate(scdm_5_dic = case_when(
    str_detect(scdm_5, "with children") ~ "Has children",
    str_detect(scdm_5, "without children") ~ "No children",
    TRUE ~ NA
    ),
    scdm_5_dic = factor(scdm_5_dic,
                        levels = c("Has children", "No children"),
                        ordered = FALSE)
  ) |>
  
  # recode length of service
  
  mutate(work_3_rec = fct_collapse(
    work_3,
    "5 years or less" = c("Less than 1 year", "1-3 years", "4-5 years"),
    "More than 10 years" = c("11-20 years", "21-30 years", "31-40 years",
                             "More than 40 years")
    )
  ) |> 
  
  # job positions
  
  mutate(
    work_4_dic = if_else(work_4 == "One",
                         "One",
                         "More than one"),
    work_4_dic = factor(work_4_dic,
                        levels = c("One", "More than one"))
  ) |> 
  
  # recode working hours
  
  mutate(
    work_8_dic = case_when(as.numeric(work_8) <= 5 ~ "No", # <= 50h
                           as.numeric(work_8) > 5 ~ "Yes"), # > 50h
    work_8_dic = factor(work_8_dic, levels = c("No", "Yes"))
  ) |> 
  
  # recode night work
  
  mutate(
    work_11_dic = 
      case_when(as.numeric(work_11) > 5 ~ "No", # 1 or 2x a month or less
                as.numeric(work_11) <= 5 ~ "Yes"), # Almost every week and more
    work_11_dic = factor(work_11_dic, levels = c("No", "Yes")),
    work_11 = fct_rev(work_11)
  ) |> 
  
  # name var for shifts
  
  mutate(work_12_dic = factor(work_12, levels = c("No", "Yes"))
  ) |> 
  
  # create dichotomic for contract type
  
  mutate(work_16_dic = fct_recode(work_16,
                                  "Yes" = "Temporary contract",
                                  "No" = "Fixed contract"),
         work_16_dic = factor(work_16_dic,
                              levels = c("No", "Yes"),
                              ordered = FALSE)
  ) |> 
  
  # recode managing patient anger
  
  mutate(
    across(
      all_of(c("work_23", "work_24")),
      ~ factor(
        fct_collapse(.x,
                     "Yes" = c("Around 1/4 of the time",
                               "Around half of the time",
                               "Around 3/4 of the time",
                               "Almost all of the time",
                               "All of the time"),
                     "No" = c("Never",
                              "Almost never")),
                     levels = c("No", "Yes"),
                     ordered = FALSE),
        .names = "{.col}_dic"
        )
      ) |> 
  
  # recode violence
  
   mutate(
    across(
      all_of(hazards),
      ~ factor(
        fct_collapse(.x,
                     "Yes" = c("Yes, daily", 
                             "Yes, weekly", 
                             "Yes, monthly", 
                             "Yes, a few times"),
                     "No" = "No"
        ),
        levels = c("No", "Yes"), ordered = FALSE
      ),
      .names = "{.col}_dic"
    )
  ) |>
  
  # Recode protocols, drop "Do not know", ensure factor levels
 
   mutate(
    across(
      all_of(protocols),
      ~ fct_recode(.x, NULL = "Do not know"),
      .names = "{.col}_dic"
    )
  ) |> 

  # relevel protocols

  mutate(
    across(
      all_of(protocols_dic),
      ~ fct_relevel(.x, "No")
    )
  ) |> 
  
  # recode protective factors (except w-l balance)
  
  mutate(
    across(
      all_of(c("work_19", "work_20", "work_21", "work_22")),
      ~ factor(
        fct_collapse(.x,
                     "No" = c("Sometimes", "Seldom", "Never / Hardly ever"),
                     "Yes" = c("Always", "Often"),
        ),
        levels = c("No", "Yes"), ordered = FALSE
      ),
      .names = "{col}_dic"
    )
  ) |> 
  
  # recode work-life balance
  
  mutate(
    work_34_dic = case_when(as.numeric(work_34) <= 3 ~ "No",
                            as.numeric(work_34) > 3 ~ "Yes"),
    work_34_dic = factor(work_34_dic, levels = c("No", "Yes"))
  ) |> 
  
  # create numeric variables
  
  mutate(
    across(
      all_of(hazards),
      ~ case_when(
        .x == "No"                ~ 0,
        .x == "Yes, a few times"  ~ 1,
        .x == "Yes, monthly"      ~ 2,
        .x == "Yes, weekly"       ~ 3,
        .x == "Yes, daily"        ~ 4,
        TRUE                      ~ NA_real_
        ),
      .names = "{.col}_num"
      )
    ) |> 
  mutate(
    across(
      all_of(demands) & !all_of("work_12"), # work_12 is binary
      \(x) as.numeric(x) - 1, # 0 as reference
    .names = "{.col}_num")) |> 
  mutate(
    across(
      all_of(resources),
      \(x) as.numeric(x) - 1, # 0 as reference
    .names = "{.col}_num")) |> 
  
  # create poisson outcomes

  mutate(
    across(
      all_of(out_dic),
      \(x) case_when(x == "Yes" ~ 1,
                     x == "No"  ~ 0,
                     TRUE       ~ NA_real_),
      .names = "{.col}_poi"
    )
  )


```

```{r dsw}
# I need this dataset for comparative weighted analyses

ds_w <- 
  
  ds |> 
  drop_na(w_country_work_sex)

```

```{r var labs}
# final labels here, following this code:

variable_labels <- readxl::read_excel("ext/var_labels_who_survey.xlsx")

for (i in 1:nrow(variable_labels)) {
  uuid <- variable_labels$Question_uuid[i]
  label <-  variable_labels$Label[i]
  ds[[uuid]] <- sjlabelled::set_label(ds[[uuid]], label)
}

rm(variable_labels,
   i,
   uuid,
   label)


```

# Missing data

This analysis was performed in the original md file.

```{r miss old}
var_names_orig <- names(ds)

names(ds) <- paste0("Item ", seq_along(ds))

var_names <-
  ds |> 
  select(1:95) |> 
  select(-c("Item 1", 
            "Item 2", 
            "Item 3", 
            "Item 4",
            "Item 5",
            "Item 6",
            "Item 7",
            "Item 8",
            "Item 9",
            "Item 11",
            "Item 12",
            "Item 13",
            "Item 14",
            "Item 15",
            "Item 17",
            "Item 18",
            "Item 24",
            "Item 25",
            "Item 28",
            "Item 30",
            "Item 31",
            "Item 66")) |>
  colnames()
  


p <- 
  
  ds |> 
  select(1:95) |> 
  select(-c("Item 1", 
            "Item 2", 
            "Item 3", 
            "Item 4",
            "Item 5",
            "Item 6",
            "Item 7",
            "Item 8",
            "Item 9",
            "Item 11",
            "Item 12",
            "Item 13",
            "Item 14",
            "Item 15",
            "Item 17",
            "Item 18",
            "Item 24",
            "Item 25",
            "Item 28",
            "Item 30",
            "Item 31",
            "Item 66")) |>  
  mutate(
    across(
      everything(),
      ~ as.character(.)
    )
  ) |>
  pivot_longer(
    everything(), 
    names_to = "variable", 
    values_to = "value"
    ) |>  
  mutate(missing = if_else(
    is.na(value), 
    "Missing", 
    "Present")) |> 
  count(variable, missing) |> 
  group_by(variable) |>
  mutate(prop = n / sum(n),
         variable = factor(variable, levels = var_names)) |> 
  filter(missing == "Missing") |>  
  ggplot(aes(x = variable, 
             y = prop)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = scales::percent,
                     limits = c(0, 0.25)) +
  scale_fill_grey(start = 0.8, end = 0.2, name = "Data") +
  theme_minimal() +
  labs(x = "Variable", 
       y = "Percent") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 9))

names(ds) <- var_names_orig

ggsave(plot = p, 
       filename = "missing_data.pdf",
       device = "pdf",
       path = "out/figures/",
       scale = 1.9,
       width = 150,
       height = 110,
       units = "mm",
       dpi = 320
       )

# For supplementary material
ragg::agg_png("out/figures/missing_data.png",
              width = 7,
              height = 5,
              units = "in",
              res = 600,
              scaling = 0.6)

print(p)

dev.off()

rm(p)
```

These analyses are new

```{r miss new ds}
ds_m <- 
  
  ds |> 
  select(loc_2,
         starts_with("scdm_"), 
         starts_with("work_"),
         -ends_with(c("_a", "_b", "_num", "_rec", "_dic", "_aux")),
         starts_with("mh_"),
         starts_with(c("wb_who_", "wb_cl", "wb_wami_")),
         -ends_with(c("_sc", "_co"))
         ) |> 
  filter(scdm_2 != "Other") |> 
  mutate(
    across(
      all_of(c(protocols, "scdm_2")),
      ~ fct_drop(.x)
      )
    )
```

```{r missing plots}
missing_summary <- miss_var_summary(ds_m)

missing_summary |> print(n = 80)

gg_miss_upset(ds_m)
```

```{r missing data tbls}
table_data <- 
  
  ds  |> 
  mutate(
    item_9_phq = ifelse(!is.na(mh_phq_9), "Responded", "No response")
  ) |> 
  select(loc_2,
         ends_with("_comp"), item_9_phq, 
         starts_with("scdm_"), 
         starts_with("work_"),
         -ends_with(c("_a", "_b", "_num", "_rec", "_dic", "_aux")),
         -starts_with(c("mh_", "mh_", "wb_who")),
         starts_with(c("wb_cl", "wb_wami_")),
         -ends_with(c("_sc", "_co"))
         ) 
  
# ---- PHQ-9 ----
missingness_table_phq <- 
  
  table_data  |> 
  tbl_summary(
    by = phq_comp,
    missing = "no"
  ) |> 
  add_p(test = list(all_categorical() ~ "chisq.test"))  |>   
  add_overall() 

missingness_table_phq |> 
  as_flex_table() |> 
  save_as_docx(path = "out/tables/miss_phq.docx")

# ---- GAD-7 ----

missingness_table_gad <- 
  
  table_data  |> 
  tbl_summary(
    by = gad_comp,
    missing = "no"
  ) |> 
  add_p(test = list(all_categorical() ~ "chisq.test"))  |>   
  add_overall() 

missingness_table_gad

# ---- CAGE ----

missingness_table_cage <- 
  
  table_data  |> 
  tbl_summary(
    by = cage_comp,
    missing = "no"
  ) |> 
  add_p(test = list(all_categorical() ~ "chisq.test"))  |>   
  add_overall() 

missingness_table_cage |> as_flex_table()

# ---- Suicidal thoughts----

missingness_table_suic <- 
  
  table_data  |> 
  tbl_summary(
    by = item_9_phq,
    missing = "no"
  ) |> 
  add_p(test = list(all_categorical() ~ "chisq.test"))  |>   
  add_overall() 

# Print
missingness_table_suic
```

# Multivariate Imputation by Chained Equations (MICE)

Everything set to eval=FALSE. This chunk loads rds files produced after imputation.

```{r load mids mice}
imp_ds <- readRDS("data/mice_imputed_data.rds") # MI ds

imputed_data_final <- readRDS("data/mice_imputed_data_scored.rds") # MI with scores

ds_imp1 <- complete(imputed_data_final, action = 1) # first MI ds

common_cols <- intersect(names(ds), names(ds_imp1))

for (col in common_cols) {
  # If the original column has a label, copy it to the new column
  if (!is.null(attr(ds[[col]], "label"))) {
    attr(ds_imp1[[col]], "label") <- attr(ds[[col]], "label")
  }
}

long_all <- complete(imputed_data_final, # required for pooling
                     action = "long", 
                     include = FALSE)

imputed_datasets <- complete(imputed_data_final,# required for assoc models
                             action = "all")

```

## Baseline setup

```{r baseline setup mice, eval = FALSE}

init_run <- mice(ds_m, 
                 maxit = 0)

# Extract default methods vector
meth <- init_run$method

# Reassign methods dynamically
for(i in names(meth)) {
  
  if(is.factor(ds_m[[i]]) || is.ordered(ds_m[[i]])) {
    meth[i] <- "cart" # Ignores collinearity traps
  } else if (is.numeric(ds_m[[i]]) || is.integer(ds_m[[i]])) {
    
    meth[i] <- "pmm"
  }
}

# Covariates need to be original, not recoded
covs_clean <- str_remove(covs_1, "_rec$|_dic$")

vars_to_impute <- 
  c(covs_clean, 
    covs_2, 
    all_exposures_bis,
    "mh_phq_1", "mh_phq_2", "mh_phq_3", "mh_phq_4", "mh_phq_5", "mh_phq_6",
    "mh_phq_7", "mh_phq_8", "mh_phq_9", 
    "mh_gad_1", "mh_gad_2", "mh_gad_3", "mh_gad_4", "mh_gad_5", "mh_gad_6",
    "mh_gad_7",
    "mh_cage_1", "mh_cage_2", "mh_cage_3", "mh_cage_4")

# Set method to "" for what is not in the list.
meth[!names(meth) %in% vars_to_impute] <- ""

# Smart predictor matrix
# mincor tells mice to use only predictors with at least 0.1 correlation
pred_smart <- quickpred(ds_m, 
                        mincor = 0.15,
                        include = "loc_2")

# Identify vars not imputed
vars_not_imputed <- names(meth)[meth == ""]

# 3Force their columns in the predictor matrix to 0
# This prevents mice from ever using them to predict anything else
pred_smart[, vars_not_imputed] <- 0

# Use more than one core
plan(multisession, workers = 4)

# Test
message("Running test drive...")
test_imputation <- mice(
  ds_m,
  method = meth,
  predictorMatrix = pred_smart, # smart matrix 
  m = 1,       
  maxit = 1,   
  seed = 123
)
```

## Run MICE

```{r run mice, eval = FALSE}
# Run imputation using custom vector
imputed_data <- futuremice(
  ds_m,
  method = meth,
  predictorMatrix = pred_smart,
  m = 20, # Standard is 20 imputations
  maxit = 5,
  parallelseed = 123
)

# Save so we don't re run
saveRDS(imputed_data, 
        file = "data/mice_imputed_data.rds")
```

## Imputed data diagnostics

```{r imp diag, eval = FALSE}


# Unpack all 20 imputations into one long dataset
# include = FALSE so we don't accidentally count the raw dataset's NAs
long_check <- complete(imp_ds, 
                       action = "long", 
                       include = FALSE)

# Count the exact number of NAs for every single column across all 20 datasets
missing_report <-
  long_check |>
  summarise(across(everything(), ~ sum(is.na(.)))) |>
  pivot_longer(
    cols = everything(), 
    names_to = "Variable", 
    values_to = "Total_NAs") |>
  # Only keep variables that still have missing data
  filter(Total_NAs > 0) |>
  arrange(desc(Total_NAs))

# Print the full report
print(missing_report, n = Inf)

# Plot the convergence for a selection of important variables

mice_plot_1_convergence <- plot(imp_ds, c("mh_phq_9", "scdm_1", "work_31", "work_8"))

# "Convergence of the MICE algorithm was confirmed via visual inspection of trace plots for the means and standard deviations of the imputed variables. The imputation chains intermingled freely and exhibited no discernible trends or pathological behavior across the 5 iterations, confirming successful convergence."

# density plot. Should be similar

# Visual check that imputed values are plausible

# Red = imputed, Blue = observed
densityplot(imp_ds, ~ mh_phq_1 + mh_phq_9 + work_8 + work_31)

stripplot(imp_ds, work_11 + work_30 + work_33 ~ .imp, pch = 20, cex = 1.2) # spread should be similar
```

## Transform variables new scores

```{r compute outcome scores, eval = FALSE}

# Define country-specific cut-offs
# Create objects with cut-off scores per country

phq_co_st <- c("Belgium",
               "Bulgaria",
               "Croatia",
               "Cyprus",
               "Czechia",
               "Denmark",
               "Estonia",
               "Finland",
               "France",
               "Greece",
               "Hungary",
               "Ireland",
               "Italy",
               "Luxembourg",
               "Malta",
               "Netherlands",
               "Norway",
               "Poland",
               "Romania",
               "Slovakia",
               "Armenia",
               "Azerbaijan",
               "Georgia",
               "Moldova",
               "Ukraine")

phq_co_8 <- "Latvia"

phq_co_9 <- c("Portugal",
              "Slovenia")

phq_co_11 <- c("Austria",
               "Germany",
               "Lithuania")

phq_co_12 <- c("Iceland",
               "Spain",
               "Sweden")

gad_co_st <- c("Austria",
               "Belgium",
               "Bulgaria",
               "Croatia",
               "Cyprus",
               "Czechia",
               "Denmark",
               "Estonia",
               "Germany",
               "Greece",
               "Hungary",
               "Iceland",
               "Ireland",
               "Italy",
               "Luxembourg",
               "Poland",
               "Romania",
               "Slovakia",
               "Slovenia",
               "Spain",
               "Armenia",
               "Azerbaijan",
               "Georgia",
               "Moldova",
               "Ukraine")

gad_co_5 <- "Latvia"

gad_co_7 <- c("Finland",
              "France")

gad_co_8 <- c("Malta",
              "Norway",
              "Portugal",
              "Sweden")

gad_co_9 <- "Lithuania"

gad_co_12 <- "Netherlands"


# Extract all 20 datasets into one "long" dataframe.
# include = TRUE pulls out original raw dataset as well (Dataset 0). 
# We must have this to package it back up into a MICE object later!

long_data <- complete(imp_ds, 
                      action = "long",
                      include = TRUE)

# Calculate the total scores across all rows
long_data_scored <- 
  
  long_data  |>
  mutate(
    phq_sc = rowSums(pick(mh_phq_1:mh_phq_9)),
    gad_sc = rowSums(pick(mh_gad_1:mh_gad_7)),
    cage_sc = rowSums(pick(mh_cage_1:mh_cage_4)),
    wb_who_sc = rowSums(pick(wb_who_1:wb_who_5)) * 4
  ) |> 
  ungroup() |> 
  # Now the cut-offs
  mutate(
    # Assign the correct threshold based on country
    phq_threshold = case_when(
      loc_2 %in% phq_co_st ~ 10,
      loc_2 %in% phq_co_8  ~ 8, 
      loc_2 %in% phq_co_9  ~ 9,
      loc_2 %in% phq_co_11 ~ 11,
      loc_2 %in% phq_co_12 ~ 12
    ),
    
    gad_threshold = case_when(
      loc_2 %in% gad_co_st ~ 10,
      loc_2 == gad_co_5    ~ 5,
      loc_2 %in% gad_co_7  ~ 7,
      loc_2 %in% gad_co_8  ~ 8,
      loc_2 == gad_co_9    ~ 9,
      loc_2 == gad_co_12   ~ 12
    ),
    
    # Create the clean binary Poisson outcomes (1 = case, 0 = healthy)
    phq_co_poi = as.numeric(phq_sc >= phq_threshold),
    gad_co_poi = as.numeric(gad_sc >= gad_threshold),
    
    # CAGE
    cage_co_poi = as.numeric(cage_sc > 2),
    
    # Item 9 PHQ
    suic_idea_poi = as.numeric(mh_phq_9 > 0),
    
    # WHO-5
    wb_who_co = as.numeric(wb_who_sc >= 50)
  )
```

```{r compute exp and covs, eval = FALSE}
# Re-create exposures recoding

long_data_transformed <- 
  
  long_data_scored |> 
  
  mutate(scdm_1_rec = fct_collapse(scdm_1,
                                   "<30" = c("Under 20", "20-25", "26-30"),
                                   "30-39" = c("31-35", "36-40"),
                                   "40-49" = c("41-45", "46-50"),
                                   "50-59" = c("51-55", "56-60"),
                                   "60+" = c("61-65", "66-70", "Over 70")
                                   )
         ) |> 
  
  mutate(scdm_5_dic = case_when(
    str_detect(scdm_5, "with children") ~ "Has children",
    str_detect(scdm_5, "without children") ~ "No children",
    TRUE ~ NA
    ),
    scdm_5_dic = factor(scdm_5_dic,
                        levels = c("Has children", "No children"),
                        ordered = FALSE)
  ) |>
  
  # recode length of service
  
  mutate(work_3_rec = fct_collapse(
    work_3,
    "5 years or less" = c("Less than 1 year", "1-3 years", "4-5 years"),
    "More than 10 years" = c("11-20 years", "21-30 years", "31-40 years",
                             "More than 40 years")
    )
  ) |> 
  
  # job positions
  
  mutate(
    work_4_dic = if_else(work_4 == "One",
                         "One",
                         "More than one"),
    work_4_dic = factor(work_4_dic,
                        levels = c("One", "More than one"))
  ) |> 
  
  # work setting
  
   mutate(work_5_rec = fct_collapse( 
    work_5,
    "Inpatient" = c("Emergency department",
                    "In-hospital care"),
    "Outpatient" = c("Outpatient primary care",
                     "Outpatient secondary care"),
    "Other" = c("Extra-hospital emergencies",
                "Other")
  )
  ) |> 
  
  # recode working hours
  
    
  mutate(
    work_8_dic = case_when(
      work_8 %in% c("< 11 h", "11-20 h", "21-30 h", "31-40 h", "41-50 h") ~ "No", # <= 50h
      work_8 %in% c("51-60 h", "61-70 h", "> 70 h") ~ "Yes"), # > 50h
    work_8_dic = factor(work_8_dic, levels = c("No", "Yes"))
  ) |> 
  
  # recode night work

  mutate(
    work_11_dic = case_when(
      work_11 %in% c("1-2 times/month", "Less than monthly", "Never/Rarely") ~ "No", # 1 or 2x a month or less
      work_11 %in% c("Daily", "Almost daily", "2-3 days/week", "Once a week", "Almost weekly") ~ "Yes"), # Almost every week and more
    work_11_dic = factor(work_11_dic, levels = c("No", "Yes")),
    work_11 = fct_rev(work_11)
  ) |> 
  
  # name var for shifts
  
  mutate(work_12_dic = factor(work_12, levels = c("No", "Yes"))
  ) |> 
  
  # create dichotomic for contract type
  
  mutate(work_16_dic = fct_recode(work_16,
                                  "Yes" = "Temporary contract",
                                  "No" = "Fixed contract"),
         work_16_dic = factor(work_16_dic,
                              levels = c("No", "Yes"),
                              ordered = FALSE)
  ) |> 
  
  # recode managing patient anger
  
  mutate(
    across(
      all_of(c("work_23", "work_24")),
      ~ factor(
        fct_collapse(.x,
                     "Yes" = c("Around 1/4 of the time",
                               "Around half of the time",
                               "Around 3/4 of the time",
                               "Almost all of the time",
                               "All of the time"),
                     "No" = c("Never",
                              "Almost never")),
                     levels = c("No", "Yes"),
                     ordered = FALSE),
        .names = "{.col}_dic"
        )
      ) |> 
  
  # recode violence
  
   mutate(
    across(
      all_of(hazards),
      ~ factor(
        fct_collapse(.x,
                     "Yes" = c("Yes, daily", 
                             "Yes, weekly", 
                             "Yes, monthly", 
                             "Yes, a few times"),
                     "No" = "No"
        ),
        levels = c("No", "Yes"), ordered = FALSE
      ),
      .names = "{.col}_dic"
    )
  ) |>
  
  # Recode protocols, drop "Do not know", ensure factor levels
 
   mutate(
    across(
      all_of(protocols),
      ~ fct_recode(.x, NULL = "Do not know"),
      .names = "{.col}_dic"
    )
  ) |> 

  # relevel protocols

  mutate(
    across(
      all_of(protocols),
      ~ fct_relevel(factor(.x), "No"),
      .names = "{.col}_dic"
    )
  ) |> 
  
  # recode protective factors (except w-l balance)
  
  mutate(
    across(
      all_of(c("work_19", "work_20", "work_21", "work_22")),
      ~ factor(
        fct_collapse(.x,
                     "No" = c("Sometimes", "Seldom", "Never / Hardly ever"),
                     "Yes" = c("Always", "Often"),
        ),
        levels = c("No", "Yes"), ordered = FALSE
      ),
      .names = "{.col}_dic"
    )
  ) |> 
  
  # recode work-life balance
  
  mutate(
    work_34_dic = case_when(
      work_34 %in% c("To a very small extent", "To a small extent", "To a moderate extent") ~ "No",
      work_34 %in% c("To a large extent", "To a very large extent") ~ "Yes"),
    work_34_dic = factor(work_34_dic, levels = c("No", "Yes"))
  ) |> 
  
  # create numeric variables
  
  mutate(
    across(
      all_of(hazards),
      ~ case_when(
        .x == "No"                ~ 0,
        .x == "Yes, a few times"  ~ 1,
        .x == "Yes, monthly"      ~ 2,
        .x == "Yes, weekly"       ~ 3,
        .x == "Yes, daily"        ~ 4,
        TRUE                      ~ NA_real_
        ),
      .names = "{.col}_num"
      )
    ) |> 
  mutate(
    across(
      all_of(demands) & !all_of("work_12"), # work_12 is binary
      \(x) as.numeric(x) - 1, # 0 as reference
    .names = "{.col}_num")) |> 
  mutate(
    across(
      all_of(resources),
      \(x) as.numeric(x) - 1, # 0 as reference
    .names = "{.col}_num"))
```

```{r wrap it up, eval = FALSE}

imputed_data_final <- as.mids(long_data_transformed)



saveRDS(imputed_data_final, file = "data/mice_imputed_data_scored.rds")


rm(gad_co_12, gad_co_5, gad_co_7, gad_co_8, gad_co_9, gad_co_st, phq_co_11, 
   phq_co_12, phq_co_8, phq_co_9, phq_co_st)
```

# Main analyses with MICE

## Sociodemographics

```{r scdm imp}

# ---- DS 1 ----

t1 <- 
  
  ds_imp1 |> 
  mutate(scdm_2 = fct_drop(scdm_2)) |>
  filter(!is.na(scdm_2)) |> 
  select(all_of(c(scdm, covs_1))) |> 
  tbl_strata(
    strata = work_2,
    .tbl_fun = ~ tbl_summary(
      .x, 
      by = scdm_2,
      missing = "no") |> 
      add_overall()
  ) |> 
  as_flex_table()

save_as_docx(t1, path = "out/tables/scdm_tbl_imp.docx")
```

## Exposures

```{r exp imp}

# ---- DS 1 ----

# Table 2

t_exp <- 
  ds_imp1 |> 
  select(all_of(c("work_2", "scdm_2", all_exposures_bis))) |> 
  tbl_strata(
    strata = work_2,
    .tbl_fun = ~ tbl_summary(
      .x, 
      by = scdm_2,
      missing = "no") |> 
      add_overall()
  ) 

# Group exposures and add labels
t_exp_groups <- 
  
  t_exp |> 
  as_tibble() |> 
  mutate(groupname_col = case_when(
      `**Characteristic**` %in% c("Extended working hours", "Frequent night shifts",
                  "Frequent rotating shifts", "Tight deadlines",
                  "Managing patient and relative anger") ~ "Job demands",
      `**Characteristic**` %in% c("Sexual harassment", "Violent threats",
                  "Physical violence", "Bullying") ~ "Job hazards",
      `**Characteristic**` %in% c("Influence over work", "Influence over work (breaks)",
                  "Colleague support", "Support from superiors") ~ "Job resources",
      `**Characteristic**` %in% c("Work council or union", "Mechanisms for employee feedback",
                  "Workplace stress action plan", "Bullying and harassment protocols", "Violence protocols") ~ "Organisational support structures",
      TRUE ~ NA_character_
  )) |> 
  tidyr::fill(groupname_col, .direction  = "down") |> 
  flextable::as_grouped_data(groups = "groupname_col") |> 
  flextable() |> 
  set_header_labels(
    values = setNames(
      gsub("\\*\\*", "", names(as_tibble(t_exp))), 
      names(as_tibble(t_exp))
      )) |> 
  set_header_labels(
    groupname_col = "Group",
    Characteristic = "Exposure"
  )|> 
  add_header_row(
    values = c("", "",  "Doctor", "Nurse"),
    colwidths = c(1, 1, 3, 3) 
  ) |> 
  align(i = 1, align = "center", part = "header") |> 
  bold(i = 1, part = "header") |> 
  bold(i = ~ !is.na(groupname_col), j = 1) 
  # Removed the italicizing of the "Missing" rows, since they no longer exist!

save_as_docx(t_exp_groups, path = "out/tables/exp_tbl_imp1.docx")

# ---- Pooled ---- 

# Format
base_exp_data <- 
  
  long_all |>
  select(work_2, scdm_2, all_of(all_exposures)) |>
  mutate(
    across(
      all_of(all_exposures), 
      ~ if_else(.x == "Yes", 1, 0)
      )
    )

# Function to calculate data
pooled_exp_stats <- 
  function(data) {
  
    data |>
    summarise(
      True_N = n() / 20,
      
      hrs_n      = round(sum(work_8_dic == 1, na.rm = TRUE) / 20),
      nights_n   = round(sum(work_11_dic == 1, na.rm = TRUE) / 20),
      shifts_n   = round(sum(work_12_dic == 1, na.rm = TRUE) / 20),
      deadlines_n= round(sum(work_23_dic == 1, na.rm = TRUE) / 20),
      angry_n    = round(sum(work_24_dic == 1, na.rm = TRUE) / 20),
      
      harass_n   = round(sum(work_30_dic == 1, na.rm = TRUE) / 20),
      threats_n  = round(sum(work_31_dic == 1, na.rm = TRUE) / 20),
      viol_n     = round(sum(work_32_dic == 1, na.rm = TRUE) / 20),
      bull_n     = round(sum(work_33_dic == 1, na.rm = TRUE) / 20),
      
      influence_n= round(sum(work_19_dic == 1, na.rm = TRUE) / 20),
      breaks_n   = round(sum(work_20_dic == 1, na.rm = TRUE) / 20),
      cols_n     = round(sum(work_21_dic == 1, na.rm = TRUE) / 20),
      sup_n      = round(sum(work_22_dic == 1, na.rm = TRUE) / 20),
      
      council_n  = round(sum(work_25_dic == 1, na.rm = TRUE) / 20),
      feedback_n = round(sum(work_26_dic == 1, na.rm = TRUE) / 20),
      stressplan_n= round(sum(work_27_dic == 1, na.rm = TRUE) / 20),
      harprot_n  = round(sum(work_28_dic == 1, na.rm = TRUE) / 20),
      vioprot_n  = round(sum(work_29_dic == 1, na.rm = TRUE) / 20),
      
      hrs_pct      = mean(work_8_dic == 1, na.rm = TRUE) * 100,
      nights_pct   = mean(work_11_dic == 1, na.rm = TRUE) * 100,
      shifts_pct   = mean(work_12_dic == 1, na.rm = TRUE) * 100,
      deadlines_pct= mean(work_23_dic == 1, na.rm = TRUE) * 100,
      angry_pct    = mean(work_24_dic == 1, na.rm = TRUE) * 100,
      
      harass_pct   = mean(work_30_dic == 1, na.rm = TRUE) * 100,
      threats_pct  = mean(work_31_dic == 1, na.rm = TRUE) * 100,
      viol_pct     = mean(work_32_dic == 1, na.rm = TRUE) * 100,
      bull_pct     = mean(work_33_dic == 1, na.rm = TRUE) * 100,
      
      influence_pct= mean(work_19_dic == 1, na.rm = TRUE) * 100,
      breaks_pct   = mean(work_20_dic == 1, na.rm = TRUE) * 100,
      cols_pct     = mean(work_21_dic == 1, na.rm = TRUE) * 100,
      sup_pct      = mean(work_22_dic == 1, na.rm = TRUE) * 100,
      
      council_pct  = mean(work_25_dic == 1, na.rm = TRUE) * 100,
      feedback_pct = mean(work_26_dic == 1, na.rm = TRUE) * 100,
      stressplan_pct= mean(work_27_dic == 1, na.rm = TRUE) * 100,
      harprot_pct  = mean(work_28_dic == 1, na.rm = TRUE) * 100,
      vioprot_pct  = mean(work_29_dic == 1, na.rm = TRUE) * 100,
      
      .groups = "drop"
    )
  }

# Calculate by subgroup
pooled_gen_exp <-
  
  base_exp_data |> 
  group_by(work_2, scdm_2) |> 
  pooled_exp_stats() |> 
  mutate(Gender = as.character(scdm_2))

pooled_ovrl_exp <- 
  
  base_exp_data |> 
  group_by(work_2) |> 
  pooled_exp_stats() |> 
  mutate(Gender = "Overall")

# Format function
fmt <- 
  function(n, pct) {
    
    sprintf("%s (%.0f%%)", format(n, big.mark = ","), pct)
    
    }

# Merge, format and clean
pooled_table2_raw <- 
  
  bind_rows(pooled_ovrl_exp, pooled_gen_exp) |>
  mutate(
    `Extended working hours`       = fmt(hrs_n, hrs_pct),
    `Frequent night shifts`        = fmt(nights_n, nights_pct),
    `Regular shift work`           = fmt(shifts_n, shifts_pct),
    `Tight deadlines`              = fmt(deadlines_n, deadlines_pct),
    `Angry patients or relatives`  = fmt(angry_n, angry_pct),
    
    `Sexual harassment`            = fmt(harass_n, harass_pct),
    `Violent threats`              = fmt(threats_n, threats_pct),
    `Physical violence`            = fmt(viol_n, viol_pct),
    `Bullying`                     = fmt(bull_n, bull_pct),
    
    `Influence over work`          = fmt(influence_n, influence_pct),
    `Influence over work (breaks)` = fmt(breaks_n, breaks_pct),
    `Colleague support`            = fmt(cols_n, cols_pct),
    `Support from superiors`       = fmt(sup_n, sup_pct),
    
    `Work council or union`        = fmt(council_n, council_pct),
    `Employee feedback`            = fmt(feedback_n, feedback_pct),
    `Stress action plan`           = fmt(stressplan_n, stressplan_pct),
    `Harassment protocol`          = fmt(harprot_n, harprot_pct),
    `Violence protocol`            = fmt(vioprot_n, vioprot_pct)
  ) |>
  select(-ends_with(c("_n", "_pct")), -True_N, -scdm_2) |> 
  rename(Profession = work_2)

# Pivot the table 
pooled_table2_final <- 
  
  pooled_table2_raw |>
  pivot_longer(
    cols = -c(Gender, Profession),
    names_to = "Characteristic",
    values_to = "Value"
  ) |>
  pivot_wider(
    names_from = c(Profession, Gender),
    values_from = Value
  ) |>
  # Enforce the correct column order
  select(Characteristic, 
         Doctor_Overall, Doctor_Female, Doctor_Male, 
         Nurse_Overall, Nurse_Female, Nurse_Male) |> 
  
  # Inject grouping logic
  mutate(groupname_col = case_when(
    Characteristic %in% c("Extended working hours", "Frequent night shifts",
                          "Regular shift work", "Tight deadlines",
                          "Angry patients or relatives") ~ "Job demands",
    Characteristic %in% c("Sexual harassment", "Violent threats",
                          "Physical violence", "Bullying") ~ "Job hazards",
    Characteristic %in% c("Influence over work", "Influence over work (breaks)",
                          "Colleague support", "Support from superiors") ~ "Job resources",
    Characteristic %in% c("Work council or union", "Employee feedback",
                          "Stress action plan", "Harassment protocol", "Violence protocol") ~ "Organisational support structures",
    TRUE ~ NA_character_
  )) |> 
  flextable::as_grouped_data(groups = "groupname_col") |> 
  flextable() |> 
  
  # Rename the columns to be clean
  set_header_labels(
    groupname_col  = "Group",
    Characteristic = "Exposure",
    Doctor_Overall = "Overall",
    Doctor_Female  = "Female",
    Doctor_Male    = "Male",
    Nurse_Overall  = "Overall",
    Nurse_Female   = "Female",
    Nurse_Male     = "Male"
  ) |> 
  
  # Spanner (Colwidths match 1 for group and exp, 3 for Docs, 3 for Nurses)
  add_header_row(
    values = c("", "Doctor", "Nurse"),
    colwidths = c(2, 3, 3) 
  ) |> 
  
  # Final styling
  align(i = 1, align = "center", part = "header") |> 
  bold(i = 1, part = "header") |> 
  bold(i = ~ !is.na(groupname_col), j = 1) |> 
  autofit()

# Save the beautifully pooled table
save_as_docx(pooled_table2_final, path = "out/tables/exp_tbl_imp_pooled.docx")
```

## Outcomes

```{r out imp 1, eval = FALSE}

# ---- DS 1 ----

t_out <- 
  
  ds_imp1 |> 
  mutate(scdm_2 = fct_drop(scdm_2)) |>
  mutate(
    across(
      all_of(out_poisson),
      \(x) if_else(x == 1, "Yes", "No"),
      .names = "{str_remove(.col, '_poi')}"
    )
  ) |> 
  filter(!is.na(scdm_2)) |>
  select(all_of(c("work_2", "scdm_2", out_dic))) |> 
  tbl_strata(
    strata = work_2,
    .tbl_fun = ~ tbl_summary(
      .x, 
      by = scdm_2,
      label = list(
        phq_co ~ "Probable depression",
        gad_co ~ "Probable anxiety",
        suic_idea ~ "Suicidal thoughts",
        cage_co ~ "Probable alcohol dependence"
      ),
      missing = "no") |> 
      add_overall()
  ) |> 
  as_flex_table()

save_as_docx(t_out, path = "out/tables/out_tbl_imp1.docx")

# ---- Pooled ----

# Format
base_out_data <- 
  
  long_all |>
  select(work_2, scdm_2, all_of(out_poisson)) 

# Function to calculate data
pooled_out_stats <- 
  function(data) {
  
    data |>
    summarise(
      True_N = n() / 20,
      
      dep_n      = round(sum(phq_co_poi == 1, na.rm = TRUE) / 20),
      anx_n   = round(sum(gad_co_poi == 1, na.rm = TRUE) / 20),
      suic_n   = round(sum(suic_idea_poi == 1, na.rm = TRUE) / 20),
      alc_n= round(sum(cage_co_poi == 1, na.rm = TRUE) / 20),
      
      dep_pct      = mean(phq_co_poi == 1, na.rm = TRUE) * 100,
      anx_pct   = mean(gad_co_poi == 1, na.rm = TRUE) * 100,
      suic_pct   = mean(suic_idea_poi == 1, na.rm = TRUE) * 100,
      alc_pct= mean(cage_co_poi == 1, na.rm = TRUE) * 100,
      
      .groups = "drop"
    )
  }

# Calculate by subgroup
pooled_gen_out <-
  
  base_out_data |> 
  group_by(work_2, scdm_2) |> 
  pooled_out_stats() |> 
  mutate(Gender = as.character(scdm_2))

pooled_ovrl_out <- 
  
  base_out_data |> 
  group_by(work_2) |> 
  pooled_out_stats() |> 
  mutate(Gender = "Overall")

# Format function
fmt <- 
  function(n, pct) {
    
    sprintf("%s (%.0f%%)", format(n, big.mark = ","), pct)
    
    }

# Merge, format and clean
pooled_table3_raw <- 
  
  bind_rows(pooled_ovrl_out, pooled_gen_out) |>
  mutate(
    `Probable depression`         = fmt(dep_n, dep_pct),
    `Probable anxiety`            = fmt(anx_n, anx_pct),
    `Suicidal thoughts`           = fmt(suic_n, suic_pct),
    `Probable alcohol dependence` = fmt(alc_n, alc_pct),
    ) |>
  select(-ends_with(c("_n", "_pct")), -True_N, -scdm_2) |> 
  rename(Profession = work_2)

# Pivot the table 
pooled_table3_final <- 
  
  pooled_table3_raw |>
  pivot_longer(
    cols = -c(Gender, Profession),
    names_to = "Characteristic",
    values_to = "Value"
  ) |>
  pivot_wider(
    names_from = c(Profession, Gender),
    values_from = Value
  ) |>
  # Enforce the correct column order
  select(Characteristic, 
         Doctor_Overall, Doctor_Female, Doctor_Male, 
         Nurse_Overall, Nurse_Female, Nurse_Male) |> 
  flextable() |> 
  
  # Rename the columns to be clean
  set_header_labels(
    Characteristic = "Outcome",
    Doctor_Overall = "Overall",
    Doctor_Female  = "Female",
    Doctor_Male    = "Male",
    Nurse_Overall  = "Overall",
    Nurse_Female   = "Female",
    Nurse_Male     = "Male"
  ) |> 
  
  # Spanner (Colwidths match 1 for outcome, 3 for Docs, 3 for Nurses)
  add_header_row(
    values = c("", "Doctor", "Nurse"),
    colwidths = c(1, 3, 3) 
  ) |> 
  
  # Final styling
  align(i = 1, align = "center", part = "header") |> 
  bold(i = 1, part = "header") |> 
  autofit()

# Save the beautifully pooled table
save_as_docx(pooled_table3_final, path = "out/tables/out_tbl_imp_pooled.docx")
```

## Associations

```{r exp-out prep}

profs <- levels(ds$work_2)

covariate_map <- list("base_covs" = covs_1)

tasks_all <- expand_grid(
  Outcome = out_poisson,
  Family = "poisson", 
  Exposure = all_exposures,
  Covar_Key = "base_covs",
  profession = "All"
  )

#---- Setup machine ----

# # Increase the future package's memory limit to 3 Gigabytes
# options(future.globals.maxSize = 3 * 1024^3)
# # SET UP SAFE PARALLEL PROCESSING (4 Cores to protect 16GB RAM)
# plan(multisession, workers = 2)

```

```{r imp model run dep agg, eval = FALSE}

# filter DEP

tasks_run <- tasks_all |> filter(Outcome == "phq_co_poi")

exp_out_all_imp_dep <- future_pmap(list(
    tasks_run$Outcome,
    tasks_run$Family,
    tasks_run$Exposure,
    tasks_run$Covar_Key,
    tasks_run$profession
    ), function(outcome, family, exposure, cov_key, prof) {
  
    # Run models across all 20 datasets sequentially within each core
    imp_results <-
      imap(imputed_datasets, 
           function(ds_i, i) {
    
    # Define a unique folder for each imputation 
    current_out_dir <- paste0("out/models/imputed/imp_", i)
      
      res_crude <- 
        run_crude_glm(
          data = ds_i,
          outcome_var = outcome, 
          exposure_var = exposure, 
          profession = prof, 
          cluster_var = covs_2, 
          family_type = family,
          output_dir = current_out_dir
          )
      
      res_adj <- 
        run_adj_glm(
          data = ds_i, 
          outcome_var = outcome, 
          exposure_var = exposure,
          profession = prof, 
          cluster_var = covs_2, 
          family_type = family,
          confounder_list = covariate_map[[cov_key]], 
          model_label = "Adjusted",
          output_dir = current_out_dir
          )
      
      return(list(crude = res_crude, adj = res_adj))
      })
    
    # Extract and stack the 20 sets of results
    crude_ml_stack <- map_dfr(imp_results, ~ .x$crude$multilevel)
    crude_rb_stack <- map_dfr(imp_results, ~ .x$crude$robust)
    adj_ml_stack   <- map_dfr(imp_results, ~ .x$adj$multilevel)
    adj_rb_stack   <- map_dfr(imp_results, ~ .x$adj$robust)
    
    # Pool them using Rubin's Rules
    row_multilevel <- 
      bind_rows(
        pool_rubins_rules(crude_ml_stack),
        pool_rubins_rules(adj_ml_stack)
        )
    
    row_robust <- 
      bind_rows(
        pool_rubins_rules(crude_rb_stack),
        pool_rubins_rules(adj_rb_stack)
        )
    
    return(list(
      multilevel = row_multilevel,
      robust     = row_robust
    ))
    
  }, .options = furrr_options(seed = TRUE))

# Unzip, Combine, and Save

imp_multilevel_df_dep <- map_dfr(exp_out_all_imp_dep, "multilevel")
imp_robust_df_dep <- map_dfr(exp_out_all_imp_dep, "robust")

saveRDS(imp_multilevel_df_dep, "out/dataframes/imp_multilevel_df_dep.rds")
saveRDS(imp_robust_df_dep, "out/dataframes/imp_robust_df_dep.rds")
```

```{r imp model run anx agg, eval = FALSE}
# filter ANX

tasks_run <- tasks_all |> filter(Outcome == "gad_co_poi")

exp_out_all_imp_anx <- future_pmap(list(
    tasks_run$Outcome,
    tasks_run$Family,
    tasks_run$Exposure,
    tasks_run$Covar_Key,
    tasks_run$profession
    ), function(outcome, family, exposure, cov_key, prof) {
  
    # Run models across all 20 datasets sequentially within each core
    imp_results <-
      imap(imputed_datasets, 
           function(ds_i, i) {
    
    # Define a unique folder for each imputation 
    current_out_dir <- paste0("out/models/imputed/imp_", i)
      
      res_crude <- 
        run_crude_glm(
          data = ds_i,
          outcome_var = outcome, 
          exposure_var = exposure, 
          profession = prof, 
          cluster_var = covs_2, 
          family_type = family,
          output_dir = current_out_dir
          )
      
      res_adj <- 
        run_adj_glm(
          data = ds_i, 
          outcome_var = outcome, 
          exposure_var = exposure,
          profession = prof, 
          cluster_var = covs_2, 
          family_type = family,
          confounder_list = covariate_map[[cov_key]], 
          model_label = "Adjusted",
          output_dir = current_out_dir
          )
      
      return(list(crude = res_crude, adj = res_adj))
      })
    
    # Extract and stack the 20 sets of results
    crude_ml_stack <- map_dfr(imp_results, ~ .x$crude$multilevel)
    crude_rb_stack <- map_dfr(imp_results, ~ .x$crude$robust)
    adj_ml_stack   <- map_dfr(imp_results, ~ .x$adj$multilevel)
    adj_rb_stack   <- map_dfr(imp_results, ~ .x$adj$robust)
    
    # Pool them using Rubin's Rules
    row_multilevel <- 
      bind_rows(
        pool_rubins_rules(crude_ml_stack),
        pool_rubins_rules(adj_ml_stack)
        )
    
    row_robust <- 
      bind_rows(
        pool_rubins_rules(crude_rb_stack),
        pool_rubins_rules(adj_rb_stack)
        )
    
    return(list(
      multilevel = row_multilevel,
      robust     = row_robust
    ))
    
  }, .options = furrr_options(seed = TRUE))

imp_multilevel_df_anx <- map_dfr(exp_out_all_imp_anx, "multilevel")
imp_robust_df_anx <- map_dfr(exp_out_all_imp_anx, "robust")

saveRDS(imp_multilevel_df_anx, "out/dataframes/imp_multilevel_df_anx.rds")
saveRDS(imp_robust_df_anx, "out/dataframes/imp_robust_df_anx.rds")
```

```{r imp model run suic agg, eval = FALSE}
# filter SUIC

tasks_run <- tasks_all |> filter(Outcome == "suic_idea_poi")

exp_out_all_imp_suic <- future_pmap(list(
    tasks_run$Outcome,
    tasks_run$Family,
    tasks_run$Exposure,
    tasks_run$Covar_Key,
    tasks_run$profession
    ), function(outcome, family, exposure, cov_key, prof) {
  
    # Run models across all 20 datasets sequentially within each core
    imp_results <-
      imap(imputed_datasets, 
           function(ds_i, i) {
    
    # Define a unique folder for each imputation 
    current_out_dir <- paste0("out/models/imputed/imp_", i)
      
      res_crude <- 
        run_crude_glm(
          data = ds_i,
          outcome_var = outcome, 
          exposure_var = exposure, 
          profession = prof, 
          cluster_var = covs_2, 
          family_type = family,
          output_dir = current_out_dir
          )
      
      res_adj <- 
        run_adj_glm(
          data = ds_i, 
          outcome_var = outcome, 
          exposure_var = exposure,
          profession = prof, 
          cluster_var = covs_2, 
          family_type = family,
          confounder_list = covariate_map[[cov_key]], 
          model_label = "Adjusted",
          output_dir = current_out_dir
          )
      
      return(list(crude = res_crude, adj = res_adj))
      })
    
    # Extract and stack the 20 sets of results
    crude_ml_stack <- map_dfr(imp_results, ~ .x$crude$multilevel)
    crude_rb_stack <- map_dfr(imp_results, ~ .x$crude$robust)
    adj_ml_stack   <- map_dfr(imp_results, ~ .x$adj$multilevel)
    adj_rb_stack   <- map_dfr(imp_results, ~ .x$adj$robust)
    
    # Pool them using Rubin's Rules
    row_multilevel <- 
      bind_rows(
        pool_rubins_rules(crude_ml_stack),
        pool_rubins_rules(adj_ml_stack)
        )
    
    row_robust <- 
      bind_rows(
        pool_rubins_rules(crude_rb_stack),
        pool_rubins_rules(adj_rb_stack)
        )
    
    return(list(
      multilevel = row_multilevel,
      robust     = row_robust
    ))
    
  }, .options = furrr_options(seed = TRUE))

imp_multilevel_df_suic <- map_dfr(exp_out_all_imp_suic, "multilevel")
imp_robust_df_suic <- map_dfr(exp_out_all_imp_suic, "robust")

saveRDS(imp_multilevel_df_suic, "out/dataframes/imp_multilevel_df_suic.rds")
saveRDS(imp_robust_df_suic, "out/dataframes/imp_robust_df_suic.rds")
```

```{r imp model run alc agg, eval = FALSE}
# filter ALC

tasks_run <- tasks_all |> filter(Outcome == "cage_co_poi")

exp_out_all_imp_alc <- future_pmap(list(
    tasks_run$Outcome,
    tasks_run$Family,
    tasks_run$Exposure,
    tasks_run$Covar_Key,
    tasks_run$profession
    ), function(outcome, family, exposure, cov_key, prof) {
  
    # Run models across all 20 datasets sequentially within each core
    imp_results <-
      imap(imputed_datasets, 
           function(ds_i, i) {
    
    # Define a unique folder for each imputation 
    current_out_dir <- paste0("out/models/imputed/imp_", i)
      
      res_crude <- 
        run_crude_glm(
          data = ds_i,
          outcome_var = outcome, 
          exposure_var = exposure, 
          profession = prof, 
          cluster_var = covs_2, 
          family_type = family,
          output_dir = current_out_dir
          )
      
      res_adj <- 
        run_adj_glm(
          data = ds_i, 
          outcome_var = outcome, 
          exposure_var = exposure,
          profession = prof, 
          cluster_var = covs_2, 
          family_type = family,
          confounder_list = covariate_map[[cov_key]], 
          model_label = "Adjusted",
          output_dir = current_out_dir
          )
      
      return(list(crude = res_crude, adj = res_adj))
      })
    
    # Extract and stack the 20 sets of results
    crude_ml_stack <- map_dfr(imp_results, ~ .x$crude$multilevel)
    crude_rb_stack <- map_dfr(imp_results, ~ .x$crude$robust)
    adj_ml_stack   <- map_dfr(imp_results, ~ .x$adj$multilevel)
    adj_rb_stack   <- map_dfr(imp_results, ~ .x$adj$robust)
    
    # Pool them using Rubin's Rules
    row_multilevel <- 
      bind_rows(
        pool_rubins_rules(crude_ml_stack),
        pool_rubins_rules(adj_ml_stack)
        )
    
    row_robust <- 
      bind_rows(
        pool_rubins_rules(crude_rb_stack),
        pool_rubins_rules(adj_rb_stack)
        )
    
    return(list(
      multilevel = row_multilevel,
      robust     = row_robust
    ))
    
  }, .options = furrr_options(seed = TRUE))

imp_multilevel_df_alc <- map_dfr(exp_out_all_imp_alc, "multilevel")
imp_robust_df_alc <- map_dfr(exp_out_all_imp_alc, "robust")

saveRDS(imp_multilevel_df_alc, "out/dataframes/imp_multilevel_df_alc.rds")
saveRDS(imp_robust_df_alc, "out/dataframes/imp_robust_df_alc.rds")
```

```{r combine}

# Load all RDS files from dataframes folder
dataframe_files <- list.files(
  path = "out/models/summary",
  pattern = "\\.rds$",
  full.names = TRUE
)

for (file in dataframe_files) {
  # Extract name from filename (remove .rds)
  name <- tools::file_path_sans_ext(basename(file))
  
  # Load and assign to environment
  assign(name, readRDS(file))
  
  cat("Loaded:", name, "\n")
}

# Combine all dataframes starting with "imp_"
imp_mods_all <- 
  
  bind_rows(mget(ls(pattern = "^imp_multilevel|^imp_robust"))) |> 
  mutate(imp = "mice",
         model = case_when(
           model == "Poisson + RSVE"     ~ "Robust SE",
           model == "Multilevel Poisson" ~ "Multilevel",
           TRUE                          ~ model)
         ) |> 
  select(!Profession)

saveRDS(imp_mods_all, "out/models/summary/imp_mods_all.rds")

# Combine all dataframes of complete-cases

cc_mods_all <- 
  
  bind_rows(glm_multilevel_df_extended, glm_robust_df_extended) |> 
  mutate(imp = "cc") |> 
  filter(Family_Type == "poisson") |> 
  select(!(c("Family_Type", "Measure", "Profession"))) |> 
  # reorder to match imp_mods_all
  select(all_of(colnames(imp_mods_all)))

# Match order

cc_and_mice <- bind_rows(cc_mods_all, imp_mods_all)
```

### Comparisons CCA v MICE

```{r compare cc mice}

#---- Bs and SEs ----

ratios <-
  
  cc_and_mice |> 
  select(model, Outcome, Exposure, Adjustment, beta, SE,PR, imp) |> 
  pivot_wider(id_cols = c(model, Outcome, Exposure, Adjustment),
              names_from = imp, 
              values_from = c(beta, SE, PR)) |> 
  mutate(beta_cc = abs(beta_cc),
         beta_mice = abs(beta_mice),
         beta_ratio = beta_cc / beta_mice,
         se_ratio = SE_cc / SE_mice,
         pr_ratio = PR_cc / PR_mice) |> 
  mutate(
    Exposure = case_when(
      Exposure == "work_21_dic" ~ "Colleague support",
      Exposure == "work_22_dic" ~ "Support from superiors",
      Exposure == "work_31_dic" ~ "Violent threats",
      Exposure == "work_32_dic" ~ "Physical violence",
      Exposure == "work_30_dic" ~ "Sexual harassment",
      Exposure == "work_33_dic" ~ "Bullying",
      Exposure == "wb_wami_1_dic" ~ "Meaning in work",
      Exposure == "wb_wami_2_dic" ~ "Purpose in work",
      TRUE ~ Exposure),
    Outcome = case_when(
      Outcome == "phq_co_poi" ~ "Depression",
      Outcome == "gad_co_poi" ~ "Anxiety",
      Outcome == "cage_co_poi" ~ "Alcohol dependence",
      Outcome == "suic_idea_poi" ~ "Suicidal thoughts",
      TRUE ~ Outcome
    )
  )
  
plot_se_ml <- 
  
  ratios |> 
  filter(model == "Multilevel") |> 
  mutate(Outcome = factor(Outcome, levels = outcome_order)) |> 
  arrange(Outcome) |> 
  ggplot(aes(x = SE_cc,
             y = SE_mice, 
             colour = Adjustment,
             shape = Adjustment)) +
  geom_abline(
    intercept = 0,
    slope = 1,
    linetype = "dashed",
    colour = "grey50"
  ) +
  geom_point(
    size = 2.5,
    alpha = 0.8
  ) +
  scale_colour_grey() +
  labs(
    x = "SEs from complete-case multilevel models",
    y = "SEs from MICE multilevel models",
    title = "SE comparison (Multilevel models)"
    ) +
  theme_minimal(base_size = 12) +
  theme(
    legend.position = "bottom"
  ) +
  facet_wrap(~Outcome) 

plot_se_rob <- 
  
  ratios |> 
  filter(model == "Robust SE") |> 
  mutate(Outcome = factor(Outcome, levels = outcome_order)) |> 
  arrange(Outcome) |> 
  ggplot(aes(x = SE_cc,
             y = SE_mice, 
             colour = Adjustment,
             shape = Adjustment)) +
  geom_abline(
    intercept = 0,
    slope = 1,
    linetype = "dashed",
    colour = "grey50"
  ) +
  xlim(0, 0.15) +
  ylim(0, 0.15) +
  geom_point(
    size = 2.5,
    alpha = 0.8
  ) +
  scale_colour_grey() +
  labs(
    x = "Robust SEs from complete-case fixed-effects models",
    y = "Robust SEs from MICE fixed-effects models",
    title = "Robust SE comparison (fixed-effects models)"
    ) +
  theme_minimal(base_size = 12) +
  theme(
    legend.position = "bottom"
  ) +
  facet_wrap(~Outcome) 

plot_b_ml <- 
  
  ratios |> 
  filter(model == "Multilevel") |> 
  mutate(Outcome = factor(Outcome, levels = outcome_order)) |> 
  arrange(Outcome) |> 
  ggplot(aes(x = beta_cc,
             y = beta_mice, 
             colour = Adjustment,
             shape = Adjustment)) +
  geom_abline(
    intercept = 0,
    slope = 1,
    linetype = "dashed",
    colour = "grey50"
  ) +
  geom_point(
    size = 2.5,
    alpha = 0.8
  ) +
  scale_colour_grey() +
  labs(
    x = "Bs from complete-case multilevel models",
    y = "Bs from MICE multilevel models",
    title = "B comparison (Multilevel models)"
    ) +
  theme_minimal(base_size = 12) +
  theme(
    legend.position = "bottom"
  ) +
  facet_wrap(~Outcome) 

plot_b_rob <- 
  
  ratios |> 
  filter(model == "Robust SE") |> 
  mutate(Outcome = factor(Outcome, levels = outcome_order)) |> 
  arrange(Outcome) |> 
  ggplot(aes(x = beta_cc,
             y = beta_mice, 
             colour = Adjustment,
             shape = Adjustment)) +
  geom_abline(
    intercept = 0,
    slope = 1,
    linetype = "dashed",
    colour = "grey50"
  ) +
  geom_point(
    size = 2.5,
    alpha = 0.8
  ) +
  scale_colour_grey() +
  labs(
    x = "Bs from complete-case fixed-effects models",
    y = "Bs from MICE fixed-effects models",
    title = "B comparison (Fixed-effects models)"
    ) +
  theme_minimal(base_size = 12) +
  theme(
    legend.position = "bottom"
  ) +
  facet_wrap(~Outcome) 

plot_pr_ml <- 
  
  ratios |> 
  filter(model == "Multilevel") |> 
  mutate(Outcome = factor(Outcome, levels = outcome_order)) |> 
  arrange(Outcome) |> 
  ggplot(aes(x = PR_cc,
             y = PR_mice, 
             colour = Adjustment,
             shape = Adjustment)) +
  geom_abline(
    intercept = 0,
    slope = 1,
    linetype = "dashed",
    colour = "grey50"
  ) +
  geom_point(
    size = 2.5,
    alpha = 0.8
  ) +
  scale_colour_grey() +
  labs(
    x = "PRs from complete-case multilevel models",
    y = "PRs from MICE multilevel models",
    title = "PR comparison (Multilevel models)"
    ) +
  theme_minimal(base_size = 12) +
  theme(
    legend.position = "bottom"
  ) +
  facet_wrap(~Outcome) 

ratios |> 
  ggplot(aes(x = se_ratio, fill = Adjustment)) + 
  geom_histogram() + 
  facet_wrap(vars(model))

ratios |> 
  mutate(beta_ratio = abs(beta_ratio)) |> 
  ggplot(aes(x = beta_ratio, fill = Adjustment)) + 
  geom_histogram() + 
  facet_wrap(vars(model))

ratios |> 
  filter(Adjustment == "Adjusted") |> 
  mutate(se_ratio_group = case_when(
    se_ratio < 0.95 ~ "MICE >5% larger",
    se_ratio > 1.15 ~ "CC >15% larger",
    TRUE ~ "Within 5-15%"
    ))  |> 
  count(model, se_ratio_group)

```

```{r main forest plot, eval = FALSE}

ml_betas_prs <- 
  
  imp_mods_all |> 
  filter(model == "Multilevel")  |> 
  select(Outcome, Exposure, Adjustment, imp, beta, PR) |> 
  rename(beta_ml = beta,
         pr_ml = PR)

imp_mods_final <- 
  
  imp_mods_all  |> 
  filter(model == "Robust SE") |> 
  select(-beta, -PR, CI_u, CI_l) |>   # Drop the Robust SE beta
  left_join(ml_betas_prs, 
            by = c("Outcome", "Exposure", "Adjustment", "imp")) |> 
  select(!c(CI_u, CI_l, Risk_Unexp, Risk_Exp)) |> 
  rename(beta = beta_ml,
         PR = pr_ml) |> 
  mutate(CI_l = PR - 1.96*SE,
         CI_u = PR + 1.96*SE)

imp_mods_plot_prep <- 
  
  imp_mods_final |> 
  mutate(Exposure = factor(Exposure, levels = exposure_order)) |> 
  mutate(
    Exposure = case_when(
      Exposure == "work_8_dic"  ~ "Extended working hours",  
      Exposure == "work_11_dic" ~ "Frequent night shifts",
      Exposure == "work_12_dic" ~ "Regular shift work",
      Exposure == "work_23_dic" ~ "Tight deadlines",
      Exposure == "work_24_dic" ~ "Angry patients or relatives",
      Exposure == "work_30_dic" ~ "Sexual harassment",
      Exposure == "work_31_dic" ~ "Violent threats",
      Exposure == "work_32_dic" ~ "Physical violence", 
      Exposure == "work_33_dic" ~ "Bullying",
      Exposure == "work_19_dic" ~ "Influence over work",
      Exposure == "work_20_dic" ~ "Influence over work (breaks)",
      Exposure == "work_21_dic" ~ "Colleague support",
      Exposure == "work_22_dic" ~ "Support from superiors",
      Exposure == "work_25_dic" ~ "Work council or union",
      Exposure == "work_26_dic" ~ "Employee feedback",
      Exposure == "work_27_dic" ~ "Stress action plan",
      Exposure == "work_28_dic" ~ "Harassment protocol",
      Exposure == "work_29_dic" ~ "Violence protocol",
      TRUE ~ Exposure),
    Outcome = case_when(
      Outcome == "phq_co_poi" ~ "Depression",
      Outcome == "gad_co_poi" ~ "Anxiety",
      Outcome == "cage_co_poi" ~ "Alcohol dependence",
      Outcome == "suic_idea_poi" ~ "Suicidal thoughts",
      TRUE ~ Outcome
    ),
    Outcome = factor(Outcome, levels = outcome_order)
  ) |> 
  arrange(Outcome, Exposure) |> 
  mutate(
    Group = case_when(
      Exposure %in% names(named_demands) ~ "Job demands",
      Exposure %in% names(named_hazards) ~ "Job hazards",
      Exposure %in% names(named_resources) ~ "Job resources",
      Exposure %in% names(named_protocols) ~ "Organisational support structures",
      TRUE ~ "Other"
      ),
    Group = factor(Group, levels = c("Job demands", "Job hazards", "Job resources", "Organisational support structures"))
  ) |> 
  filter(Adjustment == "Adjusted") |> 
  rename(Lower = CI_l, Upper = CI_u) |> 
  mutate(
    Outcome = factor(Outcome, levels = outcome_order),
    Exposure = factor(Exposure, levels = exposure_order_named),
    PR_fmt = format(round(PR, 2), nsmall = 1, decimal.mark = "·"),
    Low_fmt = format(round(Lower, 2), nsmall = 1, decimal.mark = "·"),
    Up_fmt = format(round(Upper, 2), nsmall = 1, decimal.mark = "·")
  ) |> 
  arrange(Outcome, Exposure)

#---- Plot ----

# Generate forest plot function
make_forest_plot <- 
  function(df, target_outcome, show_y = TRUE) {
  
  p <- 
    
    df |>
    filter(Outcome == target_outcome) |> 
    ggplot(aes(x = PR, y = fct_rev(Exposure))) +
    geom_point(size = 2.5) +
    geom_linerange(aes(xmin = Lower, xmax = Upper)) +
    geom_text(aes(x = 3, label = paste0(PR_fmt, " (", Low_fmt, "-", Up_fmt, ")")),
              hjust = 1, size = 4) + 
    
    facet_grid(Group ~ ., scales = "free_y", space = "free_y", switch = "y") +
    geom_vline(xintercept = 1, linetype = "dashed") +
    
    scale_x_log10(
      breaks = c(0.2, 0.5, 1, 2),
      labels = scales::label_number(accuracy = 0.1, decimal.mark = "·")
    ) +
    
    labs(y = "", x = "Prevalence Ratio", title = target_outcome) + 
    ggpubr::theme_pubr() + 
    theme(
      plot.title = element_text(hjust = 0.5, face = "bold", size = 12),
      strip.placement = "outside",
      strip.background.y = element_blank(),
      strip.text.y.left = element_text(angle = 0, face = "bold", size = 10),
      axis.text = element_text(size = 10),
      axis.title.x = element_text(size = 10),
      panel.border = element_rect(color = "black", fill = NA, linewidth = 0.5) 
    )
  
  # RULE FOR THE RIGHT-SIDE PLOTS 
  # If show_y is FALSE, we make the y-axis text and Group labels invisible
  if (!show_y) {
    p <- p + theme(
      axis.text.y = element_blank(),      # Hides the exposure names
      axis.ticks.y = element_blank(),     # Hides the little tick marks
      strip.text.y.left = element_blank() # Hides the Group names
    )
  }
  
  return(p)
  }

# Left plots get the labels (show_y = TRUE is the default)
p_dep <- make_forest_plot(imp_mods_plot_prep, "Depression", show_y = TRUE)
p_alc <- make_forest_plot(imp_mods_plot_prep, "Alcohol dependence", show_y = TRUE)

# Right plots hide the labels
p_anx <- make_forest_plot(imp_mods_plot_prep, "Anxiety", show_y = FALSE)
p_sui <- make_forest_plot(imp_mods_plot_prep, "Suicidal thoughts", show_y = FALSE)

# Stitch them together!
final_grid_adj <- (p_dep | p_anx) / (p_alc | p_sui)

# View it
final_grid_adj

ragg::agg_png("out/figures/forest_adjusted_mice.png",
              width = 9,
              height = 7,
              units = "in",
              res = 600,
              scaling = 0.5)

print(final_grid_adj)

dev.off()

ggsave(final_grid_adj, 
       filename = "forest_adjusted_mice.pdf",
       device = "pdf",
       path = "out/figures/",
       scale = 3.5,
       width = 140,
       height = 100,
       units = "mm",
       dpi = 320
       )

rm(final_grid_adj)
```

# Main analyses with alternative methods

## Generate models

Set to eval = FALSE to avoid computation. This chunk loads generated RDS comparing
all models

```{r load methods summary}
methods_summary <- readRDS("out/models/summary/methods_summary.RDS")
```


```{r exp-out prep comparison, eval = FALSE}

# define outcomes, exposures, covariates

out_poisson # Keep it this way as it is specified 1/0.

# already defined

demands_dic

hazards_dic

protocols_dic

resources_dic

covs_1

covs_2

# define strata

profs <- levels(ds$work_2)

# maps

covariate_map <- list(
  "base_covs" = covs_1
)

# Create grid with both families
tasks <- expand_grid(
  Outcome = out_poisson,
  Family = c("poisson", "log-binomial", "logistic"), # Add new families
  Exposure = all_exposures,
  Covar_Key = "base_covs",      
  profession = profs            
)

tasks_all <- expand_grid(
  Outcome = out_poisson,
  Family = c("poisson", "log-binomial", "logistic"), 
  Exposure = all_exposures,
  Covar_Key = "base_covs",
  profession = "All"
)

#---- Computation ----

# # Set up parallel processing (uses all cores minus whatever you want)
plan(sequential)
  
```

```{r exp-out all, eval = FALSE}
exp_out_all <- future_pmap(list(
  tasks_all$Outcome,
  tasks_all$Family,
  tasks_all$Exposure,
  tasks_all$Covar_Key,
  tasks_all$profession
), function(outcome, family, exposure, cov_key, prof) {
  
  message(paste("Processing:", outcome, "x", exposure, "in", prof))

  res_crude <- run_crude_mods(
    data = ds,
    outcome_var = outcome,
    exposure_var = exposure,
    profession = prof,
    cluster_var = covs_2,
    family_type = family
  )

  res_adj <- run_adj_mods(
    data = ds,
    outcome_var = outcome,
    exposure_var = exposure,
    profession = prof,
    family_type = family,
    cluster_var = covs_2,
    confounder_list = covariate_map[[cov_key]],
    model_label = "Adjusted"
  )

  # Combine internally
  
  row_multilevel <- 
    
    bind_rows(
    res_crude$multilevel,
      res_adj$multilevel
    )
  
  row_robust <- 
    
    bind_rows(
    res_crude$robust,
      res_adj$robust
    )
  
  # return as clean pair
  
  return(list(
    multilevel = row_multilevel,
    robust     = row_robust
  ))
}, .options = furrr_options(seed = TRUE))


# Unzip and combine

glm_multilevel_df <- map_dfr(exp_out_all, "multilevel")

glm_robust_df <- map_dfr(exp_out_all, "robust")


# Save

saveRDS(glm_multilevel_df, "out/dataframes/glm_multilevel_df.rds")
saveRDS(glm_robust_df, "out/dataframes/glm_robust_df.rds")
```

## Compare methods

```{r merge robust se, eval = FALSE}
robust_mods <- readRDS("out/dataframes/glm_robust_df.rds")
ml_mods <- readRDS("out/dataframes/glm_multilevel_df.rds")

# Join everything
model_summary <-
  
  ml_mods |> 
  bind_rows(robust_mods) |> 
  select(-c(Profession, N_Analysis, starts_with("Risk"))) |>
  mutate(model = if_else(model == "Robust SE", "Robust", "Standard")) |> 
  pivot_wider(
    names_from = model,
    values_from = c(beta, SE, PR, CI_l, CI_u)
  ) |> 
  mutate(
    SE = if_else(Family_Type == "poisson", SE_Robust, SE_Standard),
    CI_l = if_else(Family_Type == "poisson", CI_l_Robust, CI_l_Standard),
    CI_u = if_else(Family_Type == "poisson", CI_u_Robust, CI_u_Standard)
    ) |> 
  rename(beta = beta_Standard,
         estimate = PR_Standard,
         family = Family_Type) |> 
  select(-ends_with(c("Standard", "Robust"))) |> 
  mutate(
    family = str_to_sentence(family),
    family = if_else(family == "Poisson", "Poisson + Robust SE", family)
  ) |> 
  relocate(estimate, .after = SE)

model_summary  

saveRDS(model_summary, "out/dataframes/methods_summary.RDS")

```

```{r plots}
# --- Prepare data ---

# Outcome labels (reuse from your existing code)
outcome_labels <- c(
  "phq_co_poi"    = "Depression",
  "gad_co_poi"    = "Anxiety",
  "suic_idea_poi" = "Suicidal thoughts",
  "cage_co_poi"   = "Alcohol dependence"
)

# Exposure short labels for the tile plot
exposure_labels <- c(
  "work_8_dic"  = "Long hours",
  "work_11_dic" = "Night shifts",
  "work_12_dic" = "Shift work",
  "work_19_dic" = "Influence",
  "work_20_dic" = "Breaks",
  "work_21_dic" = "Colleague support",
  "work_22_dic" = "Superior support",
  "work_23_dic" = "Deadlines",
  "work_24_dic" = "Angry patients",
  "work_25_dic" = "Union/council",
  "work_26_dic" = "Feedback",
  "work_27_dic" = "Stress plan",
  "work_28_dic" = "Harassment prot.",
  "work_29_dic" = "Violence prot.",
  "work_30_dic" = "Sexual harassment",
  "work_31_dic" = "Violent threats",
  "work_32_dic" = "Physical violence",
  "work_33_dic" = "Bullying"
)

# Pivot to wide: one row per Outcome × Exposure × Adjustment
comp_wide <- methods_summary |>
  filter(family %in% c("Poisson + Robust SE", "Log-binomial")) |>
  select(family, Outcome, Exposure, Adjustment, beta) |>
  mutate(
    Outcome   = recode(Outcome,   !!!outcome_labels),
    Exposure  = recode(Exposure,  !!!exposure_labels),
    Outcome   = factor(Outcome,   levels = unname(outcome_labels))
  ) |>
  pivot_wider(names_from = family, values_from = beta) |>
  rename(beta_poisson = `Poisson + Robust SE`,
         beta_logbin  = `Log-binomial`) |>
  mutate(converged = !is.na(beta_logbin))

# Convergence failure counts for annotation
n_failed <- sum(!comp_wide$converged)
n_total  <- nrow(comp_wide)
pct_fail <- round(100 * n_failed / n_total)

# ---- Panel A: scatter of betas ----

panel_a <- comp_wide |>
  filter(converged) |>
  ggplot(aes(x = beta_poisson, y = beta_logbin, shape = Adjustment)) +
  geom_abline(intercept = 0, slope = 1,
              linetype = "dashed", colour = "grey50") +
  geom_point(size = 2.5, alpha = 0.85, colour = "grey20") +
  facet_wrap(~Outcome, nrow = 2) +
  labs(
    x     = "log(PR)  —  Poisson + Robust SE",
    y     = "log(PR)  —  Log-binomial",
    shape = "Adjustment",
    tag   = "A"
  ) +
  coord_equal() +
  theme_minimal(base_size = 11) +
  theme(legend.position = "bottom",
        panel.grid.minor = element_blank(),
        strip.text = element_text(face = "bold"))

# ---- Panel B: convergence failure tile ----

panel_b <- comp_wide |>
  # keep one row per Outcome × Exposure × Adjustment
  mutate(
    status = if_else(converged, "Converged", "Failed"),
    Adjustment = factor(Adjustment, levels = c("Crude", "Adjusted"))
  ) |>
  ggplot(aes(x = Adjustment, y = Exposure, fill = status)) +
  geom_tile(colour = "white", linewidth = 0.4) +
  facet_wrap(~Outcome, nrow = 1) +
  scale_fill_manual(
    values = c("Converged" = "grey85", "Failed" = "#c0392b"),
    name   = "Log-binomial"
  ) +
  labs(
    x   = NULL,
    y   = NULL,
    tag = "B"
  ) +
  theme_minimal(base_size = 11) +
  theme(
    axis.text.x  = element_text(angle = 30, hjust = 1),
    axis.text.y  = element_text(size = 9),
    legend.position = "bottom",
    panel.grid   = element_blank(),
    strip.text   = element_text(face = "bold")
  )

# ---- Combine and export ----

fig_combined <- panel_a / panel_b +
  plot_layout(heights = c(1.4, 1)) +
  plot_annotation(
    title    = "Comparison of Poisson + Robust SE and log-binomial models",
    subtitle = glue(
      "Panel A: log(PR) agreement where both models converged (n = {sum(comp_wide$converged)}).\n",
      "Panel B: convergence status of log-binomial across all Outcome × Exposure × Adjustment combinations ",
      "({n_failed}/{n_total} failed, {pct_fail}%)."
    ),
    theme = theme(
      plot.title    = element_text(face = "bold", size = 13),
      plot.subtitle = element_text(size = 10, colour = "grey30")
    )
  )

ragg::agg_png(
  "out/figures/sensitivity_logbinomial.png",
  width = 9, height = 10, units = "in", res = 600, scaling = 0.55
)
print(fig_combined)
dev.off()

# ---- Scatter plot of SEs ----

comp_wide_se <- 
  
  methods_summary |>
  filter(family %in% c("Poisson + Robust SE", "Log-binomial")) |>
  select(family, Outcome, Exposure, Adjustment, SE) |>
  mutate(
    Outcome   = recode(Outcome,   !!!outcome_labels),
    Exposure  = recode(Exposure,  !!!exposure_labels),
    Outcome   = factor(Outcome,   levels = unname(outcome_labels))
  ) |>
  pivot_wider(names_from = family, values_from = SE) |>
  rename(SE_poisson = `Poisson + Robust SE`,
         SE_logbin  = `Log-binomial`) |>
  mutate(converged = !is.na(SE_logbin))

se_plot <- comp_wide_se |>
  filter(converged) |>
  ggplot(aes(x = SE_poisson, y = SE_logbin, shape = Adjustment)) +
  geom_abline(intercept = 0, slope = 1,
              linetype = "dashed", colour = "grey50") +
  geom_point(size = 2.5, alpha = 0.85, colour = "grey20") +
  facet_wrap(~Outcome, nrow = 2) +
  labs(
    x     = "log(PR)  —  Poisson + Robust SE",
    y     = "log(PR)  —  Log-binomial",
    shape = "Adjustment",
    tag   = "C"
  ) +
  coord_equal() +
  theme_minimal(base_size = 11) +
  theme(legend.position = "bottom",
        panel.grid.minor = element_blank(),
        strip.text = element_text(face = "bold")) +
  xlim(0,0.15) +
  ylim(0,0.15)

ragg::agg_png(
  "out/figures/sensitivity_logbinomial_SE.png",
  width = 9, height = 10, units = "in", res = 600, scaling = 0.55
)
print(se_plot)
dev.off()
```
